---
title: "analysis_new"
author: "Wenyu"
date: "5/11/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(tidymodels)
library(ggsci)
```

## Unsupervised target and network analysis

```{r}
# kegg_tibble <- read_csv("~/cluster_scratch/prior/kegg_tibble.csv")
# 
# load("~/cluster_scratch/glmnet_modelling/target_pred_server/targetpred_serverinput.RData")
# 
# source('~/cluster_wrk/drug_moa/unsupervised_target_exploration/get_target_matrix_from_long_target_tibble.R')
# source('~/cluster_wrk/drug_moa/unsupervised_target_exploration/annotate_feature_matrix.R')
# 
# target_tibble_drugbank= ctrp_target_tibble %>%
#   ungroup() %>%
#   select(broad_cpd_id, gene_symbol_of_protein_target) %>%
#   rename(drug=broad_cpd_id, target_gene=gene_symbol_of_protein_target) %>% 
#   mutate(binding_score= 1)
# 
# target_tibble_dtc <- ctrp_target_dtc %>% 
#   select(standard_inchi_key, gene_name, interaction_strength) %>%
#   filter(interaction_strength!= 0) %>% 
#   drop_na() %>% 
#   group_by(standard_inchi_key, gene_name) %>% 
#   summarize(interaction_strength= median(interaction_strength,na.rm = T)) %>% 
#   ungroup() %>% 
#   inner_join(ctrpv2_list_to_zia,by= c("standard_inchi_key"= "InChIKey")) %>% 
#   select(broad_cpd_id, gene_name, interaction_strength) %>% 
#   group_by(broad_cpd_id, gene_name) %>% 
#   summarize(interaction_strength= max(interaction_strength,na.rm = T)) %>% 
#   ungroup() %>%   rename(drug=broad_cpd_id, target_gene=gene_name, binding_score= interaction_strength) 

# length(unique(target_tibble$drug))

# Plotting feature_imp vs dtc target binding plot
# use dtc target as a base to join drugbank and feature importance

# res <- target_tibble_dtc %>% 
#   left_join(target_tibble_drugbank %>% rename(drug_bank_target= binding_score)) %>% 
#   inner_join(
#     y=feature_imp_ridge_ctrp_ces1 %>% 
#       pivot_longer(cols= -broad_cpd_id, names_to= "gene", values_to= "feature_imp"),
#     by= c("drug" = "broad_cpd_id", "target_gene" = "gene")) %>% 
#   mutate(drug_bank_target= replace_na(drug_bank_target, 0) )
#     
#     
# res %>% 
#   # filter(drug_bank_target ==1) %>% 
#   ggplot(aes(y= log10(abs(feature_imp)), x=binding_score)) + 
#   geom_point(aes(shape= factor(drug_bank_target)),size= 0.01)+
#   theme_classic()
```

## 1 Load the binary target network

```{r}
CTRP_binary_PPIold_data <- read_csv( "~/cluster_scratch/prior/CTRP_binary_PPIold_data.csv") 
CTRP_binary_PPInew_data <- read_csv( "~/cluster_scratch/prior/CTRP_binary_PPInew_data.csv")
GDSC_binary_PPIold_data <- read_csv( "~/cluster_scratch/prior/GDSC_binary_PPIold_data.csv") 
GDSC_binary_PPInew_data <- read_csv( "~/cluster_scratch/prior/GDSC_binary_PPInew_data.csv")
# PRISM_binary_PPIold_data <- read_csv( "~/cluster_scratch/prior/PRISM_binary_PPIold_data.csv")
# PRISM_binary_PPInew_data <- read_csv( "~/cluster_scratch/prior/PRISM_binary_PPInew_data.csv")
```

check data correctness
```{r}

#first check if sig value is correct here
# BRD-K28360340	BCL2
CTRP_binary_PPIold_data %>% 
  filter(drug== "BRD-K28360340") %>% 
  filter(gene=="BCL2")
# Why the value is the same?? this is definately wrong
CTRP_binary_PPIold_data %>% 
  filter(drug== "BRD-K28392481") %>% 
  filter(gene=="DDR1")

# setwd("~/cluster_scratch//L1000/consensus_signatures_challenge/")
# drug_consensus_ctrp <- read_csv("feature_consensus_ctrp.csv")

drug_consensus_ctrp %>% 
  filter(drug %in% c("BRD-K28392481","BRD-K28360340")) %>% 
  select(drug,DDR1, BCL2)
```


## 2 Ugly result
Now I have a annotation matrix for the ConSen-sig and ConExp-sig
lets compare how they can be used

In this comparison I don't care about direction, but only the absolute value.

1）direct comparison, but instead of using the original value which is too small and not comparable across two signatures, should I use rank?
```{r}
CTRP_binary_PPIold_data %>% 
  mutate(anno_type1= 
           fct_relevel(anno_type1, c("Target","1st degree","2nd degree","3rd degree","over_3","Not_connected", "Unknown" ))) %>% 
  filter(anno_type1 != "Unknown") %>% 
  # filter(anno_type !="Target") %>% 
  group_by(drug, imptype) %>% 
  mutate(rank=rank(desc(abs(imp)))/n() ) %>%
  ungroup() %>% 
  ggplot(aes(x= imptype,y = rank, fill= anno_type1)) +
  # geom_bar(stat = "summary" , fun.y = "mean",position = position_dodge())+
  # stat_summary(fun.data = mean_se, geom = "errorbar",position = position_dodge())
  geom_boxplot(position = position_dodge(),outlier.shape=NA )
  # ylim(c(0,0.006))

# CTRP_binary_PPInew_data %>% 
#   mutate(anno_type1= 
#            fct_relevel(anno_type1, c("Target","1st degree","2nd degree","3rd degree","over_3","Not_connected", "Unknown" ))) %>% 
#   filter(anno_type1 != "Unknown") %>% 
#   group_by(drug, imptype) %>% 
#   mutate(rank=rank(desc(abs(imp)))/n() ) %>%
#   ungroup() %>% 
#   ggplot(aes(x= imptype,y = rank, fill= anno_type1)) +
#   # geom_bar(stat = "summary" , fun.y = "mean",position = position_dodge())+
#   # stat_summary(fun.data = mean_se, geom = "errorbar",position = position_dodge())
#   geom_boxplot(position = position_dodge(),outlier.shape=NA )
#   # ylim(c(0,0.006))
# 

# CTRP_binary_PPIold_data %>% 
#   mutate(anno_type1= 
#            fct_relevel(anno_type1, c("Target","1st degree","2nd degree","3rd degree","over_3","Not_connected", "Unknown" ))) %>% 
#   filter(anno_type1 != "Unknown") %>% 
#   group_by(drug, imptype) %>% 
#   mutate(rank=rank(desc(abs(imp)))/n() ) %>%
#   ungroup() %>% 
#   ggplot(aes(x= imptype,y = rank, fill= anno_type1)) +
#   geom_bar(stat = "summary" , fun.y = "mean",position = position_dodge())+
#   stat_summary(fun.data = mean_se, geom = "errorbar",position = position_dodge())
#   # geom_boxplot(position = position_dodge(),outlier.shape=NA )
#   # ylim(c(0,0.006))
# 
# CTRP_binary_PPInew_data %>% 
#   mutate(anno_type1= 
#            fct_relevel(anno_type1, c("Target","1st degree","2nd degree","3rd degree","over_3","Not_connected", "Unknown" ))) %>% 
#   filter(anno_type1 != "Unknown") %>% 
#   group_by(drug, imptype) %>% 
#   mutate(rank=rank(desc(abs(imp)))/n() ) %>%
#   ungroup() %>% 
#   ggplot(aes(x= imptype,y = rank, fill= anno_type1)) +
#   geom_bar(stat = "summary" , fun.y = "mean",position = position_dodge())+
#   stat_summary(fun.data = mean_se, geom = "errorbar",position = position_dodge())
#   # geom_boxplot(position = position_dodge(),outlier.shape=NA )
#   # ylim(c(0,0.006))  
```

Well, despite the ConSen-sig perform better that ConExp-Sig, using rank is not so persuasive since average ranking of the target is around 30%.


how about z normalization of the score so that they are comparable,


```{r}
CTRP_binary_PPIold_data %>% 
  mutate(anno_type1= 
           fct_relevel(anno_type1, c("Target","1st degree","2nd degree","3rd degree","over_3","Not_connected", "Unknown" ))) %>% 
  filter(anno_type1 != "Unknown") %>% 
  # filter(anno_type !="Target") %>% 
  group_by(drug, imptype) %>% 
  mutate(rank=rank(desc(abs(imp)))/n() ) %>%
  ungroup() %>% 
  ggplot(aes(x= imptype,y = rank, fill= anno_type1)) +
  # geom_bar(stat = "summary" , fun.y = "mean",position = position_dodge())+
  # stat_summary(fun.data = mean_se, geom = "errorbar",position = position_dodge())
  geom_boxplot(position = position_dodge(),outlier.shape=NA )
```




2) pick top 50, 100, 200 genes and compare to what percentage of drugs can be prioritized by the
top genes

say we choose top 50 genes for each drug, 
then how many drugs the target of which is picked?

for all the picked drug gene pairs, if the are not drug target pair then what are they


```{r}
get_drug_frac <- function(dataset, top_num, res_type = "target_summary", top_method="top_abs"){
  # The function calculates that for a given dataset, how many drug, the target of which is prioritized? 
  # top drug is selected by abosoulte values (top_abs) or both side(top_both)
  
  
  n_drug= dataset %>% filter(anno_type1 %in%  "Target") %>% select(drug) %>% distinct() %>% nrow()
  
# target
  if(top_method == "top_both") {
      top_druggenepairs<-
  bind_rows(
    dataset %>%
      group_by(drug,imptype) %>% 
      top_n(wt=imp,  n= top_num) %>% 
      ungroup() %>% 
      mutate(impdef= "toppos gene"),
    dataset %>% 
      group_by(drug, imptype) %>% 
      top_n(wt=imp, n = -top_num) %>% 
      ungroup() %>% 
      mutate(impdef= "topneg gene"),
  )
  }
  
  
  if(top_method == "top_abs") {
      top_druggenepairs<-
    dataset %>%
      mutate(imp_abs= abs(imp)) %>% 
      group_by(drug,imptype) %>% 
      top_n(wt=imp_abs,  n= top_num) %>% 
      ungroup() %>%
      mutate(impdef= case_when(
        imp>0 ~"toppos gene",
        imp<0 ~"topneg gene"))

  }
  

  drug_shortest_path_tibble <- top_druggenepairs %>% 
    mutate(anno_type2 = case_when(
    anno_type!="Target" ~anno_type,
    TRUE ~ "0")) %>%    
  mutate(anno_type2= as.numeric(anno_type2) ) %>% 
  drop_na() %>% 
  group_by(drug, imptype) %>% 
  top_n(wt = anno_type2,n = -1) %>% 
  ungroup() %>% 
  select(imptype,drug, anno_type2,impdef) %>% 
  distinct(imptype,drug, anno_type2,.keep_all = TRUE)
  
  target_summary <- 
    top_druggenepairs %>% 
      filter(anno_type1 %in% "Target") %>% 
      select(drug, imptype, impdef) %>% 
      distinct() %>% 
      group_by(imptype,impdef) %>% 
      summarize(frac= round(n()*100/n_drug, 1),
                count= n()) %>% 
      mutate(top_n= top_num)
  

  if (res_type == "target_summary") {return(target_summary)} 
  if (res_type == "toppair") {return(top_druggenepairs)} 
  if (res_type == "druglevel") {return(drug_shortest_path_tibble)} 

}


get_drug_frac(CTRP_binary_PPIold_data,top_num = 50,res_summmarized = F) %>% 
   filter(anno_type1 %in%  "Target") %>% 
      select(drug, imptype, impdef) %>% 
      distinct()


tmp <- get_drug_frac(CTRP_binary_PPIold_data,top_num = 50,res_type = "toppair",top_method = "top_abs") 
```


```{r}
target_idf <- bind_rows(
  map_dfr(
    .x = c(50, 100, 200), 
    .f = ~get_drug_frac(dataset= CTRP_binary_PPIold_data, top_num=.x)) %>% 
    mutate(dataset= "CTRP"),
  map_dfr(.x = c(50, 100, 200), 
          .f = ~get_drug_frac(dataset= GDSC_binary_PPIold_data, top_num=.x)) %>% 
    mutate(dataset= "GDSC")
  # map_dfr(.x = c(50, 100, 200), 
  #         .f = ~get_drug_frac(dataset= PRISM_binary_PPIold_data, top_num=.x)) %>% 
  #   mutate(dataset= "PRISM")
)

# Bar plot: pos/neg stack, top_n dodge, imptype x axis, dataset facet 
# seems impossible to both stack and dodge

target_idf %>% 
  # filter(frac!=50) %>% 
  ggplot(aes(x= factor(top_n),y = frac, fill= impdef)) +
  geom_bar(stat = "identity",position = "stack")+
  facet_grid(cols = vars(dataset), rows = vars(imptype))+
  xlab("top N genes ranked by signature value")+
  ylab("% drugs")

```

#lets still go back to drug percentage,
checking
```{r}
# get_drug_frac(CTRP_binary_PPIold_data,top_num = 100,res_type = "druglevel") %>% 
#   select(-drug) 
# 
# get_drug_frac(dataset= GDSC_binary_PPIold_data, top_num=100, res_type = "druglevel") %>% 
#     mutate(dataset= "GDSC")
# 
# get_drug_frac(dataset= PRISM_binary_PPIold_data, top_num=100, res_type = "druglevel") %>% 
#     mutate(dataset= "PRISM")
# 
# 
# CTRP_binary_PPIold_data %>% 
#   filter(!(anno_type1 %in% c("Unknown","Not_connected"))) %>% 
#   select(drug) %>% 
#   distinct() %>% 
#   nrow() #196
# 
# GDSC_binary_PPIold_data %>% 
#   filter(!(anno_type1 %in% c("Unknown","Not_connected"))) %>% 
#   select(drug) %>% 
#   distinct() %>% 
#   nrow() # 49
# 
# PRISM_binary_PPIold_data %>% 
#   filter(!(anno_type1 %in% c("Unknown","Not_connected"))) %>% 
#   select(drug) %>% 
#   distinct() %>% 
#   nrow() #805
# 
# 
# tmp <- get_drug_frac(dataset= PRISM_binary_PPIold_data, top_n=100, res_type = "toppair") %>% 
#     mutate(dataset= "PRISM") %>% select(drug) %>% distinct() #918
# 
# # there are 5 drugs the top genes are not 
# tmp <- get_drug_frac(dataset= PRISM_binary_PPIold_data, top_n=100, res_type = "toppair") %>% 
#     filter(!(anno_type1 %in% c("Unknown","Not_connected"))) %>% select(drug) %>% distinct() #918
# tmp1 <- PRISM_binary_PPIold_data %>% 
#   filter(!(anno_type1 %in% c("Unknown","Not_connected"))) %>% 
#   select(drug) %>% 
#   distinct() 
# tmp2 <- setdiff(tmp1,tmp)
# tmp3 <- PRISM_binary_PPIold_data %>% 
#   # filter(!(anno_type1 %in% c("Unknown","Not_connected"))) %>% 
#   filter(drug %in% tmp2$drug)
# # the reason that the 5 drugs are not avaliable is because their target is not among top genes,
# # and all the other genes are not in the network.
```


```{r}
network_idf <- bind_rows(
  get_drug_frac(dataset= CTRP_binary_PPIold_data, top_n=100, res_type = "druglevel") %>% 
    mutate(dataset= "CTRP") %>%  select(-drug) ,
  get_drug_frac(dataset= GDSC_binary_PPIold_data, top_n=100, res_type = "druglevel") %>% 
    mutate(dataset= "GDSC") %>%  select(-drug) 
  # get_drug_frac(dataset= PRISM_binary_PPIold_data, top_n=100, res_type = "druglevel") %>% 
  #   mutate(dataset= "PRISM") %>%  select(-drug) 
)

network_idf %>% 
  ggplot(aes(x= factor(anno_type2), fill= impdef)) +
  geom_bar(stat = "count",position = "stack")+
  facet_grid(cols = vars(dataset), rows = vars(imptype))+
  xlab("top N genes ranked by signature value")+
  ylab("number of drugs")

network_idf %>% 
  group_by(dataset,imptype) %>% 
  mutate(num= n()) %>% 
  ungroup() %>% 
  group_by(impdef, anno_type2,dataset, imptype) %>% 
  summarize(perc= n()/num) %>% 
  ungroup() %>% distinct() %>% 
  ggplot(aes(x= factor(anno_type2),y=perc, fill= impdef)) +
  geom_bar(stat = "identity",position = "stack")+
  facet_grid(cols = vars(dataset), rows = vars(imptype))+
  xlab("top N genes ranked by signature value")+
  ylab("% drugs")  
```




For top genes, if the are not target then what are they (this plot is ugly)
```{r}
get_drug_frac(CTRP_binary_PPIold_data,top_num = 100,res_type = "toppair") %>%
  ggplot(aes(x= imptype, fill= anno_type)) +
  geom_bar(stat = "count",position = "dodge")

table(CTRP_binary_PPIold_data1$imptype)
```


```{r}
# for top 100 top and bottom genes how does them distribute in the target network?
tmp <- CTRP_binary_PPIold_data1 %>% filter(imptype=="ConSen-Sig")
table(tmp$impdef,tmp$anno_type1)
tmp <- CTRP_binary_PPIold_data1 %>% filter(imptype=="ConExp-Sig")
table(tmp$impdef,tmp$anno_type1)



CTRP_binary_PPIold_data1 %>% 
  mutate(degree= as.numeric(anno_type)) %>% 
  drop_na() %>% 
  group_by(imptype) %>% 
  summarise(cor= cor(degree, imp,method="spearman"))

```

3) ROC and AUC 

Lets use target, target+ 1st negibour... as binarizing threshold and plot AUC for the ranked gene list for the two type of signatures


for each dataset I draw several such ROC curves. I think within one dataset, only one curve is drawn for all the drugs.

How should I combine the  AUC curves for multiple drugs? Or should I use box plot to represent AUC for each drug?

perhaps a direct comparison for the available drugs how many target are detected by the most important genes

show me the percentage of the drugs the target of which are being identified as top important genes
```{r}
# tmp <- CTRP_binary_PPIold_data %>% 
#   filter(anno_type == "Target") %>% 
#   left_join(CTRP_binary_PPIold_data1) %>% 
#   select(-anno_type, -anno_type1) %>% 
#   mutate(impdef=replace_na(impdef, replace = "others"))
# 
# table(tmp$imptype, tmp$impdef) # this is meaningless considering that there are more "background genes"
# 
# # for drugs with both two type of data, how many drugs the target of which has been picked by the top 100 genes?
#   
# drug_list <- 
#   ctrp_target_binary %>% 
#   filter(drug %in% ctrp_drug_list) %>% 
#   pull(drug)
# 
# # Or, directly compare whether the drug target ranked higher in consensig than conexp sig
# map_chr(drug_list, function(x){
#   target= ctrp_target_binary %>% 
#     fitler(drug==x) %>% 
#     pull(target)
#   rank_consensig= consen
#   if (target)
#   
# }
#         )
```


better coverage and comparable or even higher AUC?
But what is the interpretation of ConExp-Sig?

For drug target direction matter. For other 1,2,3,neighbour it doesn't
```{r}
# The consen-imp for target should be positive. The higher the value the more likely it is a target?
CTRP_binary_PPIold_data %>%
  filter(anno_type1!="Unknown") %>%
  filter(imptype=="ConSen-Sig") %>%
  filter(imp>0) %>%
  mutate(anno_binary= factor(anno_type1=="Target",levels = c(TRUE,FALSE))) %>% 
  group_by(drug) %>% 
  summarise(AUC= roc_auc_vec(truth = anno_binary,estimate = imp,event_level = "first")) %>% 
  ungroup() %>% 
  pull(AUC) %>% summary

# Consensig imp
CTRP_binary_PPIold_data %>%
  filter(anno_type1!="Unknown") %>%
  filter(imptype=="ConSen-Sig") %>%
  mutate(anno_binary= factor(anno_type1=="Target",levels = c(TRUE,FALSE))) %>% 
  group_by(drug) %>% 
  summarise(AUC= roc_auc_vec(truth = anno_binary,estimate = imp,event_level = "first")) %>% 
  ungroup() %>% 
  pull(AUC) %>% summary

# Consensig (imp <0) => imp = 0
CTRP_binary_PPIold_data %>%
  filter(anno_type1!="Unknown") %>%
  filter(imptype=="ConSen-Sig") %>%
  mutate(anno_binary= factor(anno_type1=="Target",levels = c(TRUE,FALSE))) %>% 
  mutate(imp = case_when(imp>0 ~ imp, 
                         imp<0 ~ 0)) %>% 
  group_by(drug, imptype) %>% 
  summarise(AUC= roc_auc_vec(truth = anno_binary,estimate = imp,event_level = "first")) %>% 
  ungroup() %>% 
  pull(AUC) %>% summary


CTRP_binary_PPIold_data %>%
  filter(anno_type1!="Unknown") %>%
  filter(imptype=="ConSen-Sig") %>%
  mutate(anno_binary= factor(anno_type1=="Target",levels = c(TRUE,FALSE))) %>% 
  group_by(drug, imptype) %>% 
  summarise(AUC= roc_auc_vec(truth = anno_binary,estimate = abs(imp))) %>% 
  ungroup() %>% 
  pull(AUC) %>% summary

# To draw the type of ROC Jing wants I need multiclass AUC
# one truth facotr vector column and multiple columns of class prediction values
# but that is not the case in my data. The multiclass AUC is for those each datapoint must be one # class.


# The conexp-imp for target should be negative. 
#The higher the abs value the more likely it is a target?
# however in our data it is not the case

#filter and abs
CTRP_binary_PPIold_data %>%
  filter(anno_type1!="Unknown") %>%
  filter(imptype=="ConExp-Sig") %>%
  filter(imp<0) %>%
  mutate(anno_binary= factor(anno_type1=="Target",levels = c(TRUE,FALSE))) %>% 
  group_by(drug, imptype) %>% 
  summarise(AUC= roc_auc_vec(truth = anno_binary,estimate = abs(imp))) %>% 
  ungroup() %>% 
  pull(AUC) %>% summary

#abs
CTRP_binary_PPIold_data %>%
  filter(anno_type1!="Unknown") %>%
  filter(imptype=="ConExp-Sig") %>%
  mutate(anno_binary= factor(anno_type1=="Target",levels = c(TRUE,FALSE))) %>% 
  group_by(drug, imptype) %>% 
  summarise(AUC= roc_auc_vec(truth = anno_binary,estimate = abs(imp))) %>% 
  ungroup() %>% 
  pull(AUC) %>% summary

# -relu
CTRP_binary_PPIold_data %>%
  filter(anno_type1!="Unknown") %>%
  filter(imptype=="ConExp-Sig") %>%
  mutate(anno_binary= factor(anno_type1=="Target",levels = c(TRUE,FALSE))) %>% 
  mutate(imp = case_when(imp<0 ~ abs(imp), 
                       imp>0 ~ 0)) %>%  
  group_by(drug, imptype) %>% 
  summarise(AUC= roc_auc_vec(truth = anno_binary,estimate = (imp))) %>% 
  ungroup() %>% 
  pull(AUC) %>% summary
  
```


Lets just use abs(imp) to identify T, T+1 T+2 for different dataset
```{r}

get_auc <- 
  function(dataset= CTRP_binary_PPIold_data, label_level= 0){
  dataset %>% 
    mutate(anno_type2 = case_when(
      anno_type!="Target" ~anno_type,
      TRUE ~ "0")) %>%    
    mutate(anno_type2= as.numeric(anno_type2) ) %>% 
    drop_na() %>% 
    mutate(abs_imp= abs(imp)) %>% 
    mutate(anno_binary= factor(x = (anno_type2 < (label_level+1)),levels = c(TRUE,FALSE))) %>% 
    group_by(drug, imptype) %>% 
    summarise(AUC= roc_auc_vec(truth = anno_binary,estimate = abs_imp)) %>% 
    ungroup() 
  }

tmp <- get_auc(dataset = CTRP_binary_PPIold_data, label_level= 0) 
tmp %>% ggplot(aes(x= imptype, y= AUC,fill=imptype)) + geom_boxplot()

tmp <- get_auc(dataset = CTRP_binary_PPIold_data, label_level= 1) 
tmp %>% ggplot(aes(x= imptype, y= AUC,fill=imptype)) + geom_boxplot()

tmp <- get_auc(dataset = CTRP_binary_PPIold_data, label_level= 2) 
tmp %>% ggplot(aes(x= imptype, y= AUC,fill=imptype)) + geom_boxplot()

tmp <- get_auc(dataset = GDSC_binary_PPIold_data, label_level= 0) 
tmp %>% ggplot(aes(x= imptype, y= AUC,fill=imptype)) + geom_boxplot()

tmp <- get_auc(dataset = GDSC_binary_PPIold_data, label_level= 1) 
tmp %>% ggplot(aes(x= imptype, y= AUC,fill=imptype)) + geom_boxplot()

tmp <- get_auc(dataset = GDSC_binary_PPIold_data, label_level= 2) 
tmp %>% ggplot(aes(x= imptype, y= AUC,fill=imptype)) + geom_boxplot()

# tmp <- get_auc(dataset = PRISM_binary_PPIold_data, label_level= 0) 
# tmp %>% ggplot(aes(x= imptype, y= AUC,fill=imptype)) + geom_boxplot()
# 
# tmp <- get_auc(dataset = PRISM_binary_PPIold_data, label_level= 1) 
# tmp %>% ggplot(aes(x= imptype, y= AUC,fill=imptype)) + geom_boxplot()
# 
# tmp <- get_auc(dataset = PRISM_binary_PPIold_data, label_level= 2) 
# tmp %>% ggplot(aes(x= imptype, y= AUC,fill=imptype)) + geom_boxplot()
```





To draw the type of ROC Jing wants I need multiclass AUC
one truth facotr vector column and multiple columns of class prediction values
but that is not the case in my data. The multiclass AUC is for those each datapoint must be one # class.

Instead what I am going to draw is the vertical averaging version of the ROC plot, similar to 
what I have done in Finemap project. But now there are existing function to do that

i.e. https://rdrr.io/cran/genscore/man/avgrocs.html

I will use ROCR package  (check ROCR.hiv in ROCR package reference mannual)

```{r}
sig_to_pred <- function(annotated_sig_df) {
  # for con sen sig we do relu, for con exp sig we do negative relu
  data1 <- 
    annotated_sig_df %>%
    filter(imptype== "ConSen-Sig") %>% 
    mutate(anno_binary= factor(anno_type1=="Target",levels = c(TRUE,FALSE))) %>%
    mutate(imp = case_when(imp>0 ~ imp, imp<0 ~ 0)) 
    
  data2 <- 
    annotated_sig_df %>%
    filter(imptype== "ConExp-Sig") %>% 
    mutate(anno_binary= factor(anno_type1=="Target",levels = c(TRUE,FALSE))) %>%
    mutate(imp = case_when(imp<0 ~ abs(imp), imp>0 ~ 0))   
  annotate_pred_df <- bind_rows(data1,data2)
  return(annotate_pred_df)
}




get_ave_roc <- function(annotated_pred_df, title, addlegend= T){
  library(ROCR)
  tmp0 <- annotated_pred_df %>%
    filter(anno_type1!="Unknown") %>%
    group_by(drug,imptype) %>% 
    summarise(AUC= roc_auc_vec(truth = anno_binary,estimate = imp,event_level = "first")) %>% 
    ungroup() %>% 
    drop_na()
  
  tmp <- annotated_pred_df %>%
    filter(anno_type1!="Unknown") %>%
    mutate(labels= factor(anno_type1=="Target",levels = c(TRUE,FALSE)), predictions= abs(imp)) %>% 
    select(drug, imptype, labels,predictions) %>% 
    nest_by(drug, imptype)  %>% 
    inner_join(tmp0)
  
  ## here I used transpost from purrr package to change the index order of this multi-level list
  ROCR.consensig <- tmp %>% filter(imptype== "ConSen-Sig") %>% pull(data) %>% transpose()
  ROCR.conexpsig <- tmp %>% filter(imptype== "ConExp-Sig") %>% pull(data) %>% transpose()
  
  pred <- prediction(ROCR.consensig$predictions, ROCR.consensig$labels)
  perf <- performance(pred,'tpr','fpr')
  pred1 <- prediction(ROCR.conexpsig$predictions, ROCR.conexpsig$labels)
  perf1 <- performance(pred1,'tpr','fpr')
  plot(perf, avg="vertical", lwd=3, col="red",spread.estimate="stderror",plotCI.lwd=2,main =title)
  plot(perf1, avg="vertical", lwd=3, col="blue",spread.estimate="stderror",plotCI.lwd=2,add=T)
  if(addlegend== T){legend("bottomright", legend = c("ConSen-Sig", "ConExp-Sig"), lty = 1, lwd = 2, col = c("red", "blue"))}
}
```


```{r,fig.height=4, fig.width=4}
get_ave_roc(sig_to_pred(annotated_sig_df = CTRP_binary_PPIold_data),title = "CTRP",addlegend = F)
get_ave_roc(sig_to_pred(annotated_sig_df = GDSC_binary_PPIold_data),title = "GDSC")
# get_ave_roc(sig_to_pred(annotated_sig_df = CTRP_binary_PPInew_data),title = "CTRP",addlegend = F)
# get_ave_roc(sig_to_pred(annotated_sig_df = GDSC_binary_PPInew_data),title = "GDSC")
```


The drug level auc here should also correlate with the fitting accuracy.
but lets check it later

So lets just show the AUC result for the CTRP and GDSC Target
```{r,fig.width=5,fig.height=3}
auc_df <- 
  bind_rows(
    get_auc(dataset = CTRP_binary_PPIold_data, label_level= 0) %>% mutate(dataset= "CTRP"),
    get_auc(dataset = GDSC_binary_PPIold_data, label_level= 0) %>% mutate(dataset= "GDSC") %>% 
      mutate(drug= as.character(drug))
    # get_auc(dataset = PRISM_binary_PPIold_data, label_level= 0) %>% mutate(dataset= "PRISM")
)


auc_df %>% 
  drop_na() %>% 
  ggplot(aes(x=imptype, y=AUC,color= imptype)) + 
  geom_violin()+
  stat_summary(fun.data = "mean_cl_boot", geom = "pointrange",
           colour = "black")+
  facet_wrap(~dataset)+
  theme_classic()+
  theme(axis.text.x = element_blank())+
  xlab(label = "")+
  ylab(label = "AUC")+
  # scale_color_manual(name="Cylinders",
  #                  labels=c("ConSen-sig", "ConExp-sig", "Fingerprint-ECFP","Fingerprint-MACCS" ))+
  scale_color_npg()
```


```{r,fig.width=5,fig.height=3}
# tmp <- auc_df %>% 
#   filter(AUC > 0.99) 
# 
# table(tmp$imptype)
# 
# tmp <- CTRP_binary_PPIold_data %>% 
#   filter(drug=="BRD-A41692738") %>% 
#   filter(imptype== "ConSen-Sig")
# 
# tmp <- CTRP_binary_PPIold_data %>% 
#   filter(drug=="BRD-A35588707") %>% 
#   filter(imptype== "ConExp-Sig")
# 
# tmp <- CTRP_binary_PPIold_data %>% 
#   filter(drug=="BRD-K09951645") %>% 
#   filter(imptype== "ConSen-Sig")

load("~/cluster_scratch/forward_modelling/targetpred_output_simplefiltering.RData")
#does the auc coorelation with fitting accuracy:
tmp <- auc_df %>% 
  filter(dataset=="CTRP") %>% 
  filter(imptype=="ConSen-Sig") %>% 
  inner_join(res_ctrp2,by=c("drug"="broad_cpd_id")) %>% 
  mutate(acc= (ceres+ces+demeter2)/3)

tmp1 <- tmp %>% filter(AUC < 0.6) %>% 
  filter(acc>0.45) %>% 
  filter(sample_size >400) 


tmp2 <- CTRP_binary_PPIold_data %>% 
  filter(imptype=="ConSen-Sig") %>% 
  filter(drug == "BRD-K15318909")
  # filter(drug %in% HDAC_inhibitors$drug)
  # filter(drug== "BRD-K77908580" )
  # filter(drug== "BRD-K02130563" )

HDAC_inhibitors <- ctrp_target_binary %>% filter(str_detect(target,pattern = "HDAC")) 

tmp2
```


```{r, fig.width=4, fig.height=4}
# library(ggrepel)
tmp %>% 
  ggplot(aes(y=AUC, x=acc)) + 
  geom_point()+
  geom_hline(yintercept = 0.6)+
  geom_vline(xintercept = 0.45)+
  geom_text(
    aes(label=ifelse( cpd_name %in% c("PAC-1" ) ,cpd_name,''),hjust=0.5,vjust=0.5))+
  xlab("Sensitivity fitting accuracy")+
  ylab("Nominal target prioritization AUC")

```


```{r}
tmp1 <- tmp %>% filter(AUC < 0.6) %>% 
  filter(acc>0.5) %>% 
  filter(sample_size >400) #BRD-K49328571

tmp1 %>% 
  ggplot(aes(x=acc, y= AUC)) + 
  geom_point()+
  geom_text(aes(label= cpd_name))
  
tmp2 <- CTRP_binary_PPIold_data %>% filter(drug %in% "BRD-K49328571" ) %>% 
  filter(imptype=="ConSen-Sig")

```

https://www.nature.com/articles/s41375-020-0978-7
HOw to prove the KIT are not a target of dasatinib
drug are still effective in KIT knockout cells.

BRD-K49328571


now considering only for drugs that have a good sensitivity fitting accuracy but bad 
target prediction accuracy, we check if this is due to lack of target label in the binary gold
standard dataset


```{r}
tmp3 <- auc_df %>% 
  filter(dataset=="CTRP") %>% 
  filter(imptype=="ConSen-Sig") %>% 
  inner_join(res_ctrp2,by=c("drug"="broad_cpd_id")) %>% 
  mutate(acc= (ceres+ces+demeter2)/3) %>% filter(AUC < 0.60) %>% 
  filter(acc>0.45) %>% 
  filter(sample_size >400) %>% 
  filter(drug %in% ctrp_target_dtc$drug)

# will these drugs, the top genes of which have a higher binding score
# examine the top ten positive gene for each drug
# tmp4 <- get_drug_frac(CTRP_binary_PPIold_data,top_num = 5,top_method = "top_both",res_type = "toppair" ) %>% 
#   filter(impdef %in% "toppos gene") %>% 
#   filter(imptype == "ConSen-Sig") %>% 
#   filter(drug %in% tmp3$drug) %>% 
#   inner_join(tmp3, by="drug")

# some experiment that true target is the top genes but not its original target


# DTC result is also limited!
# tmp5 <- tmp4 %>% inner_join(ctrp_target_dtc %>% rename(gene= target))

tmp4 <- get_drug_frac(CTRP_binary_PPIold_data,top_num = 10,top_method = "top_both",res_type = "toppair" ) %>% 
  filter(impdef %in% "toppos gene") %>% 
  filter(imptype == "ConSen-Sig") %>% 
  filter(drug == "BRD-K92991072") %>% 
  select(gene, imp, anno_type1) %>% 
  mutate(imp= round(imp, 3))

tmp5 <- CTRP_binary_PPIold_data %>% 
   filter(anno_type1 %in% "Target") %>% 
  filter(imptype == "ConSen-Sig") %>% 
  filter(drug == "BRD-K92991072") %>% 
  select(gene, imp, anno_type1) %>% 
  mutate(imp= round(imp, 3)) %>% 
  bind_rows(tmp4)


tmp4 <- get_drug_frac(CTRP_binary_PPIold_data,top_num = 10,top_method = "top_both",res_type = "toppair" ) %>% 
  filter(impdef %in% "toppos gene") %>% 
  filter(imptype == "ConSen-Sig") %>% 
  filter(drug == "BRD-K49328571") %>% 
  select(gene, imp, anno_type1) %>% 
  mutate(imp= round(imp, 3))

tmp5 <- CTRP_binary_PPIold_data %>% 
   filter(anno_type1 %in% "Target") %>% 
  filter(imptype == "ConSen-Sig") %>% 
  filter(drug == "BRD-K49328571") %>% 
  select(gene, imp, anno_type1) %>% 
  mutate(imp= round(imp, 3)) %>% 
  bind_rows(tmp4)

```




## 2 pathway analysis
```{r}
load("~/cluster_scratch/ctrp/ctrpv2_data.RData")
load("~/cluster_scratch/glmnet_modelling/target_pred_server/res_pathway_go.RData")
feature_imp_ridge_ctrp_ces1 <- read_csv("~/cluster_scratch/glmnet_modelling/result_largevm/feature_imp_ridge_ctrp_ces1.csv")

pathways_df <- 
  tibble(
    broad_cpd_id=feature_imp_ridge_ctrp_ces1$broad_cpd_id,res_pathway) %>% 
  unnest()%>% 
  arrange(padj) %>% 
  inner_join(y = ctrpv2_data %>% select_at(1:5),
             by= "broad_cpd_id")
  
doxorubicin <- pathways_df %>% filter(cpd_name=="doxorubicin") #topoisomerase II
# Trametinib <- pathways_df %>% filter(cpd_name=="trametinib")
dinaciclib <- pathways_df %>% filter(cpd_name=="dinaciclib")
alvocidib <- pathways_df %>% filter(cpd_name=="alvocidib")

# check which pathway are enriched in a category of drug
# tmp <- pathways_df %>% 
#   filter(target_or_activity_of_compound== "inhibitor of cyclin-dependent kinases") %>%
#   group_by(pathway) %>% 
#   summarise(mean_p =mean(padj))

tmp <- pathways_df %>% 
  filter(target_or_activity_of_compound== "inhibitor of cyclin-dependent kinases") %>%
  # filter(broad_cpd_id == "BRD-K64800655") %>% 
  filter(pathway== "GOCC_CHROMOSOME_CENTROMERIC_REGION")


# https://www.ncbi.nlm.nih.gov/pmc/articles/PMC4156313/
tmp <- res2 %>% 
  filter(target_or_activity_of_compound== "inhibitor of cyclin-dependent kinases") 



top_5drugs <- pathways_df %>% select(broad_cpd_id) %>% distinct() %>% slice(1:5)

tmp  <- pathways_df %>% 
  filter(broad_cpd_id %in% top_5drugs$broad_cpd_id) 
  
```

## 3
What is the expectation of MDR1 and ABCB1?
I suppose they ranked highly irrespecive of drug identity.
WEll not really..

```{r}
tmp <- feature_imp_ridge_ctrp_comb1 %>% 
  filter(drug %in% ctrp_drug_list) %>% 
  pivot_longer(-drug,names_to="gene", values_to="imp") %>% 
  group_by(drug) %>% 
  mutate(gene_rank= rank(imp)) %>% 
  ungroup() %>% 
  group_by(gene) %>% 
  summarize(meanrank= mean(gene_rank))

tmp <- feature_imp_ridge_ctrp_comb1 %>% 
  filter(drug %in% ctrp_drug_list) %>% 
  pivot_longer(-drug,names_to="gene", values_to="imp") %>% 
  group_by(drug) %>% 
  mutate(gene_rank= rank(imp)) %>% 
  ungroup() %>% 
  filter(gene=="ABCB1")


tmp2 <- apply(feature_imp_ridge_gdsc_comb1[,-1],MARGIN = 1, rank) 
summary(tmp[rownames(tmp)=="ABCB1","ZZZ3"])
tmp3 <- apply(tmp2, 1, mean) 

tmp4 <- 
  bind_cols(
as.data.frame(tmp1) %>% rownames_to_column(var = "gene") %>% arrange(gene),
as.data.frame(tmp3) %>% rownames_to_column(var = "gene") %>% arrange(gene)
)



```






