---
title: "unsupervised target exploration"
author: "Wenyu"
date: "3/10/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Note all the useful analysis has been moved.
This file is nolonger used


# 2 Unsupervised target exploration
use network long table, target long table and feature long table to generate a full long table with at least 5 columns


Now I derive the ces based feature importance vector to see 

```{r}
kegg_tibble <- read_csv("~/cluster_scratch/prior/kegg_tibble.csv")

target_tibble <- ctrp_target_tibble %>%
  ungroup() %>%
  select(broad_cpd_id, gene_symbol_of_protein_target) %>%
  rename(drug=broad_cpd_id, target_gene=gene_symbol_of_protein_target) %>% 
  mutate(binding_score= 1)


save(ces1_glm_feature_annotated,
     file = "~/cluster_scratch/glmnet_modelling/drugbank_annotated_feature_importance.RData"
     )
```

plot how the feature importance top ranked genes falls in direct target and 1, 2,3 neighbors. 
```{r}
load("~/cluster_scratch/glmnet_modelling/drugbank_annotated_feature_importance.RData")

drugbank_annotated_feature_importance <- 
  ces1_glm_feature_annotated %>% 
  mutate(ess= "ces1") 
%>% 
  bind_rows(ces2_glm_feature_annotated %>% mutate(ess= "ces2")) %>% 
  bind_rows(ceres_glm_feature_annotated %>% mutate(ess= "ceres")) %>%   
  bind_rows(demeter_glm_feature_annotated %>% mutate(ess= "demeter")) 


#let plot a grouped table of how target and their 1,2,3 neighbors are identified.

# feature importance distribution 

tmp <- drugbank_annotated_feature_importance %>%
  filter(imp!=0) %>% 
  pull(imp)
hist(tmp)  


drugbank_annotated_feature_importance %>% 
  filter(imp!=0) %>% 
  ggplot(aes(x= target_cat, y= imp, fill= ess)) +
  geom_violin()+
  theme_classic()+
  geom_hline(yintercept =0)

# drugbank_annotated_feature_importance %>% 
#   filter(imp!=0) %>% 
#   ggplot(aes(x= target_cat, y= log2(imp+1), fill= ess)) +
#   geom_violin()+
#   theme_classic()
fig <- drugbank_annotated_feature_importance %>% 
  filter(imp!=0) %>% 
  # ggplot(aes(x= target_cat, y= log(imp+1), fill= ess)) +
  ggplot(aes(x= target_cat, y= imp, fill= ess)) +
  geom_boxplot(outlier.size = 0.01)+ #outlier.size = -1
  geom_hline(yintercept = 0, lty=4, color= "red")+
  theme_classic()+
  xlab("Gene type")+
  ylab("Feature importance")+
  labs(fill= "Essentiality") +
  scale_x_discrete(breaks=c("0","1","2","3","4"),
        labels=c("Nomial target", "1st neighbour", "2nd neigbour", "3rd neighbour", "Others"))
  

# drugbank_annotated_feature_importance %>% 
#   filter(imp!=0) %>% 
#   ggplot(aes(x= target_cat, y= log2(imp+1), fill= ess)) +
#   geom_boxplot()+
#   theme_classic()

# how to transform the y axis so that it distribute more equally?

```

```{r, fig.height=2,fig.width=6}
fig
```


```{r}
#how many target and 1,2,3 neighbours has been identified by the non-zero feature importance?
drugbank_annotated_feature_importance %>% 
  filter(imp!=0) %>% 
  # filter(target_cat!=4) %>% 
  select(-imp) %>% 
  ggplot(aes(x= target_cat,  fill= ess)) +
  geom_bar(position = position_dodge())

# note dont use numbers, use the percentage: such as what percent of all the target are identified by the positive drug-gene feature importance?
tmp <- drugbank_annotated_feature_importance %>% 
  filter(target_cat==0) %>% 
  filter(imp > 0) %>%
  # filter(imp!0) %>% 
  group_by(ess) %>% 
  summarise(Percetage= n()/744)

# looks that the percentage of identifying the direct target is not looking good.
# (ceres result better than ces1?)
# perhaps stay with the form plot.
# or maybe tailer a threshold?


#How many target has been identified by the positive feature importance?
tmp <- drugbank_annotated_feature_importance %>% 
  # filter(target_cat==0) %>% 
  filter(imp > 0) %>%
  group_by(ess) %>% 
  summarise(Percetage= n())

```

ROC curve
```{r}
# tmp <-drugbank_annotated_feature_importance %>% 
#   mutate(d= (target_cat == "0")) 
  # pivot_wider(names_from=ess, values_from=imp)
  

library(plotROC)


fig <-  drugbank_annotated_feature_importance %>% 
  filter(imp>0) %>% 
  mutate(d= (target_cat == "0")) %>% 
  ggplot(aes(d = d, m = imp, color = ess )) + 
  geom_roc(n.cuts=0, size =0.3) + 
  style_roc(xlab="FPR",ylab="TPR")+
  theme_classic()+
  ggtitle("drugbank")+
      scale_x_continuous(breaks=seq(0,1,0.2),name = "FPR")+
    scale_y_continuous(breaks=seq(0,1,0.2),name = "TPR")
```

```{r,fig.height=2, fig.width=3}
fig
```





How about use dtc target to annotate
note now you also have interaction strength!

```{r}
ctrpv2_list_to_zia <- read_csv("~/cluster_scratch/prior/ctrpv2_list_to_zia.csv")
ctrp_target_dtc <- read_csv("~/cluster_scratch/prior/ctrp_target_dtc.csv")

target_tibble <- ctrp_target_dtc %>% 
  select(standard_inchi_key, gene_name, interaction_strength) %>%
  filter(interaction_strength!= 0) %>% 
  drop_na() %>% 
  group_by(standard_inchi_key, gene_name) %>% 
  summarize(interaction_strength= median(interaction_strength,na.rm = T)) %>% 
  ungroup() %>% 
  inner_join(ctrpv2_list_to_zia,by= c("standard_inchi_key"= "InChIKey")) %>% 
  select(broad_cpd_id, gene_name, interaction_strength) %>% 
  group_by(broad_cpd_id, gene_name) %>% 
  summarize(interaction_strength= median(interaction_strength,na.rm = T)) %>% 
  ungroup() %>%   rename(drug=broad_cpd_id, target_gene=gene_name, binding_score= interaction_strength) 

# ces1_glm_feature_annotated <- 
#   annotate_feature_matrix(
#     network = kegg_tibble,
#     feature_imp_mat = feature_imp_glmnet_ctrp_ces1%>% 
#       rename(drug= broad_cpd_id),
#     target=  target_tibble
#     )
# 
# ces2_glm_feature_annotated <- 
#   annotate_feature_matrix(
#     network = kegg_tibble,
#     feature_imp_mat = feature_imp_glmnet_ctrp_ces2%>% 
#       rename(drug= broad_cpd_id),
#     target=  target_tibble
#     )
#   
# ceres_glm_feature_annotated <- 
#     annotate_feature_matrix(
#     network = kegg_tibble,
#     feature_imp_mat = feature_imp_glmnet_ctrp_ceres %>% 
#       rename(drug= broad_cpd_id),
#     target=  target_tibble
#     )
# 
# demeter_glm_feature_annotated <- 
#     annotate_feature_matrix(
#     network = kegg_tibble,
#     feature_imp_mat = feature_imp_glmnet_ctrp_demeter2 %>% 
#       rename(drug= broad_cpd_id),
#     target=  target_tibble
#     )
# 
# save(list = c("ces1_glm_feature_annotated","ces2_glm_feature_annotated","ceres_glm_feature_annotated","demeter_glm_feature_annotated"),
#      file = "~/cluster_scratch/glmnet_modelling/DTC_annotated_feature_importance.RData"
#      )

```

since both feature importance and target binding score are continues now
lets see how do they agree with each other.

Is there a correlation?  for genes that do have a drug target binding score, does the feature importance value correlate with the numeric binding strength (original values or abs or only take the negative/positive ones?))


```{r}
load("~/cluster_scratch/glmnet_modelling/DTC_annotated_feature_importance.RData")
DTC_annotated_feature_importance <- 
  ces1_glm_feature_annotated %>% 
  mutate(ess= "ces1") %>% 
  bind_rows(ces2_glm_feature_annotated %>% mutate(ess= "ces2")) %>% 
  bind_rows(ceres_glm_feature_annotated %>% mutate(ess= "ceres")) %>%   
  bind_rows(demeter_glm_feature_annotated %>% mutate(ess= "demeter")) %>% 
  left_join(target_tibble,by= c("drug"= "drug", "gene"= "target_gene"))

```

Is there a linear relationship?

```{r}
fig <- DTC_annotated_feature_importance %>% 
  drop_na() %>%
  filter(imp!=0) %>% 
  ggplot(aes(y= imp, x= binding_score, color= ess)) 

fig +  geom_point()
fig +  stat_summary_bin(geom="crossbar",position = position_dodge()) 
```


```{r}
fig <- DTC_annotated_feature_importance %>% 
  drop_na() %>%
  filter(imp>0) %>%
  filter(ess== "ces1") %>% 
  ggplot(aes(y= log10(imp), x= binding_score))+
  geom_point(size= 0.1)+
  # stat_summary_bin(geom="crossbar",width= 0.3, color= "red",bins = 8)+
  theme_classic()
```


```{r, fig.width=2, fig.height=2}
fig
```

How does the ROC and Precision-recall curve looks like?

Note the precision and recall curve requires a binary label.
lets just use binding score 0, 0.2, 0.4, 0.6, 0.8 as threshold for binarization
```{r}
generate_roc_by_thresholding <- function(x){
  tmp <- DTC_annotated_feature_importance %>% 
  replace_na(list(binding_score = 0)) %>% 
  mutate(d= as.integer(binding_score>x))  %>% 
  filter(imp > 0)
  # mutate(threshold_0= (binding_score>0)) %>% 
  # mutate(threshold_0.2= (binding_score>0.2)) %>% 
  # mutate(threshold_0.4= (binding_score>0.4)) %>% 
  # mutate(threshold_0.6= (binding_score>0.6) ) %>% 
  # mutate(threshold_0.8= (binding_score>0.8)) %>% 
  # filter(threshold== threshold_0.2) %>% 
  # pivot_longer(cols = starts_with("thres"),names_to = "threshold", values_to= "D") %>% 
  tmp %>% 
  ggplot(aes(d = d, m = imp, color = ess)) + 
  geom_roc(n.cuts=0) + 
  style_roc(xlab="FPR",ylab="TPR")+
  theme_classic()+
  ggtitle(paste("threshold", x,sep= " "))

  }


```

```{r}
generate_roc_by_thresholding(0.2)
generate_roc_by_thresholding(0.4)
generate_roc_by_thresholding(0.5)
generate_roc_by_thresholding(0.6)
generate_roc_by_thresholding(0.8)


```


how many drug are there for each expression dataset?
```{r}
x <- ctrpv2_data$sensitivity[[1]]
tmp <- ctrpv2_data %>% 
  mutate(exp_data_point= map_int(.x = sensitivity, .f = function(x){
    tmp <- x %>% inner_join( 
      y= janitor::clean_names(exp_seq_imputed[,1:2])%>% 
        rename_at(vars(!contains("dep_map_id")), .fun= ~paste0(., "_predictors")), 
            by= c("DepMap_ID"="dep_map_id")) 
    tmp1 <- nrow(tmp)
    return(tmp1)
  })) 
estimate_performance_glmnet(sen_df = x,ess = exp_seq_imputed[,1:10])
estimate_performance_glmnet(sen_df = x,ess = exp_seq_imputed[,1:10])
```


explore how ces1 feature importance correspond to drug perturbated gene expression?
```{r}
#first check the overlapping drugs available between ctrp and consensus signature.
consensus_signature_shRNA <- read_csv("/home/cloud-user/cluster_scratch/L1000/consensus_signatures_challenge/consensus_signature_shRNA.csv")
# also check the overlapping genes between the gene vector and perturbed genes.
consensus_signature_drugs <- read_csv("/home/cloud-user/cluster_scratch/L1000/consensus_signatures_challenge/consensus_signature_drugs.csv")


# 183 overlapping drugs
overlapping_drug <- intersect(consensus_signature_drugs$X1, ctrpv2_data$broad_cpd_id)

load("~/cluster_scratch/glmnet_modelling/target_pred_server/targetpred_serverinput.RData")

# 3562 overlapped perturved genes. 
overlapping_gene <- intersect(consensus_signature_shRNA$X1,
            colnames(feature_imp_ridge_ctrp_ces1))

```




 




```{r}
pathways_df <- 
  tibble(broad_cpd_id=feature_imp_ridge_ctrp_ces1$broad_cpd_id,res_pathway) %>% 
  unnest()%>% 
  arrange(padj) %>% 
  inner_join(y = ctrpv2_data %>% select_at(1:5),
             by= "broad_cpd_id")
  
top_5drugs <- pathways_df %>% select(broad_cpd_id) %>% distinct() %>% slice(1:5)
tmp  <- pathways_df %>% 
  filter(broad_cpd_id %in% top_5drugs$broad_cpd_id) 
  
```

