---
title: "Modelling output exploration Part2 drug target prediction"
author: "Wenyu"
date: "1/15/2021"
output: html_document
---

The aim of this nootbook is to explore whether the extracted model importances from the sen~ess glmnet model can be used in supervised drug target prediction


## 1)
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(tidymodels)
load("~/cluster_scratch/forward_modelling/forwardmodelling_all.RData")
```

## 2) read in files. 

read in all the needed csv file for drug target prediction using various predictors and then save an RData file as input for modelscript

### 2.1 read in model based features
```{r,warning = FALSE, message=FALSE}
feature_imp_ridge_ctrp_ces1 <- read_csv("~/cluster_scratch/forward_modelling/feature_imp/feature_imp_ridge_ctrp_ces1.csv")

feature_imp_ridge_ctrp_ceres <- read_csv("~/cluster_scratch/forward_modelling/feature_imp/feature_imp_ridge_ctrp_ceres.csv")

feature_imp_ridge_ctrp_demeter2 <- read_csv("~/cluster_scratch/forward_modelling/feature_imp/feature_imp_ridge_ctrp_ces1.csv")

feature_imp_ridge_ctrp_exp <- read_csv("~/cluster_scratch/forward_modelling/feature_imp/feature_imp_ridge_ctrp_exp.csv")

feature_imp_ridge_gdsc_ces1 <- read_csv("~/cluster_scratch/forward_modelling/feature_imp/feature_imp_ridge_gdsc_ces1.csv")

feature_imp_ridge_gdsc_ceres <- read_csv("~/cluster_scratch/forward_modelling/feature_imp/feature_imp_ridge_gdsc_ceres.csv")

feature_imp_ridge_gdsc_demeter2 <- read_csv("~/cluster_scratch/forward_modelling/feature_imp/feature_imp_ridge_gdsc_ces1.csv")

feature_imp_ridge_gdsc_exp <- read_csv("~/cluster_scratch/forward_modelling/feature_imp/feature_imp_ridge_gdsc_exp.csv")

feature_imp_ridge_prism_ces1 <- read_csv("~/cluster_scratch/forward_modelling/feature_imp/feature_imp_ridge_prism_ces1.csv")

feature_imp_ridge_prism_ceres <- read_csv("~/cluster_scratch/forward_modelling/feature_imp/feature_imp_ridge_prism_ceres.csv")

feature_imp_ridge_prism_demeter2 <- read_csv("~/cluster_scratch/forward_modelling/feature_imp/feature_imp_ridge_prism_ces1.csv")

feature_imp_ridge_prism_exp <- read_csv("~/cluster_scratch/forward_modelling/feature_imp/feature_imp_ridge_prism_exp.csv")
```

### 2.2 read in target labels 
```{r,warning = FALSE, message=FALSE}
ctrp_target_binary <- read_csv("~/cluster_scratch/prior/ctrpv2_target_binary.csv")
gdsc_target_binary <- read_csv("~/cluster_scratch/prior/gdsc_target_binary.csv")
prism_target_binary <- read_csv("~/cluster_scratch/prior/prism_target_binary.csv")
ctrp_target_dtc <- read_csv("~/cluster_scratch/prior/ctrpv2_target_dtc.csv")
gdsc_target_dtc <- read_csv("~/cluster_scratch/prior/gdsc_target_dtc.csv")
prism_target_dtc <- read_csv("~/cluster_scratch/prior/ctrpv2_target_dtc.csv")
```

### 2.3 read in additional feature preparation
```{r,warning = FALSE, message=FALSE}
#fingerprint
setwd("~/cluster_scratch/fingerprints/new/fingerprint/result")
feature_maccs_ctrp <- read_csv("maccs_finger_ctrp.csv") %>% select(-smiles, -InChIKey,-pubchem_cid) %>% rename(drug =broad_cpd_id)
feature_extended_ctrp <- read_csv("extended_finger_ctrp.csv") %>% select(-smiles, -InChIKey,-pubchem_cid) %>% rename(drug =broad_cpd_id)

feature_maccs_gdsc <- read_csv("maccs_finger_gdsc.csv")%>% select(-smiles,-PubCHEM) %>% rename(drug =DRUG_ID)
feature_extended_gdsc <- read_csv("extended_finger_gdsc.csv")%>% select(-smiles, -PubCHEM) %>% rename(drug =DRUG_ID)

feature_maccs_prism <- read_csv("maccs_finger_prism.csv")%>% select(-smiles, -InChIKey,-pubchem_cid) %>% rename(drug =BROAD_ID)
feature_extended_prism <- read_csv("extended_finger_prism.csv") %>% select(-smiles, -InChIKey,-pubchem_cid) %>% rename(drug =BROAD_ID)

## Consensus signature
setwd("~/cluster_scratch//L1000/consensus_signatures_challenge/")
drug_consensus_ctrp <- read_csv("feature_consensus_ctrp.csv")
drug_consensus_prism <- read_csv("feature_consensus_prism.csv")
drug_consensus_gdsc <- read_csv("feature_consensus_gdsc.csv")
```

### 2.4 save workspace
```{r,warning = FALSE, message=FALSE}
save.image("~/cluster_scratch/forward_modelling/targetpred_serverinput.RData")
```


Some previous analysis
```{r,warning = FALSE, message=FALSE}
# Write A function to calculate jaccard similarity based on fingerprint
# extended_cor <- feature_extended_finger_print %>% 
#   pivot_longer(cols = -broad_cpd_id,names_to= "name", values_to= "value") %>% 
#   pivot_wider(id_cols = name, names_from= broad_cpd_id,  values_from= value) %>%
#   arrange(name) %>% 
#   select(-name) %>% 
#   as.matrix() %>%
#   prabclus::jaccard()
  # cor(method = "spearman")
  

# hist(extended_cor) 
# extended_cor1 <- (extended_cor - 0.5)* (-2)
# extended_cor1 <- -extended_cor + mean(extended_cor)
# hist(extended_cor1) 

# maccs_cor <- feature_maccs_finger_print %>% 
#   pivot_longer(cols = -broad_cpd_id,names_to= "name", values_to= "value") %>% 
#   arrange(broad_cpd_id) %>% 
#   pivot_wider(id_cols = name, names_from= broad_cpd_id,  values_from= value) %>% 
#   select(-name) %>% 
#   as.matrix() %>% 
#   prabclus::jaccard()
#   # cor(method = "spearman")

# hist(maccs_cor)
# maccs_cor1 <- -maccs_cor + mean(maccs_cor)
# hist(maccs_cor1) 
# hist(sen_cor)
 
# ces1_cor <- cor(t(
#   x = feature_imp_ridge_ctrp_ces1 %>% 
#     rename(drug=broad_cpd_id) %>% 
#     arrange(drug) %>% 
#     select(-drug) %>% 
#     mutate_all(.funs = scale)), method = "spearman")
# ces1_cor[ces1_cor<0] <- 0
# colnames(ces1_cor) <- row.names(ces1_cor) <- sort(feature_imp_ridge_ctrp_ces1$broad_cpd_id)
# 
# sen_cor <- cor(t(
#   x = feature_sen_ctrp %>% 
#     rename(drug=broad_cpd_id) %>% 
#     arrange(drug) %>% 
#     select(-drug) %>% 
#     mutate_all(.funs = scale)), method = "spearman")
# sen_cor[sen_cor<0] <- 0
# colnames(sen_cor) <- row.names(sen_cor) <- sort(feature_imp_ridge_ctrp_ces1$broad_cpd_id)


# ces1_extended_cor <- (ces1_cor + extended_cor)/2
# ces1_extended_sen_cor <- (ces1_cor + extended_cor+ sen_cor)/3
# ces1_maccs_cor <- (ces1_cor + maccs_cor)/2
# ces1_maccs_sen_cor <- (ces1_cor + maccs_cor+ sen_cor)/3

save.image("~/cluster_scratch/glmnet_modelling/target_pred_server/targetpred_serverinput.RData")
```

lets use the existing target information of the
365 drugs to do cv and predict drug target

The prediction algorithm can be based on dream challenge and performance is evaluated using cv.
We then consider again a nested cv to first find the thresholding parameters 

the central idea is to check what additional value can such basal cell info bring to MOA prediction in addition to the drug sensitivity and how does the accuracy comparing to, for example, chemical fingerprint based prediction?

## 3) Supervisied prediction with ctrpv2's own target info (from DrugBank)
```{r}
# load("~/cluster_scratch/forward_modelling/targetpred_serverinput.RData")


```



write a function to output a acc_df for choice of estimation method, dataset, and target file.

```{r}
function(dataset= "ctrp", id_list= NULL, estimation_method= , target_source= ctrp_target_binary){
  source('~/cluster_wrk/drug_moa/supervised_target_pred/no_tunning_weighted_averaging.R')
  source('~/cluster_wrk/drug_moa/supervised_target_pred/get_target_matrix_from_long_target_tibble.R')
  
  if (estimation_method== "fold_cv") {
    source('~/cluster_wrk/drug_moa/supervised_target_pred/return_acc_estimate_5fold_cv.R')
    } 
  if (estimation_method== "loocv") {
    source('~/cluster_wrk/drug_moa/supervised_target_pred/return_acc_estimate_loocv.R')
    } 
  set.seed(0000)
  
  acc_ces1 <- return_acc_estimate_cv(
    target_tibble = target_source,
    predictors_tibble = eval(as.symbol(
        str_c("feature_imp_ridge_", dataset, "_ces1" ,collapse = "") )) )
  
  acc_ceres<- return_acc_estimate_cv(
    target_tibble = target_source,
        predictors_tibble = eval(as.symbol(
        str_c("feature_imp_ridge_", dataset, "_ces1" ,collapse = "") )) ) 
  
  acc_demeter2<- return_acc_estimate_cv(
    target_tibble = target_source,
        predictors_tibble = eval(as.symbol(
        str_c("feature_imp_ridge_", dataset, "_ces1" ,collapse = "") ))  ) 
  
  acc_exp<- return_acc_estimate_cv(
    target_tibble = target_source,
        predictors_tibble = eval(as.symbol(
        str_c("feature_imp_ridge_", dataset, "_ces1" ,collapse = "") ))  )
  
  acc_maccs<- return_acc_estimate_cv(
    target_tibble = target_source,
    predictors_tibble = eval(as.symbol(
        str_c("feature_maccs_", dataset,collapse = "") ))  ,
    similiarity = "tahimoto")
  
  acc_extended<- return_acc_estimate_cv(
    target_tibble = target_source,
    predictors_tibble = eval(as.symbol(
        str_c("feature_extended_", dataset,collapse = "") ))  ,
    similiarity = "tahimoto")
  
  acc_consensus <- return_acc_estimate_cv(
    target_tibble = target_source,
    predictors_tibble = eval(as.symbol(
        str_c("drug_consensus_", dataset,collapse = "") )) ) 
  
  acc_df <- acc_ces1 %>% mutate(method = "ces1") %>% 
      bind_rows(acc_ceres %>% mutate(method = "ceres")) %>% 
      bind_rows(acc_demeter2 %>% mutate(method = "demeter2")) %>% 
      bind_rows(acc_exp %>% mutate(method = "exp")) %>% 
      bind_rows(acc_extended %>% mutate(method = "structure_ECFP")) %>%
      bind_rows(acc_maccs %>% mutate(method = "structure_MACCS")) %>%
      bind_rows(acc_consensus %>% mutate(method = "Consensus_exp_perturb"))
  return(acc_df)
```


```{r}
acc_df %>% 
  group_by(method) %>% 
  summarise(acc_mean= mean(acc,na.rm = T))

acc_df %>% 
  ggplot(aes(x=method, y=acc)) + 
  geom_violin()+
  coord_flip()+
  theme_classic()

acc_df %>% 
  ggplot(aes(x=method, y=acc)) + 
  geom_boxplot()+
  coord_flip()+
  theme_classic()  

save.image("~/cluster_scratch/glmnet_modelling/target_pred_server/targetpred_ctrp_drugbank_5foldcv.RData")

acc_df %>% 
  filter(method %in% c("structure_MACCS", "structure_ECFP", "sen", "ces1", "Consensus_exp_perturb", "exp","ceres", "demeter2" )) %>% 
  ggplot(aes(x=method, y=acc)) +
  geom_boxplot()+
  coord_flip()+
  theme_classic() 
```


```{r,warning = FALSE, message=FALSE,eval= FALSE}
source('~/cluster_wrk/drug_moa/supervised_target_pred/return_acc_estimate_loocv.R')
set.seed(0000) 
acc_ces1 <- return_acc_estimate_loocv(
  target_tibble = ctrp_target_binary,
  predictors_tibble = feature_imp_ridge_ctrp_ces1 %>% rename(drug=broad_cpd_id) ) 

acc_ceres<- return_acc_estimate_loocv(
  target_tibble = target_tibble,
  predictors_tibble = feature_imp_ridge_ctrp_ceres %>% rename(drug=broad_cpd_id) ) 

acc_demeter2<- return_acc_estimate_loocv(
  target_tibble = target_tibble,
  predictors_tibble = feature_imp_ridge_ctrp_demeter2 %>% rename(drug=broad_cpd_id) ) 

acc_exp<- return_acc_estimate_loocv(
  target_tibble = target_tibble,
  predictors_tibble = feature_imp_ridge_ctrp_exp %>% rename(drug=broad_cpd_id) )

acc_maccs<- return_acc_estimate_loocv(
  target_tibble = target_tibble,
  cor_mat = maccs_cor )

acc_extended <- return_acc_estimate_loocv(
  target_tibble = target_tibble,
  cor_mat = extended_cor )

acc_consensus <- return_acc_estimate_loocv(
  target_tibble = target_tibble,
  predictors_tibble = drug_consensus %>% rename(drug=BROAD_ID) ) 



acc_df <- acc_ces1 %>% mutate(method = "ces1") %>% 
  bind_rows(acc_ces2 %>% mutate(method = "ces2")) %>% 
    bind_rows(acc_ceres %>% mutate(method = "ceres")) %>% 
    bind_rows(acc_demeter2 %>% mutate(method = "demeter2")) %>% 
    bind_rows(acc_sen %>% mutate(method = "sen")) %>% 
    bind_rows(acc_sen_ces1 %>% mutate(method = "ces1_sen")) %>% 
    bind_rows(acc_exp %>% mutate(method = "exp")) %>% 
    bind_rows(acc_sen_exp %>% mutate(method = "exp_sen")) %>% 
    bind_rows(acc_extended %>% mutate(method = "structure_ECFP")) %>% 
    bind_rows(acc_ces1_extended %>% mutate(method = "ces1_ECFP")) %>% 
    bind_rows(acc_ces1_extended_sen %>% mutate(method = "ces1_ECFP_sen")) %>% 
    bind_rows(acc_maccs %>% mutate(method = "structure_MACCS")) %>% 
    bind_rows(acc_ces1_maccs %>% mutate(method = "ces1_MACCS")) %>% 
    bind_rows(acc_ces1_maccs_sen %>% mutate(method = "ces1_MACCS_sen")) %>% 
    bind_rows(acc_consensus %>% mutate(method = "Consensus_exp_perturb")) 

acc_df %>% 
  group_by(method) %>% 
  summarise(acc_mean= mean(acc,na.rm = T))
  

acc_df %>% 
  ggplot(aes(x=method, y=acc)) + 
  geom_violin()+
  coord_flip()+
  theme_classic()

acc_df %>% 
  ggplot(aes(x=method, y=acc)) + 
  geom_boxplot()+
  coord_flip()+
  theme_classic()  

save.image("~/cluster_scratch/glmnet_modelling/target_pred_server/targetpred_ctrp_drugbank_loocv.RData")

```


how about gdsc
```{r}
source('~/cluster_wrk/drug_moa/supervised_target_pred/return_acc_estimate_5fold_cv.R')
set.seed(0000)
acc_ces1 <- return_acc_estimate_foldcv(
  target_tibble = gdsc_target_binary,
  predictors_tibble = feature_imp_ridge_gdsc_ces1 ) 

acc_ceres<- return_acc_estimate_foldcv(
  target_tibble = gdsc_target_binary,
  predictors_tibble = feature_imp_ridge_gdsc_ceres ) 

acc_demeter2<- return_acc_estimate_foldcv(
  target_tibble = gdsc_target_binary,
  predictors_tibble = feature_imp_ridge_gdsc_demeter2 ) 

acc_exp<- return_acc_estimate_foldcv(
  target_tibble = gdsc_target_binary,
  predictors_tibble = feature_imp_ridge_gdsc_exp )

acc_maccs<- return_acc_estimate_foldcv(
  target_tibble = gdsc_target_binary,
  predictors_tibble = feature_maccs_gdsc ,
  similiarity = "tahimoto")

acc_extended <- return_acc_estimate_foldcv(
  target_tibble = gdsc_target_binary,
  predictors_tibble = feature_extended_gdsc,
  similiarity = "tahimoto")

acc_consensus <- return_acc_estimate_foldcv(
  target_tibble = gdsc_target_binary,
  predictors_tibble = drug_consensus ) 


acc_df <- acc_ces1 %>% mutate(method = "ces1") %>% 
    bind_rows(acc_ceres %>% mutate(method = "ceres")) %>% 
    bind_rows(acc_demeter2 %>% mutate(method = "demeter2")) %>% 
    bind_rows(acc_exp %>% mutate(method = "exp")) %>% 
    bind_rows(acc_extended %>% mutate(method = "structure_ECFP")) %>%
    bind_rows(acc_maccs %>% mutate(method = "structure_MACCS")) %>%
    bind_rows(acc_consensus %>% mutate(method = "Consensus_exp_perturb")) 

acc_df %>% 
  group_by(method) %>% 
  summarise(acc_mean= mean(acc,na.rm = T))

acc_df %>% 
  ggplot(aes(x=method, y=acc)) + 
  geom_violin()+
  coord_flip()+
  theme_classic()

acc_df %>% 
  ggplot(aes(x=method, y=acc)) + 
  geom_boxplot()+
  coord_flip()+
  theme_classic()  

save.image("~/cluster_scratch/glmnet_modelling/target_pred_server/targetpred_ctrp_drugbank_5foldcv.RData")

acc_df %>% 
  filter(method %in% c("structure_MACCS", "structure_ECFP", "sen", "ces1", "Consensus_exp_perturb", "exp","ceres", "demeter2" )) %>% 
  ggplot(aes(x=method, y=acc)) +
  geom_boxplot()+
  coord_flip()+
  theme_classic() 
```



comparing performance of ces1 and consensus with same sample size
```{r}
overlapping_drugs = intersect(feature_imp_ridge_ctrp_ces1$broad_cpd_id, drug_consensus$BROAD_ID)
acc_ces1 <- return_acc_estimate_foldcv(
  target_tibble = target_tibble,
  predictors_tibble = feature_imp_ridge_ctrp_ces1 %>% 
    rename(drug=broad_cpd_id) %>% 
    filter(drug %in% overlapping_drugs) ) 

acc_sen <-  return_acc_estimate_foldcv(
  target_tibble = target_tibble,
  predictors_tibble = feature_sen_ctrp %>% 
    rename(drug=broad_cpd_id) %>% 
    filter(drug %in% overlapping_drugs) ) 

acc_consensus <- return_acc_estimate_foldcv(
  target_tibble = target_tibble,
  predictors_tibble = drug_consensus %>% 
    rename(drug=X1) %>% 
   filter(drug %in% overlapping_drugs) 
  ) 

acc_ces1_consensus <- return_acc_estimate_foldcv(
  target_tibble = target_tibble,
  predictors_tibble =  inner_join(
    x= feature_imp_ridge_ctrp_ces1 %>%     rename(drug=broad_cpd_id) ,
    y= drug_consensus %>%  rename_all( .funs = tolower) %>% rename(drug=BROAD_ID) ,
    by= "drug"
    ) 
  )

acc_sen_ces1 <- return_acc_estimate_foldcv(
  target_tibble = target_tibble,
  predictors_tibble = feature_sen_ces1_ctrp %>% rename(drug=broad_cpd_id) %>%  filter(drug %in% overlapping_drugs)  )



acc_sen_consensus <- return_acc_estimate_foldcv(
  target_tibble = target_tibble,
  predictors_tibble =   inner_join(
    x=  feature_sen_ctrp %>% 
    rename(drug=broad_cpd_id) %>% 
    filter(drug %in% overlapping_drugs),
    y= drug_consensus %>%  rename_all( .funs = tolower) %>% rename(drug=BROAD_ID) ,
    by= "drug"
    ) 
    
    )


acc_df <- acc_ces1 %>% mutate(method = "ces1") %>% 
    bind_rows(acc_sen %>% mutate(method = "sen")) %>% 
    bind_rows(acc_consensus %>% mutate(method = "Consensus_exp_perturb")) %>% 
    bind_rows(acc_ces1_consensus %>% mutate(method = "Consensusexp_ces1_perturb")) %>%
    bind_rows(acc_ces1_consensus %>% mutate(method = "Consensusexp_sen_perturb")) %>% 
    bind_rows(acc_sen_ces1 %>% mutate(method = "Consensusexp_sen_perturb"))   
  

acc_df %>% 
  group_by(method) %>% 
  summarise(acc_mean= mean(acc,na.rm = T))

acc_df %>% 
  ggplot(aes(x=method, y=acc)) + 
  geom_violin()+
  coord_flip()+
  theme_classic()

acc_df %>% 
  ggplot(aes(x=method, y=acc)) + 
  geom_boxplot()+
  coord_flip()+
  theme_classic()  

save.image("~/cluster_scratch/glmnet_modelling/target_pred_server/targetpred_ctrp_drugbank_5foldcv_183sample.RData")
```




## 4) Supervisied prediction with DTC target


```{r,warning = FALSE, message=FALSE}
target_tibble <- ctrp_target_dtc %>% 
  select(standard_inchi_key, gene_name, interaction_strength) %>%
  filter(interaction_strength!= 0) %>% 
  drop_na() %>% 
  group_by(standard_inchi_key, gene_name) %>% 
  summarize(interaction_strength= median(interaction_strength,na.rm = T)) %>% 
  ungroup() %>% 
  inner_join(ctrpv2_list_to_zia,by= c("standard_inchi_key"= "InChIKey")) %>% 
  select(broad_cpd_id, gene_name, interaction_strength) %>% 
  group_by(broad_cpd_id, gene_name) %>% 
  summarize(interaction_strength= max(interaction_strength,na.rm = T)) %>% 
  ungroup() %>%   rename(drug=broad_cpd_id, target_gene=gene_name, binding_score= interaction_strength) %>% 
  filter(binding_score>0.4) %>% 
    mutate(binding_score= 1)

# length(unique(target_tibble$drug))
```

fold cv
```{r,warning = FALSE, message=FALSE}
set.seed(1234)
acc_ces1 <- return_acc_estimate_foldcv(
  target_tibble = target_tibble,
  predictors_tibble = feature_imp_ridge_ctrp_ces1 %>% rename(drug=broad_cpd_id) ) 

acc_ces2<- return_acc_estimate_foldcv(
  target_tibble = target_tibble,
  predictors_tibble = feature_imp_ridge_ctrp_ces2 %>% rename(drug=broad_cpd_id) ) 


 
acc_ceres<- return_acc_estimate_foldcv(
  target_tibble = target_tibble,
  predictors_tibble = feature_imp_ridge_ctrp_ceres %>% rename(drug=broad_cpd_id) ) 



 
acc_demeter2<- return_acc_estimate_foldcv(
  target_tibble = target_tibble,
  predictors_tibble = feature_imp_ridge_ctrp_demeter2 %>% rename(drug=broad_cpd_id) ) 


 
acc_sen<- return_acc_estimate_foldcv(
  target_tibble = target_tibble,
  predictors_tibble = feature_sen_ctrp %>% rename(drug=broad_cpd_id) ) 



acc_sen_ces1 <- return_acc_estimate_foldcv(
  target_tibble = target_tibble,
  predictors_tibble = feature_sen_ces1_ctrp %>% rename(drug=broad_cpd_id) )

 
# acc_sen_ces1_1<- return_acc_estimate_foldcv(
#   target_tibble = target_tibble,
#   predictors_tibble = feature_sen_ces1_ctrp %>% rename(drug=broad_cpd_id) )

# 
#  
# acc_sen_ces1_2<- return_acc_estimate_foldcv(
#   target_tibble = target_tibble,
#   cor_mat = ces1_sen_cor)


acc_exp<- return_acc_estimate_foldcv(
  target_tibble = target_tibble,
  predictors_tibble = feature_imp_ridge_ctrp_exp %>% rename(drug=broad_cpd_id) )


acc_sen_exp <- return_acc_estimate_foldcv(
  target_tibble = target_tibble,
  predictors_tibble = feature_sen_exp_ctrp %>% rename(drug=broad_cpd_id) )

######################
acc_maccs<- return_acc_estimate_foldcv(
  target_tibble = target_tibble,
  cor_mat = maccs_cor )


acc_ces1_maccs <- return_acc_estimate_foldcv(
  target_tibble = target_tibble,
  cor_mat = ces1_maccs_cor ) 


acc_ces1_maccs_sen <- return_acc_estimate_foldcv(
  target_tibble = target_tibble,
  cor_mat = ces1_maccs_sen_cor )


#################
acc_extended <- return_acc_estimate_foldcv(
  target_tibble = target_tibble,
  cor_mat = extended_cor )


acc_ces1_extended <- return_acc_estimate_foldcv(
  target_tibble = target_tibble,
  cor_mat = ces1_extended_cor ) 


acc_ces1_extended_sen <- return_acc_estimate_foldcv(
  target_tibble = target_tibble,
  cor_mat = ces1_extended_sen_cor )

acc_consensus <- return_acc_estimate_foldcv(
   target_tibble = target_tibble,
   predictors_tibble = drug_consensus %>% rename(drug=BROAD_ID) ) 

acc_df <- acc_ces1 %>% mutate(method = "ces1") %>% 
  bind_rows(acc_ces2 %>% mutate(method = "ces2")) %>% 
    bind_rows(acc_ceres %>% mutate(method = "ceres")) %>% 
    bind_rows(acc_demeter2 %>% mutate(method = "demeter2")) %>% 
    bind_rows(acc_sen %>% mutate(method = "sen")) %>% 
    bind_rows(acc_sen_ces1 %>% mutate(method = "ces1_sen")) %>% 
    bind_rows(acc_exp %>% mutate(method = "exp")) %>% 
    bind_rows(acc_sen_exp %>% mutate(method = "exp_sen")) %>% 
    bind_rows(acc_extended %>% mutate(method = "structure_ECFP")) %>% 
    bind_rows(acc_ces1_extended %>% mutate(method = "ces1_ECFP")) %>% 
    bind_rows(acc_ces1_extended_sen %>% mutate(method = "ces1_ECFP_sen")) %>% 
    bind_rows(acc_maccs %>% mutate(method = "structure_MACCS")) %>% 
    bind_rows(acc_ces1_maccs %>% mutate(method = "ces1_MACCS")) %>% 
    bind_rows(acc_ces1_maccs_sen %>% mutate(method = "ces1_MACCS_sen")) %>% 
    bind_rows(acc_consensus %>% mutate(method = "Consensus_exp_perturb")) 

acc_df %>% 
  ggplot(aes(x=method, y=acc)) + 
  geom_violin()+
  coord_flip()+
  theme_classic()



acc_df %>% 
  ggplot(aes(x=method, y=acc)) + 
  geom_boxplot()+
  coord_flip()+
  theme_classic()  

acc_df %>% 
  filter(method %in% c("structure_MACCS", "structure_ECFP", "sen", "ces1", "Consensus_exp_perturb", "exp","ceres", "demeter2" )) %>% 
  ggplot(aes(x=method, y=acc)) +
  geom_boxplot()+
  coord_flip()+
  theme_classic() 

save.image("~/cluster_scratch/glmnet_modelling/target_pred_server/targetpred_ctrp_dtc_5foldcv.RData")
```

```{r}
overlapping_drugs = intersect(feature_imp_ridge_ctrp_ces1$broad_cpd_id, drug_consensus$BROAD_ID)
acc_ces1 <- return_acc_estimate_foldcv(
  target_tibble = target_tibble,
  predictors_tibble = feature_imp_ridge_ctrp_ces1 %>% 
    rename(drug=broad_cpd_id) %>% 
    filter(drug %in% overlapping_drugs) ) 

acc_sen <-  return_acc_estimate_foldcv(
  target_tibble = target_tibble,
  predictors_tibble = feature_sen_ctrp %>% 
    rename(drug=broad_cpd_id) %>% 
    filter(drug %in% overlapping_drugs) ) 

acc_consensus <- return_acc_estimate_foldcv(
  target_tibble = target_tibble,
  predictors_tibble = drug_consensus %>% 
    rename(drug=BROAD_ID) %>% 
   filter(drug %in% overlapping_drugs) 
  ) 

acc_ces1_consensus <- return_acc_estimate_foldcv(
  target_tibble = target_tibble,
  predictors_tibble =  inner_join(
    x= feature_imp_ridge_ctrp_ces1 %>%     rename(drug=broad_cpd_id) ,
    y= drug_consensus %>%  rename_all( .funs = tolower) %>% rename(drug=BROAD_ID) ,
    by= "drug"
    ) 
  )

acc_sen_ces1 <- return_acc_estimate_foldcv(
  target_tibble = target_tibble,
  predictors_tibble = feature_sen_ces1_ctrp %>% rename(drug=broad_cpd_id) %>%  filter(drug %in% overlapping_drugs)  )



acc_sen_consensus <- return_acc_estimate_foldcv(
  target_tibble = target_tibble,
  predictors_tibble =   inner_join(
    x=  feature_sen_ctrp %>% 
    rename(drug=broad_cpd_id) %>% 
    filter(drug %in% overlapping_drugs),
    y= drug_consensus %>%  rename_all( .funs = tolower) %>% rename(drug=BROAD_ID) ,
    by= "drug"
    ) 
    
    )


acc_df <- acc_ces1 %>% mutate(method = "ces1") %>% 
    bind_rows(acc_sen %>% mutate(method = "sen")) %>% 
    bind_rows(acc_consensus %>% mutate(method = "Consensus_exp_perturb")) %>% 
    bind_rows(acc_ces1_consensus %>% mutate(method = "Consensusexp_ces1_perturb")) %>%
    bind_rows(acc_ces1_consensus %>% mutate(method = "Consensusexp_sen_perturb")) %>% 
    bind_rows(acc_sen_ces1 %>% mutate(method = "Consensusexp_sen_perturb"))   
  

acc_df %>% 
  group_by(method) %>% 
  summarise(acc_mean= mean(acc,na.rm = T))

acc_df %>% 
  ggplot(aes(x=method, y=acc)) + 
  geom_violin()+
  coord_flip()+
  theme_classic()

acc_df %>% 
  ggplot(aes(x=method, y=acc)) + 
  geom_boxplot()+
  coord_flip()+
  theme_classic()  
```


loocv
```{r,warning = FALSE, message=FALSE}

target_tibble <- ctrp_target_dtc %>% 
  select(standard_inchi_key, gene_name, interaction_strength) %>%
  filter(interaction_strength!= 0) %>% 
  drop_na() %>% 
  group_by(standard_inchi_key, gene_name) %>% 
  summarize(interaction_strength= median(interaction_strength,na.rm = T)) %>% 
  ungroup() %>% 
  inner_join(ctrpv2_list_to_zia,by= c("standard_inchi_key"= "InChIKey")) %>% 
  select(broad_cpd_id, gene_name, interaction_strength) %>% 
  group_by(broad_cpd_id, gene_name) %>% 
  summarize(interaction_strength= max(interaction_strength,na.rm = T)) %>% 
  ungroup() %>%   rename(drug=broad_cpd_id, target_gene=gene_name, binding_score= interaction_strength) %>% 
  filter(binding_score>0.4) %>% 
    mutate(binding_score= 1)

# length(unique(target_tibble$drug)) 

set.seed(1234)
acc_ces1 <- return_acc_estimate_loocv(
  target_tibble = target_tibble,
  predictors_tibble = feature_imp_ridge_ctrp_ces1 %>% rename(drug=broad_cpd_id) ) 

acc_ces2<- return_acc_estimate_loocv(
  target_tibble = target_tibble,
  predictors_tibble = feature_imp_ridge_ctrp_ces2 %>% rename(drug=broad_cpd_id) ) 
mean(acc_ces2$acc) #0.84

 
acc_ceres<- return_acc_estimate_loocv(
  target_tibble = target_tibble,
  predictors_tibble = feature_imp_ridge_ctrp_ceres %>% rename(drug=broad_cpd_id) ) 
mean(acc_ceres$acc) #0.84


 
acc_demeter2<- return_acc_estimate_loocv(
  target_tibble = target_tibble,
  predictors_tibble = feature_imp_ridge_ctrp_demeter2 %>% rename(drug=broad_cpd_id) ) 
mean(acc_demeter2$acc) #0.84

 
acc_sen<- return_acc_estimate_loocv(
  target_tibble = target_tibble,
  predictors_tibble = feature_sen_ctrp %>% rename(drug=broad_cpd_id) ) 
mean(acc_sen$acc) 


acc_sen_ces1 <- return_acc_estimate_loocv(
  target_tibble = target_tibble,
  predictors_tibble = feature_sen_ces1_ctrp %>% rename(drug=broad_cpd_id) )
mean(acc_sen_ces1$acc) 
 
# acc_sen_ces1_1<- return_acc_estimate_loocv(
#   target_tibble = target_tibble,
#   predictors_tibble = feature_sen_ces1_ctrp %>% rename(drug=broad_cpd_id) )
# mean(acc_sen_ces1_1$acc) 
# 
#  
# acc_sen_ces1_2<- return_acc_estimate_loocv(
#   target_tibble = target_tibble,
#   cor_mat = ces1_sen_cor)
# mean(acc_sen_ces1_2$acc) 

acc_exp<- return_acc_estimate_loocv(
  target_tibble = target_tibble,
  predictors_tibble = feature_imp_ridge_ctrp_exp %>% rename(drug=broad_cpd_id) )
mean(acc_exp$acc) 

acc_sen_exp <- return_acc_estimate_loocv(
  target_tibble = target_tibble,
  predictors_tibble = feature_sen_exp_ctrp %>% rename(drug=broad_cpd_id) )

######################
acc_maccs<- return_acc_estimate_loocv(
  target_tibble = target_tibble,
  cor_mat = maccs_cor )
mean(acc_maccs$acc) 

acc_ces1_maccs <- return_acc_estimate_loocv(
  target_tibble = target_tibble,
  cor_mat = ces1_maccs_cor ) 
mean(acc_ces1_maccs$acc)

acc_ces1_maccs_sen <- return_acc_estimate_loocv(
  target_tibble = target_tibble,
  cor_mat = ces1_maccs_sen_cor )
mean(acc_ces1_maccs_sen$acc) 

#################
acc_extended <- return_acc_estimate_loocv(
  target_tibble = target_tibble,
  cor_mat = extended_cor )
mean(acc_extended$acc) 

acc_ces1_extended <- return_acc_estimate_loocv(
  target_tibble = target_tibble,
  cor_mat = ces1_extended_cor ) 
mean(acc_ces1_extended$acc)

acc_ces1_extended_sen <- return_acc_estimate_loocv(
  target_tibble = target_tibble,
  cor_mat = ces1_extended_sen_cor )
mean(acc_ces1_extended_sen$acc) 

acc_df <- acc_ces1 %>% mutate(method = "ces1") %>% 
  bind_rows(acc_ces2 %>% mutate(method = "ces2")) %>% 
    bind_rows(acc_ceres %>% mutate(method = "ceres")) %>% 
    bind_rows(acc_demeter2 %>% mutate(method = "demeter2")) %>% 
    bind_rows(acc_sen %>% mutate(method = "sen")) %>% 
    bind_rows(acc_sen_ces1 %>% mutate(method = "ces1_sen")) %>% 
    bind_rows(acc_exp %>% mutate(method = "exp")) %>% 
    bind_rows(acc_sen_exp %>% mutate(method = "exp_sen")) %>% 
    bind_rows(acc_extended %>% mutate(method = "structure_ECFP")) %>% 
    bind_rows(acc_ces1_extended %>% mutate(method = "ces1_ECFP")) %>% 
    bind_rows(acc_ces1_extended_sen %>% mutate(method = "ces1_ECFP_sen")) %>% 
    bind_rows(acc_maccs %>% mutate(method = "structure_MACCS")) %>% 
    bind_rows(acc_ces1_maccs %>% mutate(method = "ces1_MACCS")) %>% 
    bind_rows(acc_ces1_maccs_sen %>% mutate(method = "ces1_MACCS_sen")) 

acc_df %>% 
  ggplot(aes(x=method, y=acc)) + 
  geom_violin()+
  coord_flip()+
  theme_classic()

acc_df %>% 
  ggplot(aes(x=method, y=acc)) + 
  geom_boxplot()+
  coord_flip()+
  theme_classic()  

save.image("~/cluster_scratch/glmnet_modelling/target_pred_server/targetpred_ctrp_dtc_loocv.RData")
```


Check prediction performance Summary
```{r}
# load("~/cluster_scratch/glmnet_modelling/dtc_supervised_prediction.RData")
# mean(acc_ces1)
# mean(acc_ces2)
# mean(acc_ceres)
# mean(acc_demeter2)
# mean(acc_sen)
# mean(acc_sen_ces1)
# mean(acc_exp)
# mean(acc_sen_exp)
# 
# wilcox.test(acc_ces1, acc_ceres,paired = T)
# wilcox.test(acc_ces1, acc_ces2,paired = T)
# wilcox.test(acc_ces1, acc_demeter2,paired = T)
# 
# median(acc_ces1)
# median(acc_ces2)
# median(acc_ceres)
# median(acc_demeter2)
# median(acc_sen)
# median(acc_sen_ces1)
# median(acc_exp)
# median(acc_sen_exp)
```


## MOA 


## 5) Combine the result and plotting
```{r}
rm(list = ls())
load("~/cluster_scratch/glmnet_modelling/drugbank_supervised_prediction.RData")
acc_list <- ls()
acc_drugbank <- map_dfc(.x = acc_list,.f = get)
colnames(acc_drugbank) <- acc_list


load("~/cluster_scratch/glmnet_modelling/dtc_supervised_prediction.RData")
acc_dtc <- map_dfc(.x = acc_list,.f = get)
colnames(acc_dtc) <- acc_list

acc_supervised_target_pred <- bind_rows(
  acc_drugbank %>% 
    pivot_longer(cols= everything(),names_to = "method",values_to= "spearman_cor") %>%
    mutate(label_dataset= "drugbank")
  ,
  acc_dtc %>%
    pivot_longer(cols= everything(),names_to = "method",values_to= "spearman_cor") %>%
    mutate(label_dataset= "dtc")
)

acc_supervised_target_pred %>% 
  ggplot(aes(x= method, y = spearman_cor, fill= label_dataset)) +
  geom_boxplot()+
  theme_classic()


fig <- acc_supervised_target_pred %>% 
  ggplot(aes(fill= method,  x= label_dataset,y = spearman_cor)) +
  geom_boxplot(outlier.color = "white")+
  theme_classic()+
  scale_fill_discrete(name = "Predictor data type", labels = c("CERES","CES1","CES2", "DEMETER2", "Sensitivity", "Sensitivity+CES1", "Sensitivity+EXP", "EXP"))+
  xlab("Target resources" )+
  ylab("Prediction accuracy")
  
fig
```



```{r,fig.width=5, fig.height=2}
fig
```
```{r}
fig <- acc_supervised_target_pred %>% 
  filter(method %in% c("acc_ces1", "acc_sen", "acc_sen_ces1", "acc_exp", "acc_sen_exp")) %>% 
  ggplot(aes(fill= method,  x= label_dataset,y = spearman_cor)) +
  geom_boxplot(outlier.color = "white")+
  theme_classic()+
  scale_fill_discrete(name = "Predictor data type", labels = c("CES1","Sensitivity", "Sensitivity+CES1", "Sensitivity+EXP", "EXP"))+
  xlab("Target resources" )+
  ylab("Prediction accuracy")
  
```


```{r,fig.width=4, fig.height=2}
fig
```











## 6) further explore the prediction result.

drug category, Does perturbation data favor certain kind of drug comparing to chemical finger print?

Continues binding score and prediction scatter plot.


## 7)

Exploring whether similiarity matrix calculated on the ess signature is a better representation of drug target based similiarity matrix
```{r}
load("~/cluster_scratch/glmnet_modelling/target_pred_server/targetpred_serverinput.RData")

source('~/cluster_wrk/drug_moa/supervised_target_pred/get_target_matrix_from_long_target_tibble.R')

target_tibble_drugbank= ctrp_target_tibble %>%
  ungroup() %>%
  select(broad_cpd_id, gene_symbol_of_protein_target) %>%
  rename(drug=broad_cpd_id, target_gene=gene_symbol_of_protein_target) %>% 
  mutate(binding_score= 1)

target_tibble_dtc <- ctrp_target_dtc %>% 
  select(standard_inchi_key, gene_name, interaction_strength) %>%
  filter(interaction_strength!= 0) %>% 
  drop_na() %>% 
  group_by(standard_inchi_key, gene_name) %>% 
  summarize(interaction_strength= median(interaction_strength,na.rm = T)) %>% 
  ungroup() %>% 
  inner_join(ctrpv2_list_to_zia,by= c("standard_inchi_key"= "InChIKey")) %>% 
  select(broad_cpd_id, gene_name, interaction_strength) %>% 
  group_by(broad_cpd_id, gene_name) %>% 
  summarize(interaction_strength= max(interaction_strength,na.rm = T)) %>% 
  ungroup() %>%   rename(drug=broad_cpd_id, target_gene=gene_name, binding_score= interaction_strength) %>% 
  filter(binding_score>0.4) %>% 
    mutate(binding_score= 1)

target_mat_ctrp <- get_target_mat(target_tibble_drugbank)

target_mat_dtc <- get_target_mat(target_tibble_dtc)
```

```{r}
target_drugbank_cor <- t(target_mat_ctrp) %>% 
  prabclus::jaccard()

consensusexp_cor <- t(drug_consensus %>% filter(BROAD_ID %in% colnames(ces1_cor 
get_long_tibble_from_mat <- function(mat){
  tmp <- as_tibble(mat) %>% 
  mutate(drug1= colnames(mat)) %>% 
  pivot_longer(cols = - drug1,names_to= 'drug2', values_to='similiarity') %>% 
    distinct()
  return(tmp)
}





res <- get_long_tibble_from_mat(target_drugbank_cor) %>%
  rename(targetdrugbank_similiarity= similiarity) %>% 
  inner_join(get_long_tibble_from_mat(maccs_cor) %>% 
               rename(maccs_similiarity= similiarity)) %>% 
  inner_join(get_long_tibble_from_mat(ces1_cor) %>% 
                rename(ces1_similiarity= similiarity)) 

  # inner_join(get_long_tibble_from_mat(ces1_cor))   


cor(res$targetdrugbank_similiarity, res$maccs_similiarity,method = "spearman") #0.26

cor(res$targetdrugbank_similiarity, res$ces1_similiarity,method = "spearman")
#-0.48

res %>% 
  ggplot(mapping = aes(y= targetdrugbank_similiarity, x= maccs_similiarity)) +
  geom_point(size=0.1)


res %>% 
  ggplot(mapping = aes(y= targetdrugbank_similiarity, x= ces1_similiarity)) +
  geom_point(size=0.1)
```


