---
title: "Modelling output exploration Part2 drug target prediction"
author: "Wenyu"
date: "1/15/2021"
output: html_document
---

The aim of this nootbook is to explore whether the extracted model importances from the sen~ess glmnet model can be used in supervised drug target prediction



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(tidymodels)

```


## 1) Extract and reformat the feature importance from the glmnet model
```{r, eval= F}
#confirm whether the gene is matched
ces1 <- read_csv("~/cluster_scratch/impute_ess_20q4/ces1_478.csv")
load("~/cluster_scratch/glmnet_modelling_cluster/ridge_feature_multinode2.RData")

# extract the vector from the list from the list column and combine with 
# gene names and drug broad id into a square matrix. then perhaps transform to 
# long table for further exploration. 

gene <- sort(colnames(ces1)[2:10569])

# tmp <- tibble(gene)
# tmp <- map(res_feature$ces1_perf,function(x){bind_cols(tmp, tibble(x))} )
tmp <- matrix(nrow = 365,ncol = 10568)
colnames(tmp) <- gene
for (i in 1:365){
    tmp[i,] <- res_feature$ces1_perf[[i]]
}
feature_imp <- bind_cols(res_feature %>% select(broad_cpd_id), data.frame(tmp) %>% as_tibble()) 
write_csv(feature_imp,"~/cluster_scratch/glmnet_modelling/result_largevm/feature_imp_ridge_ctrp_ces1.csv")

for (i in 1:365){
    tmp[i,] <- res_feature$ces2_perf[[i]]
}
feature_imp <- bind_cols(res_feature %>% select(broad_cpd_id), data.frame(tmp) %>% as_tibble()) 
  
write_csv(feature_imp,"~/cluster_scratch/glmnet_modelling/result_largevm/feature_imp_ridge_ctrp_ces2.csv")

for (i in 1:365){
    tmp[i,] <- res_feature$ceres_perf[[i]]
}
feature_imp <- bind_cols(res_feature %>% select(broad_cpd_id), data.frame(tmp) %>% as_tibble()) 

write_csv(feature_imp,"~/cluster_scratch/glmnet_modelling/result_largevm/feature_imp_ridge_ctrp_ceres.csv")

for (i in 1:365){
    tmp[i,] <- res_feature$demeter2_perf[[i]]
}
feature_imp <- bind_cols(res_feature %>% select(broad_cpd_id), data.frame(tmp) %>% as_tibble()) 

write_csv(feature_imp,"~/cluster_scratch/glmnet_modelling/result_largevm/feature_imp_ridge_ctrp_demeter2.csv")


load("~/cluster_scratch/impute_and_derive_exp_based_feature_importance/res_feature_imp_expseq2.RData")
exp_seq_pca <- read_csv("~/cluster_scratch/impute_and_derive_exp_based_feature_importance/exp_seq_pca.csv")

gene <- sort(colnames(exp_seq_pca)[2:1204])
tmp <- matrix(nrow = 365,ncol = 1203)
colnames(tmp) <- gene

for (i in 1:365){
    tmp[i,] <- res_feature$exp_perf[[i]]
}
feature_imp <- bind_cols(res_feature %>% select(broad_cpd_id), data.frame(tmp) %>% as_tibble())

write_csv(feature_imp,"~/cluster_scratch/glmnet_modelling/result_largevm/feature_imp_ridge_ctrp_seq_pca.csv")
rm(list = ls())


```

## 2) Read in the data you write out by the previous chunk

read in all the needed csv file for drug target prediction using various predictors and then save an RData file as input for modelscript

```{r,warning = FALSE, message=FALSE}
feature_imp_ridge_ctrp_ces1 <- read_csv("~/cluster_scratch/glmnet_modelling/result_largevm/feature_imp_ridge_ctrp_ces1.csv")

feature_imp_ridge_ctrp_ces2 <- read_csv("~/cluster_scratch/glmnet_modelling/result_largevm/feature_imp_ridge_ctrp_ces2.csv")

feature_imp_ridge_ctrp_ceres <- read_csv("~/cluster_scratch/glmnet_modelling/result_largevm/feature_imp_ridge_ctrp_ceres.csv")

feature_imp_ridge_ctrp_demeter2 <- read_csv("~/cluster_scratch/glmnet_modelling/result_largevm/feature_imp_ridge_ctrp_demeter2.csv")

feature_sen_ctrp <- read_csv("~/cluster_scratch/impute_ctrp/ctrp_imputed.csv")

feature_imp_ridge_ctrp_seqpca <- read_csv("~/cluster_scratch/glmnet_modelling/result_largevm/feature_imp_ridge_ctrp_seq_pca.csv")

# update the analysis now (normalize the vector after merging)
feature_sen_ces1_ctrp <- inner_join(feature_imp_ridge_ctrp_ces1, feature_sen_ctrp,by = "broad_cpd_id") %>% 
  mutate_at(-1, .funs = scale )

feature_sen_seqpca_ctrp <- inner_join(feature_imp_ridge_ctrp_seqpca, feature_sen_ctrp,by = "broad_cpd_id") %>% 
    mutate_at(-1, .funs = scale )

ctrp_target_tibble <- read_csv("~/cluster_scratch/prior/target_long_ctrpv2.csv")
ctrpv2_list_to_zia <- read_csv("~/cluster_scratch/prior/ctrpv2_list_to_zia.csv")
ctrp_target_dtc <- read_csv("~/cluster_scratch/prior/ctrp_target_dtc.csv")

# generate cor martix directly based on fingerprint
feature_maccs_finger_print <- read_csv("~/cluster_scratch/fingerprints/maccs_finger.csv")
feature_extended_finger_print <- read_csv("~/cluster_scratch/fingerprints/extended_finger.csv")

extended_cor <- feature_extended_finger_print %>% 
  pivot_longer(cols = -broad_cpd_id,names_to= "name", values_to= "value") %>% 
  pivot_wider(id_cols = name, names_from= broad_cpd_id,  values_from= value) %>%
  arrange(name) %>% 
  select(-name) %>% 
  as.matrix() %>%
  prabclus::jaccard()
  # cor(method = "spearman")
  

# hist(extended_cor) 
# extended_cor1 <- (extended_cor - 0.5)* (-2)
# extended_cor1 <- -extended_cor + mean(extended_cor)
# hist(extended_cor1) 

maccs_cor <- feature_maccs_finger_print %>% 
  pivot_longer(cols = -broad_cpd_id,names_to= "name", values_to= "value") %>% 
  pivot_wider(id_cols = name, names_from= broad_cpd_id,  values_from= value) %>% 
  select(-name) %>% 
  as.matrix() %>% 
  prabclus::jaccard()
  # cor(method = "spearman")

# hist(maccs_cor)
# maccs_cor1 <- -maccs_cor + mean(maccs_cor)
# hist(maccs_cor1) 
# hist(sen_cor)
 
ces1_cor <- cor(t(
  x = feature_imp_ridge_ctrp_ces1 %>% 
    rename(drug=broad_cpd_id) %>% 
    arrange(drug) %>% 
    select(-drug) %>% 
    mutate_all(.funs = scale)), method = "spearman")
ces1_cor[ces1_cor<0] <- 0
colnames(ces1_cor) <- row.names(ces1_cor) <- sort(feature_imp_ridge_ctrp_ces1$broad_cpd_id)

sen_cor <- cor(t(
  x = feature_sen_ctrp %>% 
    rename(drug=broad_cpd_id) %>% 
    arrange(drug) %>% 
    select(-drug) %>% 
    mutate_all(.funs = scale)), method = "spearman")
sen_cor[sen_cor<0] <- 0
colnames(sen_cor) <- row.names(sen_cor) <- sort(feature_imp_ridge_ctrp_ces1$broad_cpd_id)


ces1_extended_cor <- (ces1_cor + extended_cor)/2
ces1_extended_sen_cor <- (ces1_cor + extended_cor+ sen_cor)/3
ces1_maccs_cor <- (ces1_cor + maccs_cor)/2
ces1_maccs_sen_cor <- (ces1_cor + maccs_cor+ sen_cor)/3

save.image("~/cluster_scratch/glmnet_modelling/target_pred_server/targetpred_serverinput.RData") 
  
```


how do we use the feature important to predict drug target?

lets form the supervised drug target prediction scenarios!

in the meantime we want to compare the 
1）signature based
2) sensitivity based prediction


lets use the existing target information of the
365 drugs to do cv and predict drug target

for these 365 drugs we will also drug sensitivities and drug consensus signatures from L1000, 
this should be quite easy. Lets aim at finishing these by tomorrow.

meanwhile I will collect the RNAseq data as basic entry for generating basal cell line info enhanced drug features.


lets build a pipeline first where a function can take a long target table, a prediction algorithm and a feature matrix to evaluate the predictability for that type of feature. 

The prediction algorithm will be based on dream challenge and performance is evaluated using cv.
We then consider again a nested cv to first find the thresholding parameters 

the central idea is to check what additional value can such basal cell info bring to MOA prediction in addition to the drug sensitivity and how does the accuracy comparing to, for example, chemical fingerprint based prediction?

## 3) Supervisied prediction with ctrpv2's own target info (from DrugBank)

```{r,warning = FALSE, message=FALSE,eval= FALSE}

# load("~/cluster_scratch/glmnet_modelling/target_pred_server/targetpred_serverinput.RData")
source('~/cluster_wrk/drug_moa/supervised_target_pred/no_tunning_weighted_averaging.R')
source('~/cluster_wrk/drug_moa/supervised_target_pred/return_acc_estimate_loocv.R')
source('~/cluster_wrk/drug_moa/supervised_target_pred/get_target_matrix_from_long_target_tibble.R')
target_tibble= ctrp_target_tibble %>%
  ungroup() %>%
  select(broad_cpd_id, gene_symbol_of_protein_target) %>%
  rename(drug=broad_cpd_id, target_gene=gene_symbol_of_protein_target) %>% 
  mutate(binding_score= 1)

set.seed(1234) 
acc_ces1 <- return_acc_estimate_loocv(
  target_tibble = target_tibble,
  predictors_tibble = feature_imp_ridge_ctrp_ces1 %>% rename(drug=broad_cpd_id) ) 

# acc_ces1_2 <- return_acc_estimate_loocv(
#   target_tibble = target_tibble,
#   cor_mat = ces1_cor1) 

acc_ces2<- return_acc_estimate_loocv(
  target_tibble = target_tibble,
  predictors_tibble = feature_imp_ridge_ctrp_ces2 %>% rename(drug=broad_cpd_id) ) 


acc_ceres<- return_acc_estimate_loocv(
  target_tibble = target_tibble,
  predictors_tibble = feature_imp_ridge_ctrp_ceres %>% rename(drug=broad_cpd_id) ) 


acc_demeter2<- return_acc_estimate_loocv(
  target_tibble = target_tibble,
  predictors_tibble = feature_imp_ridge_ctrp_demeter2 %>% rename(drug=broad_cpd_id) ) 

acc_sen<- return_acc_estimate_loocv(
  target_tibble = target_tibble,
  predictors_tibble = feature_sen_ctrp %>% rename(drug=broad_cpd_id) ) 

acc_sen_ces1 <- return_acc_estimate_loocv(
  target_tibble = target_tibble,
  predictors_tibble = feature_sen_ces1_ctrp %>% rename(drug=broad_cpd_id) )
 
# acc_sen_ces1_1<- return_acc_estimate_loocv(
#   target_tibble = target_tibble,
#   predictors_tibble = feature_sen_ces1_ctrp %>% rename(drug=broad_cpd_id) )
# mean(acc_sen_ces1_1$acc) 
# 
#  
# acc_sen_ces1_2<- return_acc_estimate_loocv(
#   target_tibble = target_tibble,
#   cor_mat = ces1_sen_cor)
# mean(acc_sen_ces1_2$acc) 

acc_seqpca<- return_acc_estimate_loocv(
  target_tibble = target_tibble,
  predictors_tibble = feature_imp_ridge_ctrp_seqpca %>% rename(drug=broad_cpd_id) )


acc_sen_seqpca <- return_acc_estimate_loocv(
  target_tibble = target_tibble,
  predictors_tibble = feature_sen_seqpca_ctrp %>% rename(drug=broad_cpd_id) )

######################
acc_maccs<- return_acc_estimate_loocv(
  target_tibble = target_tibble,
  cor_mat = maccs_cor )


acc_ces1_maccs <- return_acc_estimate_loocv(
  target_tibble = target_tibble,
  cor_mat = ces1_maccs_cor ) 


acc_ces1_maccs_sen <- return_acc_estimate_loocv(
  target_tibble = target_tibble,
  cor_mat = ces1_maccs_sen_cor )

#################
acc_extended <- return_acc_estimate_loocv(
  target_tibble = target_tibble,
  cor_mat = extended_cor )


acc_ces1_extended <- return_acc_estimate_loocv(
  target_tibble = target_tibble,
  cor_mat = ces1_extended_cor ) 


acc_ces1_extended_sen <- return_acc_estimate_loocv(
  target_tibble = target_tibble,
  cor_mat = ces1_extended_sen_cor )

acc_df <- acc_ces1 %>% mutate(method = "ces1") %>% 
  bind_rows(acc_ces2 %>% mutate(method = "ces2")) %>% 
    bind_rows(acc_ceres %>% mutate(method = "ceres")) %>% 
    bind_rows(acc_demeter2 %>% mutate(method = "demeter2")) %>% 
    bind_rows(acc_sen %>% mutate(method = "sen")) %>% 
    bind_rows(acc_sen_ces1 %>% mutate(method = "ces1_sen")) %>% 
    bind_rows(acc_seqpca %>% mutate(method = "seq")) %>% 
    bind_rows(acc_sen_seqpca %>% mutate(method = "seq_sen")) %>% 
    bind_rows(acc_extended %>% mutate(method = "structure_ECFP")) %>% 
    bind_rows(acc_ces1_extended %>% mutate(method = "ces1_ECFP")) %>% 
    bind_rows(acc_ces1_extended_sen %>% mutate(method = "ces1_ECFP_sen")) %>% 
    bind_rows(acc_maccs %>% mutate(method = "structure_MACCS")) %>% 
    bind_rows(acc_ces1_maccs %>% mutate(method = "ces1_MACCS")) %>% 
    bind_rows(acc_ces1_maccs_sen %>% mutate(method = "ces1_MACCS_sen")) 

acc_df %>% 
  group_by(method) %>% 
  summarise(acc_mean= mean(acc,na.rm = T))
  

acc_df %>% 
  ggplot(aes(x=method, y=acc)) + 
  geom_violin()+
  coord_flip()+
  theme_classic()

acc_df %>% 
  ggplot(aes(x=method, y=acc)) + 
  geom_boxplot()+
  coord_flip()+
  theme_classic()  

save.image("~/cluster_scratch/glmnet_modelling/target_pred_server/targetpred_ctrp_drugbank_loocv.RData")

```

lets try fold cv to see if we can finder a larger difference
```{r}
load("~/cluster_scratch/glmnet_modelling/target_pred_server/targetpred_serverinput.RData")
source('~/cluster_wrk/drug_moa/supervised_target_pred/no_tunning_weighted_averaging.R')
source('~/cluster_wrk/drug_moa/supervised_target_pred/return_acc_estimate_5fold_cv.R')
source('~/cluster_wrk/drug_moa/supervised_target_pred/get_target_matrix_from_long_target_tibble.R')
set.seed(1234)
acc_ces1 <- return_acc_estimate_foldcv(
  target_tibble = target_tibble,
  predictors_tibble = feature_imp_ridge_ctrp_ces1 %>% rename(drug=broad_cpd_id) ) 

acc_ces2<- return_acc_estimate_foldcv(
  target_tibble = target_tibble,
  predictors_tibble = feature_imp_ridge_ctrp_ces2 %>% rename(drug=broad_cpd_id) ) 
 
acc_ceres<- return_acc_estimate_foldcv(
  target_tibble = target_tibble,
  predictors_tibble = feature_imp_ridge_ctrp_ceres %>% rename(drug=broad_cpd_id) ) 

acc_demeter2<- return_acc_estimate_foldcv(
  target_tibble = target_tibble,
  predictors_tibble = feature_imp_ridge_ctrp_demeter2 %>% rename(drug=broad_cpd_id) ) 

acc_sen<- return_acc_estimate_foldcv(
  target_tibble = target_tibble,
  predictors_tibble = feature_sen_ctrp %>% rename(drug=broad_cpd_id) ) 

acc_sen_ces1 <- return_acc_estimate_foldcv(
  target_tibble = target_tibble,
  predictors_tibble = feature_sen_ces1_ctrp %>% rename(drug=broad_cpd_id) )

# acc_sen_ces1_1<- return_acc_estimate_foldcv(
#   target_tibble = target_tibble,
#   predictors_tibble = feature_sen_ces1_ctrp %>% rename(drug=broad_cpd_id) )
# mean(acc_sen_ces1_1$acc) 
# 
#  
# acc_sen_ces1_2<- return_acc_estimate_foldcv(
#   target_tibble = target_tibble,
#   cor_mat = ces1_sen_cor)
# mean(acc_sen_ces1_2$acc) 

acc_seqpca<- return_acc_estimate_foldcv(
  target_tibble = target_tibble,
  predictors_tibble = feature_imp_ridge_ctrp_seqpca %>% rename(drug=broad_cpd_id) )

acc_sen_seqpca <- return_acc_estimate_foldcv(
  target_tibble = target_tibble,
  predictors_tibble = feature_sen_seqpca_ctrp %>% rename(drug=broad_cpd_id) )

######################
acc_maccs<- return_acc_estimate_foldcv(
  target_tibble = target_tibble,
  cor_mat = maccs_cor )

acc_ces1_maccs <- return_acc_estimate_foldcv(
  target_tibble = target_tibble,
  cor_mat = ces1_maccs_cor ) 

acc_ces1_maccs_sen <- return_acc_estimate_foldcv(
  target_tibble = target_tibble,
  cor_mat = ces1_maccs_sen_cor )

#################
acc_extended <- return_acc_estimate_foldcv(
  target_tibble = target_tibble,
  cor_mat = extended_cor )

acc_ces1_extended <- return_acc_estimate_foldcv(
  target_tibble = target_tibble,
  cor_mat = ces1_extended_cor ) 

acc_ces1_extended_sen <- return_acc_estimate_foldcv(
  target_tibble = target_tibble,
  cor_mat = ces1_extended_sen_cor )

acc_df <- acc_ces1 %>% mutate(method = "ces1") %>% 
  bind_rows(acc_ces2 %>% mutate(method = "ces2")) %>% 
    bind_rows(acc_ceres %>% mutate(method = "ceres")) %>% 
    bind_rows(acc_demeter2 %>% mutate(method = "demeter2")) %>% 
    bind_rows(acc_sen %>% mutate(method = "sen")) %>% 
    bind_rows(acc_sen_ces1 %>% mutate(method = "ces1_sen")) %>% 
    bind_rows(acc_seqpca %>% mutate(method = "seq")) %>% 
    bind_rows(acc_sen_seqpca %>% mutate(method = "seq_sen")) %>% 
    bind_rows(acc_extended %>% mutate(method = "structure_ECFP")) %>% 
    bind_rows(acc_ces1_extended %>% mutate(method = "ces1_ECFP")) %>% 
    bind_rows(acc_ces1_extended_sen %>% mutate(method = "ces1_ECFP_sen")) %>% 
    bind_rows(acc_maccs %>% mutate(method = "structure_MACCS")) %>% 
    bind_rows(acc_ces1_maccs %>% mutate(method = "ces1_MACCS")) %>% 
    bind_rows(acc_ces1_maccs_sen %>% mutate(method = "ces1_MACCS_sen")) 

acc_df %>% 
  group_by(method) %>% 
  summarise(acc_mean= mean(acc,na.rm = T))

acc_df %>% 
  ggplot(aes(x=method, y=acc)) + 
  geom_violin()+
  coord_flip()+
  theme_classic()

acc_df %>% 
  ggplot(aes(x=method, y=acc)) + 
  geom_boxplot()+
  coord_flip()+
  theme_classic()  

save.image("~/cluster_scratch/glmnet_modelling/target_pred_server/targetpred_ctrp_drugbank_5foldcv.RData")

acc_df %>% 
  filter(method %in% c("structure_MACCS", "structure_ECFP", "sen", "ces1", "ces1_sen")) %>% 
  ggplot(aes(x=method, y=acc)) + 
  geom_boxplot()+
  coord_flip()+
  theme_classic()  
```





## 4) Supervisied prediction with DTC target


```{r,warning = FALSE, message=FALSE}
target_tibble <- ctrp_target_dtc %>% 
  select(standard_inchi_key, gene_name, interaction_strength) %>%
  filter(interaction_strength!= 0) %>% 
  drop_na() %>% 
  group_by(standard_inchi_key, gene_name) %>% 
  summarize(interaction_strength= median(interaction_strength,na.rm = T)) %>% 
  ungroup() %>% 
  inner_join(ctrpv2_list_to_zia,by= c("standard_inchi_key"= "InChIKey")) %>% 
  select(broad_cpd_id, gene_name, interaction_strength) %>% 
  group_by(broad_cpd_id, gene_name) %>% 
  summarize(interaction_strength= max(interaction_strength,na.rm = T)) %>% 
  ungroup() %>%   rename(drug=broad_cpd_id, target_gene=gene_name, binding_score= interaction_strength) %>% 
  filter(binding_score>0.4) %>% 
    mutate(binding_score= 1)

# length(unique(target_tibble$drug))
```

fold cv
```{r,warning = FALSE, message=FALSE}
set.seed(1234)
acc_ces1 <- return_acc_estimate_foldcv(
  target_tibble = target_tibble,
  predictors_tibble = feature_imp_ridge_ctrp_ces1 %>% rename(drug=broad_cpd_id) ) 

acc_ces2<- return_acc_estimate_foldcv(
  target_tibble = target_tibble,
  predictors_tibble = feature_imp_ridge_ctrp_ces2 %>% rename(drug=broad_cpd_id) ) 
mean(acc_ces2$acc) #0.84

 
acc_ceres<- return_acc_estimate_foldcv(
  target_tibble = target_tibble,
  predictors_tibble = feature_imp_ridge_ctrp_ceres %>% rename(drug=broad_cpd_id) ) 
mean(acc_ceres$acc) #0.84


 
acc_demeter2<- return_acc_estimate_foldcv(
  target_tibble = target_tibble,
  predictors_tibble = feature_imp_ridge_ctrp_demeter2 %>% rename(drug=broad_cpd_id) ) 
mean(acc_demeter2$acc) #0.84

 
acc_sen<- return_acc_estimate_foldcv(
  target_tibble = target_tibble,
  predictors_tibble = feature_sen_ctrp %>% rename(drug=broad_cpd_id) ) 
mean(acc_sen$acc) 


acc_sen_ces1 <- return_acc_estimate_foldcv(
  target_tibble = target_tibble,
  predictors_tibble = feature_sen_ces1_ctrp %>% rename(drug=broad_cpd_id) )
mean(acc_sen_ces1$acc) 
 
# acc_sen_ces1_1<- return_acc_estimate_foldcv(
#   target_tibble = target_tibble,
#   predictors_tibble = feature_sen_ces1_ctrp %>% rename(drug=broad_cpd_id) )
# mean(acc_sen_ces1_1$acc) 
# 
#  
# acc_sen_ces1_2<- return_acc_estimate_foldcv(
#   target_tibble = target_tibble,
#   cor_mat = ces1_sen_cor)
# mean(acc_sen_ces1_2$acc) 

acc_seqpca<- return_acc_estimate_foldcv(
  target_tibble = target_tibble,
  predictors_tibble = feature_imp_ridge_ctrp_seqpca %>% rename(drug=broad_cpd_id) )
mean(acc_seqpca$acc) 

acc_sen_seqpca <- return_acc_estimate_foldcv(
  target_tibble = target_tibble,
  predictors_tibble = feature_sen_seqpca_ctrp %>% rename(drug=broad_cpd_id) )

######################
acc_maccs<- return_acc_estimate_foldcv(
  target_tibble = target_tibble,
  cor_mat = maccs_cor )
mean(acc_maccs$acc) 

acc_ces1_maccs <- return_acc_estimate_foldcv(
  target_tibble = target_tibble,
  cor_mat = ces1_maccs_cor ) 
mean(acc_ces1_maccs$acc)

acc_ces1_maccs_sen <- return_acc_estimate_foldcv(
  target_tibble = target_tibble,
  cor_mat = ces1_maccs_sen_cor )
mean(acc_ces1_maccs_sen$acc) 

#################
acc_extended <- return_acc_estimate_foldcv(
  target_tibble = target_tibble,
  cor_mat = extended_cor )
mean(acc_extended$acc) 

acc_ces1_extended <- return_acc_estimate_foldcv(
  target_tibble = target_tibble,
  cor_mat = ces1_extended_cor ) 
mean(acc_ces1_extended$acc)

acc_ces1_extended_sen <- return_acc_estimate_foldcv(
  target_tibble = target_tibble,
  cor_mat = ces1_extended_sen_cor )
mean(acc_ces1_extended_sen$acc) 

acc_df <- acc_ces1 %>% mutate(method = "ces1") %>% 
  bind_rows(acc_ces2 %>% mutate(method = "ces2")) %>% 
    bind_rows(acc_ceres %>% mutate(method = "ceres")) %>% 
    bind_rows(acc_demeter2 %>% mutate(method = "demeter2")) %>% 
    bind_rows(acc_sen %>% mutate(method = "sen")) %>% 
    bind_rows(acc_sen_ces1 %>% mutate(method = "ces1_sen")) %>% 
    bind_rows(acc_seqpca %>% mutate(method = "seq")) %>% 
    bind_rows(acc_sen_seqpca %>% mutate(method = "seq_sen")) %>% 
    bind_rows(acc_extended %>% mutate(method = "structure_ECFP")) %>% 
    bind_rows(acc_ces1_extended %>% mutate(method = "ces1_ECFP")) %>% 
    bind_rows(acc_ces1_extended_sen %>% mutate(method = "ces1_ECFP_sen")) %>% 
    bind_rows(acc_maccs %>% mutate(method = "structure_MACCS")) %>% 
    bind_rows(acc_ces1_maccs %>% mutate(method = "ces1_MACCS")) %>% 
    bind_rows(acc_ces1_maccs_sen %>% mutate(method = "ces1_MACCS_sen")) 

acc_df %>% 
  ggplot(aes(x=method, y=acc)) + 
  geom_violin()+
  coord_flip()+
  theme_classic()



acc_df %>% 
  ggplot(aes(x=method, y=acc)) + 
  geom_boxplot()+
  coord_flip()+
  theme_classic()  

acc_df %>% 
  filter(method %in% c("structure_MACCS", "structure_ECFP", "sen", "ces1", "ces1_sen")) %>% 
  ggplot(aes(x=method, y=acc)) +
  geom_boxplot()+
  coord_flip()+
  theme_classic() 

save.image("~/cluster_scratch/glmnet_modelling/target_pred_server/targetpred_ctrp_dtc_5foldcv.RData")
```

loocv
```{r,warning = FALSE, message=FALSE}

target_tibble <- ctrp_target_dtc %>% 
  select(standard_inchi_key, gene_name, interaction_strength) %>%
  filter(interaction_strength!= 0) %>% 
  drop_na() %>% 
  group_by(standard_inchi_key, gene_name) %>% 
  summarize(interaction_strength= median(interaction_strength,na.rm = T)) %>% 
  ungroup() %>% 
  inner_join(ctrpv2_list_to_zia,by= c("standard_inchi_key"= "InChIKey")) %>% 
  select(broad_cpd_id, gene_name, interaction_strength) %>% 
  group_by(broad_cpd_id, gene_name) %>% 
  summarize(interaction_strength= max(interaction_strength,na.rm = T)) %>% 
  ungroup() %>%   rename(drug=broad_cpd_id, target_gene=gene_name, binding_score= interaction_strength) %>% 
  filter(binding_score>0.4) %>% 
    mutate(binding_score= 1)

# length(unique(target_tibble$drug)) 

set.seed(1234)
acc_ces1 <- return_acc_estimate_loocv(
  target_tibble = target_tibble,
  predictors_tibble = feature_imp_ridge_ctrp_ces1 %>% rename(drug=broad_cpd_id) ) 

acc_ces2<- return_acc_estimate_loocv(
  target_tibble = target_tibble,
  predictors_tibble = feature_imp_ridge_ctrp_ces2 %>% rename(drug=broad_cpd_id) ) 
mean(acc_ces2$acc) #0.84

 
acc_ceres<- return_acc_estimate_loocv(
  target_tibble = target_tibble,
  predictors_tibble = feature_imp_ridge_ctrp_ceres %>% rename(drug=broad_cpd_id) ) 
mean(acc_ceres$acc) #0.84


 
acc_demeter2<- return_acc_estimate_loocv(
  target_tibble = target_tibble,
  predictors_tibble = feature_imp_ridge_ctrp_demeter2 %>% rename(drug=broad_cpd_id) ) 
mean(acc_demeter2$acc) #0.84

 
acc_sen<- return_acc_estimate_loocv(
  target_tibble = target_tibble,
  predictors_tibble = feature_sen_ctrp %>% rename(drug=broad_cpd_id) ) 
mean(acc_sen$acc) 


acc_sen_ces1 <- return_acc_estimate_loocv(
  target_tibble = target_tibble,
  predictors_tibble = feature_sen_ces1_ctrp %>% rename(drug=broad_cpd_id) )
mean(acc_sen_ces1$acc) 
 
# acc_sen_ces1_1<- return_acc_estimate_loocv(
#   target_tibble = target_tibble,
#   predictors_tibble = feature_sen_ces1_ctrp %>% rename(drug=broad_cpd_id) )
# mean(acc_sen_ces1_1$acc) 
# 
#  
# acc_sen_ces1_2<- return_acc_estimate_loocv(
#   target_tibble = target_tibble,
#   cor_mat = ces1_sen_cor)
# mean(acc_sen_ces1_2$acc) 

acc_seqpca<- return_acc_estimate_loocv(
  target_tibble = target_tibble,
  predictors_tibble = feature_imp_ridge_ctrp_seqpca %>% rename(drug=broad_cpd_id) )
mean(acc_seqpca$acc) 

acc_sen_seqpca <- return_acc_estimate_loocv(
  target_tibble = target_tibble,
  predictors_tibble = feature_sen_seqpca_ctrp %>% rename(drug=broad_cpd_id) )

######################
acc_maccs<- return_acc_estimate_loocv(
  target_tibble = target_tibble,
  cor_mat = maccs_cor )
mean(acc_maccs$acc) 

acc_ces1_maccs <- return_acc_estimate_loocv(
  target_tibble = target_tibble,
  cor_mat = ces1_maccs_cor ) 
mean(acc_ces1_maccs$acc)

acc_ces1_maccs_sen <- return_acc_estimate_loocv(
  target_tibble = target_tibble,
  cor_mat = ces1_maccs_sen_cor )
mean(acc_ces1_maccs_sen$acc) 

#################
acc_extended <- return_acc_estimate_loocv(
  target_tibble = target_tibble,
  cor_mat = extended_cor )
mean(acc_extended$acc) 

acc_ces1_extended <- return_acc_estimate_loocv(
  target_tibble = target_tibble,
  cor_mat = ces1_extended_cor ) 
mean(acc_ces1_extended$acc)

acc_ces1_extended_sen <- return_acc_estimate_loocv(
  target_tibble = target_tibble,
  cor_mat = ces1_extended_sen_cor )
mean(acc_ces1_extended_sen$acc) 

acc_df <- acc_ces1 %>% mutate(method = "ces1") %>% 
  bind_rows(acc_ces2 %>% mutate(method = "ces2")) %>% 
    bind_rows(acc_ceres %>% mutate(method = "ceres")) %>% 
    bind_rows(acc_demeter2 %>% mutate(method = "demeter2")) %>% 
    bind_rows(acc_sen %>% mutate(method = "sen")) %>% 
    bind_rows(acc_sen_ces1 %>% mutate(method = "ces1_sen")) %>% 
    bind_rows(acc_seqpca %>% mutate(method = "seq")) %>% 
    bind_rows(acc_sen_seqpca %>% mutate(method = "seq_sen")) %>% 
    bind_rows(acc_extended %>% mutate(method = "structure_ECFP")) %>% 
    bind_rows(acc_ces1_extended %>% mutate(method = "ces1_ECFP")) %>% 
    bind_rows(acc_ces1_extended_sen %>% mutate(method = "ces1_ECFP_sen")) %>% 
    bind_rows(acc_maccs %>% mutate(method = "structure_MACCS")) %>% 
    bind_rows(acc_ces1_maccs %>% mutate(method = "ces1_MACCS")) %>% 
    bind_rows(acc_ces1_maccs_sen %>% mutate(method = "ces1_MACCS_sen")) 

acc_df %>% 
  ggplot(aes(x=method, y=acc)) + 
  geom_violin()+
  coord_flip()+
  theme_classic()

acc_df %>% 
  ggplot(aes(x=method, y=acc)) + 
  geom_boxplot()+
  coord_flip()+
  theme_classic()  

save.image("~/cluster_scratch/glmnet_modelling/target_pred_server/targetpred_ctrp_dtc_loocv.RData")
```


Check prediction performance Summary
```{r}
# load("~/cluster_scratch/glmnet_modelling/dtc_supervised_prediction.RData")
# mean(acc_ces1)
# mean(acc_ces2)
# mean(acc_ceres)
# mean(acc_demeter2)
# mean(acc_sen)
# mean(acc_sen_ces1)
# mean(acc_seqpca)
# mean(acc_sen_seqpca)
# 
# wilcox.test(acc_ces1, acc_ceres,paired = T)
# wilcox.test(acc_ces1, acc_ces2,paired = T)
# wilcox.test(acc_ces1, acc_demeter2,paired = T)
# 
# median(acc_ces1)
# median(acc_ces2)
# median(acc_ceres)
# median(acc_demeter2)
# median(acc_sen)
# median(acc_sen_ces1)
# median(acc_seqpca)
# median(acc_sen_seqpca)
```

## 5) Combine the result and plotting
```{r}
rm(list = ls())
load("~/cluster_scratch/glmnet_modelling/drugbank_supervised_prediction.RData")
acc_list <- ls()
acc_drugbank <- map_dfc(.x = acc_list,.f = get)
colnames(acc_drugbank) <- acc_list


load("~/cluster_scratch/glmnet_modelling/dtc_supervised_prediction.RData")
acc_dtc <- map_dfc(.x = acc_list,.f = get)
colnames(acc_dtc) <- acc_list

acc_supervised_target_pred <- bind_rows(
  acc_drugbank %>% 
    pivot_longer(cols= everything(),names_to = "method",values_to= "spearman_cor") %>%
    mutate(label_dataset= "drugbank")
  ,
  acc_dtc %>%
    pivot_longer(cols= everything(),names_to = "method",values_to= "spearman_cor") %>%
    mutate(label_dataset= "dtc")
)

acc_supervised_target_pred %>% 
  ggplot(aes(x= method, y = spearman_cor, fill= label_dataset)) +
  geom_boxplot()+
  theme_classic()


fig <- acc_supervised_target_pred %>% 
  ggplot(aes(fill= method,  x= label_dataset,y = spearman_cor)) +
  geom_boxplot(outlier.color = "white")+
  theme_classic()+
  scale_fill_discrete(name = "Predictor data type", labels = c("CERES","CES1","CES2", "DEMETER2", "Sensitivity", "Sensitivity+CES1", "Sensitivity+EXP", "EXP"))+
  xlab("Target resources" )+
  ylab("Prediction accuracy")
  
fig
```



```{r,fig.width=5, fig.height=2}
fig
```
```{r}
fig <- acc_supervised_target_pred %>% 
  filter(method %in% c("acc_ces1", "acc_sen", "acc_sen_ces1", "acc_seqpca", "acc_sen_seqpca")) %>% 
  ggplot(aes(fill= method,  x= label_dataset,y = spearman_cor)) +
  geom_boxplot(outlier.color = "white")+
  theme_classic()+
  scale_fill_discrete(name = "Predictor data type", labels = c("CES1","Sensitivity", "Sensitivity+CES1", "Sensitivity+EXP", "EXP"))+
  xlab("Target resources" )+
  ylab("Prediction accuracy")
  
```


```{r,fig.width=4, fig.height=2}
fig
```


```{r}

```









## 6)