---
title: "Modelling output exploration Part2 drug target prediction"
author: "Wenyu"
date: "1/15/2021"
output: html_document
---

The aim of this nootbook is to explore whether the extracted model importances from the sen~ess glmnet model can be used in supervised drug target prediction



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(tidymodels)

```


## 1) Extract and reformat the feature importance from the glmnet model
```{r, eval= F}
#confirm whether the gene is matched
ces1 <- read_csv("~/cluster_scratch/impute_ess_20q4/ces1_478.csv")
load("~/cluster_scratch/glmnet_modelling_cluster/ridge_feature_multinode2.RData")

# extract the vector from the list from the list column and combine with 
# gene names and drug broad id into a square matrix. then perhaps transform to 
# long table for further exploration. 

gene <- sort(colnames(ces1)[2:10569])

# tmp <- tibble(gene)
# tmp <- map(res_feature$ces1_perf,function(x){bind_cols(tmp, tibble(x))} )
tmp <- matrix(nrow = 365,ncol = 10568)
colnames(tmp) <- gene
for (i in 1:365){
    tmp[i,] <- res_feature$ces1_perf[[i]]
}
feature_imp <- bind_cols(res_feature %>% select(broad_cpd_id), data.frame(tmp) %>% as_tibble()) 
write_csv(feature_imp,"~/cluster_scratch/glmnet_modelling/result_largevm/feature_imp_ridge_ctrp_ces1.csv")

for (i in 1:365){
    tmp[i,] <- res_feature$ces2_perf[[i]]
}
feature_imp <- bind_cols(res_feature %>% select(broad_cpd_id), data.frame(tmp) %>% as_tibble()) 
  
write_csv(feature_imp,"~/cluster_scratch/glmnet_modelling/result_largevm/feature_imp_ridge_ctrp_ces2.csv")

for (i in 1:365){
    tmp[i,] <- res_feature$ceres_perf[[i]]
}
feature_imp <- bind_cols(res_feature %>% select(broad_cpd_id), data.frame(tmp) %>% as_tibble()) 

write_csv(feature_imp,"~/cluster_scratch/glmnet_modelling/result_largevm/feature_imp_ridge_ctrp_ceres.csv")

for (i in 1:365){
    tmp[i,] <- res_feature$demeter2_perf[[i]]
}
feature_imp <- bind_cols(res_feature %>% select(broad_cpd_id), data.frame(tmp) %>% as_tibble()) 

write_csv(feature_imp,"~/cluster_scratch/glmnet_modelling/result_largevm/feature_imp_ridge_ctrp_demeter2.csv")


load("~/cluster_scratch/impute_and_derive_exp_based_feature_importance/res_feature_imp_expseq2.RData")
exp_seq_pca <- read_csv("~/cluster_scratch/impute_and_derive_exp_based_feature_importance/exp_seq_pca.csv")

gene <- sort(colnames(exp_seq_pca)[2:1204])
tmp <- matrix(nrow = 365,ncol = 1203)
colnames(tmp) <- gene

for (i in 1:365){
    tmp[i,] <- res_feature$exp_perf[[i]]
}
feature_imp <- bind_cols(res_feature %>% select(broad_cpd_id), data.frame(tmp) %>% as_tibble())

write_csv(feature_imp,"~/cluster_scratch/glmnet_modelling/result_largevm/feature_imp_ridge_ctrp_seq_pca.csv")
rm(list = ls())


```

## 2) Read in the data you write out by the previous chunk

read in all the needed csv file for drug target prediction using various predictors and then save an RData file as input for modelscript

```{r,warning = FALSE, message=FALSE}
feature_imp_ridge_ctrp_ces1 <- read_csv("~/cluster_scratch/glmnet_modelling/result_largevm/feature_imp_ridge_ctrp_ces1.csv")

feature_imp_ridge_ctrp_ces2 <- read_csv("~/cluster_scratch/glmnet_modelling/result_largevm/feature_imp_ridge_ctrp_ces2.csv")

feature_imp_ridge_ctrp_ceres <- read_csv("~/cluster_scratch/glmnet_modelling/result_largevm/feature_imp_ridge_ctrp_ceres.csv")

feature_imp_ridge_ctrp_demeter2 <- read_csv("~/cluster_scratch/glmnet_modelling/result_largevm/feature_imp_ridge_ctrp_demeter2.csv")

feature_sen_ctrp <- read_csv("~/cluster_scratch/impute_ctrp/ctrp_imputed.csv")

feature_imp_ridge_ctrp_seqpca <- read_csv("~/cluster_scratch/glmnet_modelling/result_largevm/feature_imp_ridge_ctrp_seq_pca.csv")


# update the analysis now (normalize the vector after merging)
feature_sen_ces1_ctrp <- inner_join(feature_imp_ridge_ctrp_ces1, feature_sen_ctrp,by = "broad_cpd_id") %>% 
  mutate_at(-1, .funs = scale )

feature_sen_seqpca_ctrp <- inner_join(feature_imp_ridge_ctrp_seqpca, feature_sen_ctrp,by = "broad_cpd_id") %>% 
    mutate_at(-1, .funs = scale )



ctrp_target_tibble <- read_csv("~/cluster_scratch/prior/target_long_ctrpv2.csv")
ctrpv2_list_to_zia <- read_csv("~/cluster_scratch/prior/ctrpv2_list_to_zia.csv")
ctrp_target_dtc <- read_csv("~/cluster_scratch/prior/ctrp_target_dtc.csv")



# generate cor martix directly based on fingerprint
feature_maccs_finger_print <- read_csv("~/cluster_scratch/fingerprints/maccs_finger.csv")
feature_extended_finger_print <- read_csv("~/cluster_scratch/fingerprints/extended_finger.csv")

# maccs_cor <- feature_maccs_finger_print %>% 
#   pivot_longer(cols = -broad_cpd_id,names_to= "name", values_to= "value") %>% 
#   pivot_wider(id_cols = name, names_from= broad_cpd_id,  values_from= value) %>% 
#   select(-name) %>% 
#   as.matrix() %>% 
#   prabclus::jaccard()

extended_cor <- feature_extended_finger_print %>% 
  pivot_longer(cols = -broad_cpd_id,names_to= "name", values_to= "value") %>% 
  pivot_wider(id_cols = name, names_from= broad_cpd_id,  values_from= value) %>% 
  select(-name) %>% 
  as.matrix() %>% 
  prabclus::jaccard()

# hist(extended_cor) 
# extended_cor1 <- (extended_cor - 0.5)* (-2)
# extended_cor1 <- -extended_cor + mean(extended_cor)
# hist(extended_cor1) 

maccs_cor <- feature_maccs_finger_print %>% 
  pivot_longer(cols = -broad_cpd_id,names_to= "name", values_to= "value") %>% 
  pivot_wider(id_cols = name, names_from= broad_cpd_id,  values_from= value) %>% 
  select(-name) %>% 
  as.matrix() %>% 
  prabclus::jaccard()


# hist(maccs_cor)
# maccs_cor1 <- -maccs_cor + mean(maccs_cor)
# hist(maccs_cor1) 
# hist(sen_cor)

ces1_cor <- cor(t(
  x = feature_imp_ridge_ctrp_ces1 %>% 
    rename(drug=broad_cpd_id) %>% 
    arrange(drug) %>% 
    select(-drug) %>% 
    mutate_all(.funs = scale)))

colnames(ces1_cor) <- row.names(ces1_cor) <- sort(feature_imp_ridge_ctrp_ces1$broad_cpd_id)
sen_cor <- cor(t(
  x = feature_sen_ctrp %>% 
    rename(drug=broad_cpd_id) %>% 
    arrange(drug) %>% 
    select(-drug) %>% 
    mutate_all(.funs = scale)))


# ces1_sen_cor <- (ces1_cor + sen_cor)/2

ces1_extended_cor <- (ces1_cor + extended_cor)/2
ces1_extended_sen_cor <- (ces1_cor + extended_cor+ sen_cor)/3
ces1_maccs_cor <- (ces1_cor + maccs_cor)/2
ces1_maccs_sen_cor <- (ces1_cor + maccs_cor+ sen_cor)/3

# hist(ces1_maccs_sen_cor)
# ces1_cor1 <- apply(ces1_cor, 1, function(vec){
#   vec[vec < mean(vec)+ sd(vec)] <- 0
#   return(vec)
# 
# } )

# colnames(ces1_cor) <- row.names(ces1_cor) <- sort(feature_imp_ridge_ctrp_ces1$broad_cpd_id)
# 
# colnames(ces1_cor1) <- row.names(ces1_cor1)  <- sort(feature_imp_ridge_ctrp_ces1$broad_cpd_id)
save.image("~/cluster_scratch/glmnet_modelling/target_pred_server/targetpred_serverinput.RData") 
  
```


```{r}
# a= rnorm(n = 100,mean = 0,sd = 1)
# b= rnorm(n = 100,mean = 0,sd = 1)
# 
# c1 = a + 3*b
# c2= 2*a + 2*b 
# c3 = 3*a + b 
# c4 = (2*a + 3*b)*10 



```


how do we use the feature important to predict drug target?

lets form the supervised drug target prediction scenarios!

in the meantime we want to compare the 
1）signature based
2) sensitivity based prediction


lets use the existing target information of the
365 drugs to do cv and predict drug target

for these 365 drugs we will also drug sensitivities and drug consensus signatures from L1000, 
this should be quite easy. Lets aim at finishing these by tomorrow.

meanwhile I will collect the RNAseq data as basic entry for generating basal cell line info enhanced drug features.


lets build a pipeline first where a function can take a long target table, a prediction algorithm and a feature matrix to evaluate the predictability for that type of feature. 

The prediction algorithm will be based on dream challenge and performance is evaluated using cv.
We then consider again a nested cv to first find the thresholding parameters 

the central idea is to check what additional value can such basal cell info bring to MOA prediction in addition to the drug sensitivity and how does the accuracy comparing to, for example, chemical fingerprint based prediction?

## 3) Supervisied prediction with ctrpv2's own target info (from DrugBank)

```{r,warning = FALSE, message=FALSE,eval= FALSE}
source('~/cluster_wrk/drug_moa/supervised_target_pred/no_tunning_weighted_averaging_predicting.R')
source('~/cluster_wrk/drug_moa/supervised_target_pred/return_acc_estimate_loocv.R')
source('~/cluster_wrk/drug_moa/supervised_target_pred/get_target_matrix_from_long_target_tibble.R')
# load("~/cluster_scratch/glmnet_modelling/target_pred_server/targetpred_serverinput.RData")
target_tibble= ctrp_target_tibble %>%
  ungroup() %>%
  select(broad_cpd_id, gene_symbol_of_protein_target) %>%
  rename(drug=broad_cpd_id, target_gene=gene_symbol_of_protein_target) %>% 
  mutate(binding_score= 1)

 
acc_ces1 <- return_acc_estimate_loocv(
  target_tibble = target_tibble,
  predictors_tibble = feature_imp_ridge_ctrp_ces1 %>% rename(drug=broad_cpd_id) ) 
mean(acc_ces1$acc) # 0.8796417

#  
# acc_ces1_2 <- return_acc_estimate_loocv(
#   target_tibble = target_tibble,
#   cor_mat = ces1_cor1) 

acc_ces2<- return_acc_estimate_loocv(
  target_tibble = target_tibble,
  predictors_tibble = feature_imp_ridge_ctrp_ces2 %>% rename(drug=broad_cpd_id) ) 
mean(acc_ces2$acc) #0.84

 
acc_ceres<- return_acc_estimate_loocv(
  target_tibble = target_tibble,
  predictors_tibble = feature_imp_ridge_ctrp_ceres %>% rename(drug=broad_cpd_id) ) 
mean(acc_ceres$acc) #0.84


 
acc_demeter2<- return_acc_estimate_loocv(
  target_tibble = target_tibble,
  predictors_tibble = feature_imp_ridge_ctrp_demeter2 %>% rename(drug=broad_cpd_id) ) 
mean(acc_demeter2$acc) #0.84

 
acc_sen<- return_acc_estimate_loocv(
  target_tibble = target_tibble,
  predictors_tibble = feature_sen_ctrp %>% rename(drug=broad_cpd_id) ) 
mean(acc_sen$acc) 


acc_sen_ces1 <- return_acc_estimate_loocv(
  target_tibble = target_tibble,
  predictors_tibble = feature_sen_ces1_ctrp %>% rename(drug=broad_cpd_id) )
mean(acc_sen_ces1$acc) 
 
# acc_sen_ces1_1<- return_acc_estimate_loocv(
#   target_tibble = target_tibble,
#   predictors_tibble = feature_sen_ces1_ctrp %>% rename(drug=broad_cpd_id) )
# mean(acc_sen_ces1_1$acc) 
# 
#  
# acc_sen_ces1_2<- return_acc_estimate_loocv(
#   target_tibble = target_tibble,
#   cor_mat = ces1_sen_cor)
# mean(acc_sen_ces1_2$acc) 

acc_seqpca<- return_acc_estimate_loocv(
  target_tibble = target_tibble,
  predictors_tibble = feature_imp_ridge_ctrp_seqpca %>% rename(drug=broad_cpd_id) )
mean(acc_seqpca$acc) 

acc_sen_seqpca <- return_acc_estimate_loocv(
  target_tibble = target_tibble,
  predictors_tibble = feature_sen_seqpca_ctrp %>% rename(drug=broad_cpd_id) )

######################
acc_maccs<- return_acc_estimate_loocv(
  target_tibble = target_tibble,
  cor_mat = maccs_cor )
mean(acc_maccs$acc) 

acc_ces1_maccs <- return_acc_estimate_loocv(
  target_tibble = target_tibble,
  cor_mat = ces1_maccs_cor ) 
mean(acc_ces1_maccs$acc)

acc_ces1_maccs_sen <- return_acc_estimate_loocv(
  target_tibble = target_tibble,
  cor_mat = ces1_maccs_sen_cor )
mean(acc_ces1_maccs_sen$acc) 

#################
acc_extended <- return_acc_estimate_loocv(
  target_tibble = target_tibble,
  cor_mat = extended_cor )
mean(acc_extended$acc) 

acc_ces1_extended <- return_acc_estimate_loocv(
  target_tibble = target_tibble,
  cor_mat = ces1_extended_cor ) 
mean(acc_ces1_extended$acc)

acc_ces1_extended_sen <- return_acc_estimate_loocv(
  target_tibble = target_tibble,
  cor_mat = ces1_extended_sen_cor )
mean(acc_ces1_extended_sen$acc) 
# 
# save(
#   list = c("acc_ces1","acc_ces2","acc_ceres","acc_demeter2","acc_sen","acc_sen_ces1","acc_seqpca","acc_sen_seqpca"),
#   file = "~/cluster_scratch/glmnet_modelling/drugbank_supervised_prediction_ridge.RData"
#   )

save.image("~/cluster_scratch/glmnet_modelling/target_pred_server/targetpred_loocv.RData") 

```

Check prediction performance Summary
```{r,warning = FALSE, message=FALSE}
# load("~/cluster_scratch/glmnet_modelling/drugbank_supervised_prediction.RData")
median(acc_ces1$acc)
median(acc_ces2$acc)
median(acc_ceres$acc)
median(acc_demeter2$acc)

median(acc_sen$acc)
median(acc_sen_ces1$acc)

median(acc_seqpca$acc)
median(acc_sen_seqpca$acc)

median(acc_maccs$acc)
median(acc_ces1_maccs$acc)
median(acc_ces1_maccs_sen$acc)

median(acc_extended$acc)
median(acc_ces1_extended$acc)
median(acc_ces1_extended_sen$acc)

median(acc_ces1$acc)
median(acc_ces2$acc)
median(acc_ceres$acc)
median(acc_demeter2$acc)

median(acc_sen$acc)
median(acc_sen_ces1$acc)

median(acc_seqpca$acc)
median(acc_sen_seqpca$acc)

median(acc_maccs$acc)
median(acc_ces1_maccs$acc)
median(acc_ces1_maccs_sen$acc)

median(acc_extended$acc)
median(acc_ces1_extended$acc)
median(acc_ces1_extended_sen$acc)


acc_df <- acc_ces1 %>% mutate(method = "ces1") %>% 
  bind_rows(acc_ces2 %>% mutate(method = "ces2")) %>% 
    bind_rows(acc_ceres %>% mutate(method = "ceres")) %>% 
    bind_rows(acc_demeter2 %>% mutate(method = "demeter2")) %>% 
    bind_rows(acc_sen %>% mutate(method = "sen")) %>% 
    bind_rows(acc_sen_ces1 %>% mutate(method = "ces1_sen")) %>% 
    bind_rows(acc_seqpca %>% mutate(method = "seq")) %>% 
    bind_rows(acc_sen_seqpca %>% mutate(method = "seq_sen")) %>% 
    bind_rows(acc_extended %>% mutate(method = "structure_ECFP")) %>% 
    bind_rows(acc_ces1_extended %>% mutate(method = "ces1_ECFP")) %>% 
    bind_rows(acc_ces1_extended_sen %>% mutate(method = "ces1_ECFP_sen")) %>% 
    bind_rows(acc_maccs %>% mutate(method = "structure_MACCS")) %>% 
    bind_rows(acc_ces1_maccs %>% mutate(method = "ces1_MACCS")) %>% 
    bind_rows(acc_ces1_maccs_sen %>% mutate(method = "ces1_MACCS_sen")) 

acc_df %>% 
  group_by(method) %>% 
  summarise(acc_mean= mean(acc,na.rm = T))
  

acc_df %>% 
  ggplot(aes(x=method, y=acc)) + 
  geom_violin()+
  coord_flip()+
  theme_classic()

acc_df %>% 
  ggplot(aes(x=method, y=acc)) + 
  geom_boxplot()+
  coord_flip()+
  theme_classic()  

# wilcox.test(acc_ces1, acc_ceres,paired = T)
```

lets try 3fold cv
```{r}

```





## 4) Supervisied prediction with DTC target
redo the calculation given above
```{r,warning = FALSE, message=FALSE}

target_tibble <- ctrp_target_dtc %>% 
  select(standard_inchi_key, gene_name, interaction_strength) %>%
  filter(interaction_strength!= 0) %>% 
  drop_na() %>% 
  group_by(standard_inchi_key, gene_name) %>% 
  summarize(interaction_strength= median(interaction_strength,na.rm = T)) %>% 
  ungroup() %>% 
  inner_join(ctrpv2_list_to_zia,by= c("standard_inchi_key"= "InChIKey")) %>% 
  select(broad_cpd_id, gene_name, interaction_strength) %>% 
  group_by(broad_cpd_id, gene_name) %>% 
  summarize(interaction_strength= median(interaction_strength,na.rm = T)) %>% 
  ungroup() %>%   rename(drug=broad_cpd_id, target_gene=gene_name, binding_score= interaction_strength) 

length(unique(target_tibble$drug)) 

set.seed(0000)
acc_ces1 <- return_target_supervised_similiarity_prediction_acc(
  target_tibble = target_tibble,
  predictors_tibble = feature_imp_glmnet_ctrp_ces1 %>% rename(drug=broad_cpd_id) ) 

set.seed(0000)
acc_ces2<- return_target_supervised_similiarity_prediction_acc(
  target_tibble = target_tibble,
  predictors_tibble = feature_imp_glmnet_ctrp_ces2 %>% rename(drug=broad_cpd_id) ) 

set.seed(0000)
acc_ceres<- return_target_supervised_similiarity_prediction_acc(
  target_tibble = target_tibble,
  predictors_tibble = feature_imp_glmnet_ctrp_ceres %>% rename(drug=broad_cpd_id) ) 

set.seed(0000)
acc_demeter2<- return_target_supervised_similiarity_prediction_acc(
  target_tibble = target_tibble,
  predictors_tibble = feature_imp_glmnet_ctrp_demeter2 %>% rename(drug=broad_cpd_id) ) 

set.seed(0000)
acc_sen<- return_target_supervised_similiarity_prediction_acc(
  target_tibble = target_tibble,
  predictors_tibble = feature_sen_ctrp %>% rename(drug=broad_cpd_id) ) 

set.seed(0000)
acc_sen_ces1 <- return_target_supervised_similiarity_prediction_acc(
  target_tibble = target_tibble,
  predictors_tibble = feature_sen_ces1_ctrp %>% rename(drug=broad_cpd_id) )

set.seed(0000)
acc_seqpca <- return_target_supervised_similiarity_prediction_acc(
  target_tibble = target_tibble,
  predictors_tibble = feature_imp_glmnet_seq_pca %>% rename(drug=broad_cpd_id) )

set.seed(0000)
acc_sen_seqpca <- return_target_supervised_similiarity_prediction_acc(
  target_tibble = target_tibble,
  predictors_tibble = feature_sen_seqpca_ctrp %>% rename(drug=broad_cpd_id) )
save(
  list = c("acc_ces1","acc_ces2","acc_ceres","acc_demeter2","acc_sen","acc_sen_ces1","acc_seqpca","acc_sen_seqpca"),
  file = "~/cluster_scratch/glmnet_modelling/dtc_supervised_prediction.RData"
  )
```

Check prediction performance Summary
```{r}
load("~/cluster_scratch/glmnet_modelling/dtc_supervised_prediction.RData")
mean(acc_ces1)
mean(acc_ces2)
mean(acc_ceres)
mean(acc_demeter2)
mean(acc_sen)
mean(acc_sen_ces1)
mean(acc_seqpca)
mean(acc_sen_seqpca)

wilcox.test(acc_ces1, acc_ceres,paired = T)
wilcox.test(acc_ces1, acc_ces2,paired = T)
wilcox.test(acc_ces1, acc_demeter2,paired = T)

median(acc_ces1)
median(acc_ces2)
median(acc_ceres)
median(acc_demeter2)
median(acc_sen)
median(acc_sen_ces1)
median(acc_seqpca)
median(acc_sen_seqpca)
```

## 5) Combine the result and plotting
```{r}
rm(list = ls())
load("~/cluster_scratch/glmnet_modelling/drugbank_supervised_prediction.RData")
acc_list <- ls()
acc_drugbank <- map_dfc(.x = acc_list,.f = get)
colnames(acc_drugbank) <- acc_list


load("~/cluster_scratch/glmnet_modelling/dtc_supervised_prediction.RData")
acc_dtc <- map_dfc(.x = acc_list,.f = get)
colnames(acc_dtc) <- acc_list

acc_supervised_target_pred <- bind_rows(
  acc_drugbank %>% 
    pivot_longer(cols= everything(),names_to = "method",values_to= "spearman_cor") %>%
    mutate(label_dataset= "drugbank")
  ,
  acc_dtc %>%
    pivot_longer(cols= everything(),names_to = "method",values_to= "spearman_cor") %>%
    mutate(label_dataset= "dtc")
)

acc_supervised_target_pred %>% 
  ggplot(aes(x= method, y = spearman_cor, fill= label_dataset)) +
  geom_boxplot()+
  theme_classic()


fig <- acc_supervised_target_pred %>% 
  ggplot(aes(fill= method,  x= label_dataset,y = spearman_cor)) +
  geom_boxplot(outlier.color = "white")+
  theme_classic()+
  scale_fill_discrete(name = "Predictor data type", labels = c("CERES","CES1","CES2", "DEMETER2", "Sensitivity", "Sensitivity+CES1", "Sensitivity+EXP", "EXP"))+
  xlab("Target resources" )+
  ylab("Prediction accuracy")
  
fig
```



```{r,fig.width=5, fig.height=2}
fig
```
```{r}
fig <- acc_supervised_target_pred %>% 
  filter(method %in% c("acc_ces1", "acc_sen", "acc_sen_ces1", "acc_seqpca", "acc_sen_seqpca")) %>% 
  ggplot(aes(fill= method,  x= label_dataset,y = spearman_cor)) +
  geom_boxplot(outlier.color = "white")+
  theme_classic()+
  scale_fill_discrete(name = "Predictor data type", labels = c("CES1","Sensitivity", "Sensitivity+CES1", "Sensitivity+EXP", "EXP"))+
  xlab("Target resources" )+
  ylab("Prediction accuracy")
  
```


```{r,fig.width=4, fig.height=2}
fig
```


```{r}

```




