---
title: "Gene essentiality signatures help target prediction for the PRISM drugs"
author: "Wenyu"
date: "1/15/2023"
output: html_document
---

This notebook explores the application of essentiality signaturing method for drug mechanism study for the PRISM drug sensitivity dataset.Rendering the notebook with pre-computed input takes around 90 seconds.

```{r setup}
knitr::opts_chunk$set(echo = TRUE,warning=FALSE, error=FALSE)
library(tidyverse)
library(ggsci)
```

# 1 Lacking of drug target annotation for PRISM repurposable screening library
collect the screening drug and their target as well as additional annotation (clinical stage) for plotting

```{r}
prism_drugs <- read_csv("~/cluster_scratch/prism/screened_drugs.csv")
prism_sc_data <- read_csv("~/cluster_scratch/prism/secondary-screen-dose-response-curve-parameters.csv")
load("~/cluster_scratch/forward_modelling/targetpred_output_simplefiltering.RData")
# load("~/cluster_scratch/forward_modelling/forwardmodelling_all_update.RData")
repurposinghub_drug <- read_csv("~/cluster_scratch/prism/drug_repurposing_hub_nobroadid.csv")
repurposinghub_sample <- read_csv("~/cluster_scratch/prism/drug_repurposing_hub_sample.csv")

res_prism2 <- res_prism2 %>%
  select(BROAD_ID, .metric, input, estimate, name, drug_category, smiles,sample_size) %>% 
  filter(.metric== "spearman coef") %>% 
  pivot_wider(names_from = input, values_from= estimate) %>% 
  mutate(acc_sen= (ceres+ces+demeter2)/3) %>% 
  drop_na() %>% 
  distinct() 

sc_druglist <- unique(prism_sc_data$broad_id)
prism_drugs <- prism_drugs %>% 
  mutate(phase= case_when(
  broad_id %in% sc_druglist ~ 2,
    TRUE ~ 1
))

repurposinghub_drug <- repurposinghub_drug %>% 
  left_join(repurposinghub_sample) %>% distinct()
rm(repurposinghub_sample)
prism_drugs <- prism_drugs %>% 
  left_join(repurposinghub_drug) 

prism_sc_drug <-  prism_sc_data %>% 
  select(broad_id, target, phase,moa) %>% 
  left_join(prism_drugs %>% select(broad_id, drug_category)) %>% 
  distinct() %>% 
  separate(col = broad_id, 
           into=c("BRD","id", NA), 
           sep = "-", remove = T, extra= "drop" ) %>% 
  unite("broad_id", BRD:id, sep = "-") %>%
  filter(broad_id %in% prism_data$BROAD_ID) %>% 
  filter(!is.na(drug_category)) %>% 
  group_by(broad_id, phase, drug_category) %>% 
  summarize(target = paste(target, collapse = ","),
            moa= paste(moa, collapse = ",")) 
# write_csv(prism_sc_drug, "~/cluster_scratch/prism/drug_repurposing_scdrugsmeta.csv")
```

Figure 5A
```{r,fig.height=3.5, fig.width=3.6}
# 1448 drugs including the withdrawn drugs. Could the withdrawn be due to the wrong target information that lead to unexpected result?
# there are too little of them to draw conclusions.
mypal <- pal_npg("nrc")(4)[c(3,4,1)]
targetinfo_drug_by_category <- prism_sc_drug %>% 
  # filter(phase!="Withdrawn") %>% 
  mutate(drug_phase= case_when(
    phase =="Launched" ~  "Approved",
    TRUE ~ "Investigational"
  )) %>%
  select(-phase) %>% 
  mutate(target_missing= (target == "NA")) %>% 
  group_by(drug_phase, drug_category) %>% 
  summarize(na_count= sum(target_missing),
            total_count= n()) %>% 
  mutate(na_percentage= round(na_count/ total_count,3)*100) %>%
  mutate(drug_category= factor(
    drug_category,
    levels= c("targeted cancer", "chemo", "noncancer"),
    labels = c(  "Targeted cancer","Chemo","Noncancer"))) %>% 
  arrange(drug_category, drug_phase) %>% 
  select(drug_category, drug_phase,total_count,na_count,  na_percentage)

fig <- targetinfo_drug_by_category %>% 
   ggplot(aes(x=drug_category, y= na_count, fill=drug_category)) +
  # geom_col(position = "fill")
  geom_bar(stat="identity",position = position_dodge())+
  # ggsci::scale_fill_npg()+
  theme_classic()+
  # ylim(c(0, 0.35))+
  # scale_y_continuous(labels = scales::percent)+
  facet_wrap(~drug_phase)+
  theme(axis.text.x   = element_blank(), axis.title.x = element_blank())+
  ylab("Number of drugs lacking target information")+
  guides(fill=guide_legend(nrow = 1))+
  scale_fill_manual(values=mypal)+
  theme(legend.position = "top",legend.title = element_blank())
fig

targetinfo_drug_by_category
# ggsave(fig,filename = "~/cluster_wrk/drug_moa/predicting_prism/fig_res/fig5a.png",width = 3.6,height = 3.5,units = "in",dpi = 500)
# ggsave(fig,filename = "~/cluster_wrk/drug_moa/predicting_prism/fig_res/fig5a.pdf",device = "pdf",width = 3.6,height = 3.5)
# write_csv(targetinfo_drug_by_category, "targetinfo_drug_by_category.csv")

```

# 2 Model fitness for PRISM drugs
Explaining the sensitivity fitting accuracy of PRISM
report the sensitivity fitting accuracy
```{r}
load("~/cluster_scratch/forward_modelling/forwardmodelling_all_new.RData")
# combined_performance3 %>% 
#   filter(sample_size>100) %>% 
#   group_by(.metric, input, dataset) %>% 
#   summarise(mean_acc= mean(estimate,na.rm = T))

# test whether the performance metric for PRISM is significantly worse.
tmp_error <- combined_performance3 %>% 
  filter(sample_size>100)  %>%
  filter(input !="exp") %>% 
  mutate(input= toupper(input)) %>%
  mutate(dataset= toupper(dataset)) %>% 
  mutate(dataset= factor(dataset, levels= c("PRISM", "CTRP","GDSC"))) %>% 
  filter(.metric %in% c("mae", "rmse"))

tmp_error_aov <- aov(estimate ~.metric+dataset+input,data= tmp_error)
# tmp <- summary(tmp_error_aov)[[1]]

# I don't care about the difference between CTRP and GDSC
# TukeyHSD(tmp_error_aov, which = "dataset", paired=T) 
error_dunnett <- data.frame(
  DescTools::DunnettTest(tmp_error$estimate, g= tmp_error$dataset)$PRISM) %>%
  rownames_to_column("comparison") %>% 
  mutate(performance_metric_category= "error")
  
tmp_acc <- combined_performance3 %>% 
  filter(sample_size>100)  %>%
  filter(input !="exp") %>% 
  mutate(input= toupper(input)) %>%
  mutate(dataset= toupper(dataset)) %>% 
  mutate(dataset= factor(dataset, levels= c("PRISM", "CTRP","GDSC"))) %>% 
  filter(!(.metric %in% c("mae", "rmse")))

tmp_acc_aov <- aov(estimate ~.metric+dataset+input,data= tmp_acc)
summary(tmp_acc_aov)

# TukeyHSD(tmp_acc_aov, which = "dataset", paired=T)
acc_dunnett <- data.frame(
  DescTools::DunnettTest(tmp_acc$estimate, g= tmp_acc$dataset)$PRISM) %>%
  rownames_to_column("comparison") %>% 
  mutate(performance_metric_category= "acc")
sig_res <- bind_rows(error_dunnett, acc_dunnett)
write_csv(sig_res, "sig_res.csv")
```

```{r}
get_auc_mean <- function(df){mean(df$auc, na.rm = T)}
get_auc_variance <- function(df){sd(df$auc, na.rm = T)}

sen_mean_var <- prism_data %>% 
  select(BROAD_ID, sensitivity) %>% 
  mutate(
    sen_mean=map_dbl(.x = sensitivity, .f = get_auc_mean),
    sen_sd=map_dbl(.x = sensitivity, .f = get_auc_variance)
         ) %>% 
  select(-sensitivity) %>% 
  inner_join(res_prism2 %>% 
               filter(.metric=="spearman coef") %>% 
               filter(input== "ces") %>% 
               filter(sample_size>100)
             ) %>% 
  mutate(drug_category= factor(
    drug_category,
    levels= c(  "noncancer","targeted cancer","chemo"),
    labels = c(  "Noncancer","Targeted cancer","Chemo")))
  # mutate(drug_category= fct_relevel(drug_category, levels= c(  "noncancer","targeted cancer","chemo") )) 

sen_mean_var %>%
  group_by(drug_category) %>% 
  summarise(median_sen=  median(sen_mean), median_spearman= median(estimate))

DescTools::DunnettTest(sen_mean_var$sen_mean, 
                       g= sen_mean_var$drug_category,paired=T)
DescTools::DunnettTest(sen_mean_var$estimate,
                       g= sen_mean_var$drug_category,paired=T)
# whether prediction accuracy is correlated with drug sensitivity level?
cor.test(sen_mean_var$sen_mean, sen_mean_var$estimate,method = "spearman")
```

Figure 5B
```{r,fig.width=3.5,fig.height=4}
mypal1 <- pal_npg("nrc")(4)[c(1,3,4)]
fig <- sen_mean_var %>% 
  ggplot(aes(y=estimate, x= sen_mean,color= drug_category)) + 
  geom_point(size = 0.2)+
  geom_smooth(method = "lm", se = FALSE)+
  theme_classic()+
  ylab("Model fitness (Spearman COR)")+
  xlab("Average drug sensitivity (AUC)")+
  guides(color= guide_legend(title = element_blank(),nrow = 1))+
  scale_color_manual(values= mypal1)+
  theme(legend.position="top")
# fig

fig <- ggExtra::ggMarginal(fig, type= "boxplot",groupColour = T,groupFill = T) 
fig
# ggsave(fig,filename = "~/cluster_wrk/drug_moa/predicting_prism/fig_res/fig5b.png",width = 3.5,height = 4,units = "in",dpi = 500)
# ggsave(fig,filename = "~/cluster_wrk/drug_moa/predicting_prism/fig_res/fig5b.pdf",device = "pdf",width = 3.5,height = 4)
```

```{r,fig.width=3,fig.height=7, eval=FALSE,include=FALSE,echo=FALSE}
cross_ref_tibble_gdsc <- read_csv("~/cluster_scratch/prior/drug_id_list/cross_ref_tibble_gdsc")
overlapping_drug_list <- sort(intersect(intersect(cross_ref_tibble_gdsc$BROAD_ID, ctrp_data$broad_cpd_id), prism_data$BROAD_ID)) # 44 drugs available (in nature cancer paper 84 compound and median 236 cell line)

imp_ctrp_shared <- feature_imp_ridge_ctrp_comb1 %>% filter(drug %in% overlapping_drug_list) %>% arrange(drug)

imp_prism_shared <- feature_imp_ridge_prism_comb1 %>% 
  filter(drug %in% overlapping_drug_list) %>% arrange(drug)

imp_gdsc_shared <- cross_ref_tibble_gdsc %>% 
  inner_join(  feature_imp_ridge_gdsc_comb1, by =c("DRUG_ID"= "drug")) %>% 
  select(-pubchem_cid, -DRUG_ID) %>% 
  rename(drug= BROAD_ID) %>% 
  filter(drug %in% overlapping_drug_list) %>% 
  arrange(drug)

get_cor_long_tibble <- function(df1,df2){ 
  cor_mat <- cor(
    x = t(df1[,-1]),
    y= t(df2[,-1]),
    method = "pearson"
    )
  cor_vec <- diag(cor_mat)
  }


cor_tibble <- tibble(
  drug= imp_ctrp_shared$drug, 
  ctrp_gdsc = get_cor_long_tibble(imp_ctrp_shared, imp_gdsc_shared), 
  ctrp_prism = get_cor_long_tibble(imp_ctrp_shared, imp_prism_shared), 
  gdsc_prism = get_cor_long_tibble(imp_prism_shared, imp_gdsc_shared)) %>% 
  inner_join(
    prism_data %>% select(BROAD_ID, name,drug_category), 
    by= c("drug"= "BROAD_ID")) %>% 
  # select(-drug) %>% 
  arrange(ctrp_gdsc)

fig <- cor_tibble %>% 
  select(-drug, -drug_category) %>% 
  pivot_longer(cols=-name, names_to= "across_dataset", values_to= "COR") %>%
  arrange(across_dataset, COR) %>% 
  mutate_at(1,factor,
            levels= cor_tibble$name) %>% 
  mutate_at(2,factor,
          levels=c("ctrp_gdsc", "ctrp_prism", "gdsc_prism"),
          labels = c("CTRP-GDSC", "CTRP-PRISM", "GDSC-PRISM")
          ) %>%
  ggplot(aes(x= name,  y= COR, fill= across_dataset))+
  geom_bar(stat = "identity", position = position_dodge())+
  scale_fill_npg()+
  coord_flip()+
  theme_classic()+
  guides(fill=guide_legend(nrow = 3))+
  theme(
    axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1),
    axis.title.y = element_blank(),
    legend.title = element_blank(),
    legend.position = c(0.7, 0.1),
    legend.direction = "horizontal"
    )
fig
```

for the 44 shared drugs'ssig whether CTRP and GDSC are more correlated?
```{r,fig.width=3,fig.height=7, eval=FALSE,include=FALSE,echo=FALSE}
summary(cor_tibble)
tmp <- cor_tibble %>% 
  pivot_longer(cols = 2:4, names_to= "comparison", values_to= "cor") %>% 
  mutate(comparison= factor(
    comparison, levels = c("ctrp_gdsc", "ctrp_prism", "gdsc_prism")))
DescTools::DunnettTest(tmp$cor, g= tmp$comparison,paired=T)

# for these 44 drugs whether drug sensitivity fitting acc is lower

# 3 dataset, 3input, 6metrics,44 drugs
fitting_acc44 <- bind_rows(
  cor_tibble %>%
  select(drug, name, drug_category) %>% 
  inner_join(y= cross_ref_tibble_gdsc %>% 
               rename(GDSC_ID=DRUG_ID) %>% 
               mutate(GDSC_ID=as.character(GDSC_ID)),
             by=c("drug"= "BROAD_ID")) %>% 
  inner_join(combined_performance3, c("drug"="ID")),

  cor_tibble %>%
  select(drug, name, drug_category) %>% 
  inner_join(y= cross_ref_tibble_gdsc %>% 
               rename(GDSC_ID=DRUG_ID) %>% 
               mutate(GDSC_ID=as.character(GDSC_ID)),
             by=c("drug"= "BROAD_ID")) %>% 
  inner_join(combined_performance3, c("GDSC_ID"="ID"))) %>% 
  select(-DRUG_ID) %>% 
  distinct() %>% 
  filter(input !="exp")

fitting_acc44 %>% 
  group_by(input, dataset,.metric) %>% 
  summarise(mean_acc= mean(estimate))

tmp_error <- fitting_acc44 %>% 
  mutate(input= toupper(input)) %>%
  mutate(dataset= toupper(dataset)) %>% 
  mutate(dataset= factor(dataset, levels= c("PRISM", "CTRP","GDSC"))) %>% 
  filter((.metric %in% c("mae", "rmse")))
error_dunnett <- data.frame(
  DescTools::DunnettTest(tmp_error$estimate, g= tmp_error$dataset)$PRISM) %>%
  rownames_to_column("comparison") %>% 
  mutate(performance_metric_category= "error")
  

tmp_acc <- fitting_acc44 %>% 
  mutate(input= toupper(input)) %>%
  mutate(dataset= toupper(dataset)) %>% 
  mutate(dataset= factor(dataset, levels= c("PRISM", "CTRP","GDSC"))) %>% 
  filter(!(.metric %in% c("mae", "rmse")))
acc_dunnett <- data.frame(
  DescTools::DunnettTest(tmp_acc$estimate, g= tmp_acc$dataset)$PRISM) %>%
  rownames_to_column("comparison") %>% 
  mutate(performance_metric_category= "acc")
sig_res1 <- bind_rows(error_dunnett, acc_dunnett)
write_csv(sig_res1, "sig_res1.csv")

```


# 3 Explore the target prediction of PRISM with different fitting accuracy
```{r}
load("~/cluster_scratch/forward_modelling/targetpred_output_prismgoodbadexplore1.RData")
get_supervised_df <- function(good_df, bad_df){
   df <- bind_rows(
    good_df %>% mutate(fitting_quality= "Top"),
    bad_df %>% mutate(fitting_quality= "Bottom"),
    acc_df_prism_binary_fold_cv %>% mutate(fitting_quality= "All")
  ) %>% 
    mutate(fitting_quality= fct_relevel(fitting_quality, c("All", "Top", "Bottom")) ) %>%  
    mutate(method= factor(
      method,
      levels = c("senbased_genesig_comb1", "Consensus_exp_perturb", "structure_ECFP", "structure_MACCS"),
      labels = c("Ess-sig", "Exp-sig", "Fingerprint-ECFP","Fingerprint-MACCS" ),
    ) )
   return(df)
   }

df_200 <- get_supervised_df(good_df = acc_df_prism_binary_fold_cv_good200,
                        bad_df = acc_df_prism_binary_fold_cv_bad200)
df_200 %>% 
  filter(fitting_quality=="All") %>% 
  group_by(method) %>% 
  summarise(median_acc= median(acc))

sig_res2 <- df_200 %>% 
  nest_by(fitting_quality) %>% 
  ungroup() %>% 
  mutate(DunnettTest_res=map(
    .x = data, 
    .f = function(df){
      res=DescTools::DunnettTest(df$acc, g= df$method)
      res= tibble(comparison= row.names(res[[1]]), 
                  diff= res[[1]][,1],
                  p.value= res[[1]][,4])
      return(res)
    }
                 )) %>% 
  select(-data) %>% 
  unnest(cols = c(DunnettTest_res))
write_csv(sig_res2, "sig_res2.csv")
```

Figure 5C
```{r,fig.height=3, fig.width=4.5}
plot_two_group <- function(df){
  # my_comparisons <- list(c("Ess-sig", "Exp-sig"), c("Ess-sig", "Fingerprint-ECFP"), c("Ess-sig", "Fingerprint-MACCS"))
  df %>% 
    ggplot(aes(x= method,y=acc, fill= method,color= method )) + 
    geom_violin()+
    # ggpubr::stat_compare_means(
    #   aes(group=method),label = "p.signif",
    #   method = "t.test",paired = T,vjust = 0.4,ref.group = 1)+
    stat_summary(fun.data = "mean_cl_boot", geom = "pointrange",
             colour = "black",position = position_dodge(width = 0.9),size=0.2)+
    ggsci::scale_fill_npg()+
    ggsci::scale_color_npg()+
    facet_wrap(~fitting_quality)+
    theme_classic()+
    ylab(label = "Target prediction accuracy (AUROC)")+
    guides(fill= guide_legend(nrow = 4))+
    theme(
          legend.title = element_blank(),
          axis.text.x = element_blank(), 
          axis.title.x = element_blank(),
          legend.position = c(.25, .25))
}


fig <- plot_two_group(df_200)
fig
ggsave(fig,filename = "~/cluster_wrk/drug_moa/predicting_prism/fig_res/fig5d.png",width = 4.5,height = 3,dpi = 500)
ggsave(fig,filename = "~/cluster_wrk/drug_moa/predicting_prism/fig_res/fig5d.pdf",width = 4.5,height = 3)
```

Figure 5D
```{r}
load("~/cluster_scratch/unsupervised_target_pred/unsupervised_target_pred_method_comparison.RData")
unsupervised_df <- bind_rows(
  prism_unsupervised_auc %>% 
    filter(drug %in% prism_good_drug_list_200) %>%
    mutate(fitting_quality= "Top drugs")
  ,
  prism_unsupervised_auc %>% 
    filter(drug %in% prism_bad_drug_list_200) %>%
    mutate(fitting_quality= "Bottom drugs")
  ) #%>% 
  # mutate(AUC= replace_na(AUC,0.5))

unsupervised_df %>% 
  group_by(imptype, fitting_quality) %>% 
  summarize(median_auc=median(AUC,na.rm = T))
```


```{r,fig.height=3,fig.width=2.5}
fig <- unsupervised_df %>% 
  mutate(imptype= factor(
    imptype,
    levels = c("ConSen-Sig", "ConExp-Sig"),
    labels = c("Ess-sig", "Exp-sig" ),
    ) ) %>% 
  ggplot(aes(y=AUC, x= fitting_quality,fill= imptype,color=imptype)) + 
  geom_violin()+
  ggpubr::stat_compare_means(
    aes(group=imptype),
    method = "t.test",vjust = 0.4,hide.ns = F,label.y = 1.1,label = "p.signif",bracket.size = 1)+
  ggpubr::stat_compare_means(
    data = unsupervised_df %>% filter(imptype=="ConSen-Sig"),
    aes(group=fitting_quality),
    method = "t.test",vjust = 0.6,hide.ns = F,label.y = 1.2,
    label = "p.signif")+
  stat_summary(fun.data = "mean_cl_boot", geom = "pointrange",
           colour = "black",position = position_dodge(width = 0.9),size=0.2)+
  ggsci::scale_fill_npg()+
  ggsci::scale_color_npg()+
  guides(fill=guide_legend(nrow = 1))+
  theme_classic()+
  ylab(label = "Signature target enrichment (AUROC)")+
  theme(axis.title.x = element_blank(),legend.position = "top",
        legend.title = element_blank())
fig
# ggsave(fig,filename = "~/cluster_wrk/drug_moa/predicting_prism/fig_res/fig5e.png",width = 2.5,height = 3,units = "in",dpi = 500)
# ggsave(fig,filename = "~/cluster_wrk/drug_moa/predicting_prism/fig_res/fig5e.pdf",device = "pdf",width = 2.5,height = 3)
```
```{r}
sessionInfo()
```


