---
title: "Untitled"
author: "Wenyu"
date: "4/29/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

collect the screening drug and their target 
I need additional annotation for plotting

```{r}

prism_drugs <- read_csv("~/cluster_scratch/prism/screened_drugs.csv")

prism_sc_data <- read_csv("~/cluster_scratch/prism/secondary-screen-dose-response-curve-parameters.csv")

sc_druglist <- unique(prism_sc_data$broad_id)
prism_drugs <- prism_drugs %>% 
  mutate(phase= case_when(
  broad_id %in% sc_druglist ~ 2,
    TRUE ~ 1
))

repurposinghub_drug <- read_csv("~/cluster_scratch/prism/drug_repurposing_hub_nobroadid.csv")
repurposinghub_sample <- read_csv("~/cluster_scratch/prism/drug_repurposing_hub_sample.csv")
repurposinghub_drug <- repurposinghub_drug %>% 
  left_join(repurposinghub_sample) %>% distinct()
rm(repurposinghub_sample)
prism_drugs <- prism_drugs %>% 
  left_join(repurposinghub_drug) 
  
```
Annotations proporations

Non-Cancer drugs is poorly studied 
even it is approved drugs

(think of a better way of visualization to emphasize your point)
```{r}

tmp <- inner_join(
  x = prism_drugs %>% 
    filter(phase==2) %>% 
    group_by(drug_category) %>% 
    summarise(NA_count= sum(is.na(target)))
  ,
  y = prism_drugs %>% 
    filter(phase==2) %>% 
    group_by(drug_category) %>% 
    summarise(all_count= n())
  ) %>% 
    drop_na() %>% 
    mutate(annotate= all_count-NA_count) %>% 
    mutate(NA_proportion= NA_count/all_count)


tmp %>% 
  select(-3,-5) %>% 
  pivot_longer(cols= -drug_category, names_to = "type", values_to= "count" ) %>% 
  ggplot(aes(x=drug_category, y=(count), fill=type)) +
  # geom_col(position = "fill")
  geom_bar(stat="identity")+
  theme_minimal()
```
check specifically how many drug target pairs available for different target
```{r}
tmp <-  prism_sc_data %>% 
  select(broad_id, target, phase) %>% 
  left_join(prism_drugs %>% select(broad_id, drug_category)) %>% 
  distinct() %>% 
  separate_rows(target, sep = ",") %>% 
  distinct()  %>% 
  mutate(drug_phase= case_when(
    phase %in%  c("Phase 1",  "Phase 1/Phase 2",  "Phase 2", "Phase 2/Phase 3", "Phase 3") ~  "In trail",
    TRUE ~ phase
  )) %>% 
  mutate(target_annotated=is.na(target)) %>% 
  select(-phase) %>% 
  group_by(drug_phase, drug_category) %>% 
  summarize(na_count= sum(target_annotated),
            total_count= n()) %>% 
  drop_na() %>% 
  mutate(na_percentage= na_count/ total_count)

```



check how many drug*cell pair available for prism and ces1
```{r}
ces1_478 <- read_csv("~/cluster_scratch/impute_ess_20q4/ces1_478.csv")
# tmp <- str_c(str_split(prism_sc_data$broad_id,pattern = "-",n = 3,simplify = T)[,1:2])
# prism_sc_data %>% 
#   mutate(broad_ID= prism)

# 312 cells available!
cell_overlap <- intersect(ces1_478$DepMap_ID, unique(prism_sc_data$depmap_id))
```



First prepare data to generate drug essentiality signatures.
a 
Then use the existing target information to check cv accuracy
In the end predict target for the drugs without target annotation.

