---
title: "Non-oncology drug exploration"
output: html_document
---

```{r, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
load("~/cluster_scratch/forward_modelling/targetpred_output_simplefiltering.RData")
rm(get_target_mat)
rm(no_tunning_weighted_averaging)
rm(get_target_pred_accuracy_batch)
rm(return_acc_estimate_cv)
library(tidyverse)
library(ggsci)
# PRISM_binary_PPIold_data <- read_csv( "~/cluster_scratch/prior/PRISM_binary_PPIold_data.csv")

source("~/cluster_wrk/drug_moa/unsupervised_target_exploration/get_drug_frac.R")
prism_sc_drug <- read_csv("~/cluster_scratch/prism/drug_repurposing_scdrugsmeta.csv")

targetpanel_dtc <- data.table::fread("~/cluster_scratch/prior/DTC_data_all.csv",
                                 select = c("gene_names")) %>% distinct() %>% pull(gene_names)

cell_line_info <- data.table::fread("~/cluster_scratch/depmap_21q1/sampleinfo")

targetpanel_drh <- read_tsv("~/cluster_scratch/prior/repurposing_drugs_20200324.txt") %>% 
  select(-disease_area, -indication) %>% 
  drop_na() %>% 
  separate_rows(target) %>% 
  distinct() 

targetpanel_drh_genelevel <- targetpanel_drh %>% 
  select(pert_iname, target) %>% 
  group_by(target) %>% 
  summarise(drug= paste(pert_iname,collapse = ","))

length(unique(targetpanel_drh$target))   # 1943 genes

cellline_hgsoc <- cell_line_info %>% 
  filter(primary_disease== "Ovarian Cancer") %>% 
  filter(Subtype== "Adenocarcinoma, high grade serous")
```


I should focus on drugs with both moa and drug target. 

go back to non-supervised prediction analysis part and check genes that are important for all drugs! they can be genes related with cell of death effect(check signature of cell death paper), or metabolic enzymes/drug efflux pumps(MDR1, ABCB1)
```{r}
res_prism2_long <- res_prism2
res_prism2 <- res_prism2_long %>%
  select(-variance) %>% 
  filter(.metric== "spearman coef") %>%
  pivot_wider(names_from = input, values_from= estimate) %>%
  mutate(acc_sen= (ceres+ces+demeter2)/3) %>%
  distinct() 

prism_good_fitted_drugs <- res_prism2 %>%
  filter(sample_size>100) %>%
  filter(acc_sen>0.2) %>%
  arrange(BROAD_ID)
# n=312

# drh annotation include both MOA and target info N=268
prism_good_fitted_drugs_drhannotated <- prism_good_fitted_drugs %>% 
  select(BROAD_ID, moa) %>% 
  drop_na() %>% 
  filter(BROAD_ID %in% prism_target_binary$drug) %>% 
  pull(BROAD_ID)
  
# DTC only care about target gene: N= 52
prism_good_fitted_drugs_dtcannotated <- prism_good_fitted_drugs %>% 
  filter(BROAD_ID %in% prism_target_dtc$drug) %>% 
  pull(BROAD_ID)

# how many non-oncology drugs? N= 63
prism_good_fitted_nononcologydrugs <-  prism_good_fitted_drugs %>% 
  filter(drug_category== "noncancer") %>% 
  arrange(BROAD_ID ) %>% 
  pull(BROAD_ID) %>% 
  unique()

  
# 46 =58-13 +1 1 drug no moa but have target.
prism_good_fitted_nononcologydrugs_drhannotated <- intersect(prism_good_fitted_drugs_drhannotated, prism_good_fitted_nononcologydrugs)

prism_good_fitted_nononcologydrugs_drhnotannotated <- setdiff(prism_good_fitted_drugs_drhannotated, prism_good_fitted_nononcologydrugs)

# prism_good_fitted_nononcologydrugs <-  prism_good_fitted_drugs %>% 
#   filter(drug_category== "noncancer") %>% 
#   arrange(BROAD_ID ) %>% 
#   filter(is.na(moa))
```

get hgsoc sensitivity for all 63 noncancer drugs
```{r}
prism_63_sen <- prism_data %>% 
  filter(BROAD_ID %in%  prism_good_fitted_nononcologydrugs) %>% 
  select(BROAD_ID ,sensitivity) %>% 
  unnest(cols=sensitivity) %>% 
  drop_na()


# list auc of HGSOC, and the number of sen HGSOC cells for that drugs
prism_63_sen_hgsoc <- full_join(
    x= prism_63_sen %>% filter(depmap_id %in% cellline_hgsoc$DepMap_ID),
    y= cellline_hgsoc %>% select(DepMap_ID, cell_line_name), 
    by=c("depmap_id"= "DepMap_ID")
  ) %>% 
  select(-ec50) %>% 
  # filter(auc< 0.8) %>%
  group_by(BROAD_ID) %>% 
  summarise(n_total= n(),n_0.8= sum(auc<0.8)  ) %>% 
  drop_na() %>% 
  ungroup() %>% 
  full_join(
  y = prism_63_sen %>% filter(depmap_id == "ACH-000524")
    )

write_csv(prism_63_sen_hgsoc, path = "~/cluster_wrk/drug_moa/predicting_prism/prism_63_sen_hgsoc.csv")

tmp= prism_data %>% filter(BROAD_ID %in% prism_good_fitted_nononcologydrugs) %>% 
  filter(!(BROAD_ID  %in% prism_good_fitted_drugs_drhannotated )) %>%  select(BROAD_ID, moa)
```


Get supervised and nonsupervised prediction accuracy
```{r}
load("~/cluster_scratch/unsupervised_target_pred/unsupervised_target_pred_ConSenSig.RData")

acc_unsupervised_prism268 <- prism_unsupervised_auc %>% 
  filter(drug %in% prism_good_fitted_drugs_drhannotated) 

setwd("~/cluster_wrk/drug_moa/supervised_target_pred/function/")
source('return_acc_estimate_loocv.R') 
acc_supervised_prism268 <- return_acc_estimate_cv(
  target_tibble = prism_target_binary %>% 
    filter(drug %in% prism_good_fitted_drugs_drhannotated) %>% 
    arrange(drug),
  predictors_tibble = feature_imp_ridge_prism_comb1 %>% 
    filter(drug %in% prism_good_fitted_drugs_drhannotated)%>% 
    arrange(drug)
  )

prism_268_all <- acc_supervised_prism268 %>% 
  left_join(acc_unsupervised_prism268) %>% 
  left_join(prism_data %>% select_at(c(1:5,8)),by= c("drug" = "BROAD_ID") ) %>%
  mutate(Drug_category= case_when(drug_category== "noncancer"~ drug_category,
                                  TRUE ~ "cancer") ) %>% 
  left_join(prism_sc_drug %>% select_at(c(1,2,4)),by= c("drug" = "broad_id")) %>% 
  rename(supervised_auc= acc) %>% 
  rename(unsupervised_auc = auc) %>% 
  rename(sample_size= n_forward_modelling) %>% 
  select(drug, name, drug_category, moa,target,phase, supervised_auc, unsupervised_auc,sample_size)

```

check the median accuracy and significance
```{r}
prism_268_all %>% 
  group_by(drug_category) %>%
  summarise(
    median_unsupervised= median(unsupervised_auc, na.rm = T),
    median_supervised= median(supervised_auc),
    ) 
prism_268_all %>% 
  t_test(supervised_auc~Drug_category)
prism_268_all %>% 
  t_test(unsupervised_auc~Drug_category)
```

```{r,fig.width=4,fig.height=4.5}
fig <- prism_268_all %>% 
  ggplot(aes(x= supervised_auc, y= unsupervised_auc, color= drug_category)) + 
  geom_point(size = 0.5)+
  theme_classic()+
  ylab("Supervised target prediction accuracy (AUC)")+
  xlab("Unsupervised target prediction accuracy (AUC)")+
  guides(color= guide_legend(title = "Drug Category"))+
  theme(legend.position="bottom")+
  # theme(
  #   legend.position = c(1, 0.00),
  #   legend.justification = c("right", "bottom"),
  #   legend.box.just = "right"
  #   )+
  ggsci::scale_color_npg()
fig <- ggExtra::ggMarginal(fig,type= "boxplot",groupColour = T,groupFill = T)
fig

# ggsave(fig,filename = "~/cluster_wrk/drug_moa/predicting_prism/fig_res/fig6.tiff",device = "tiff",width = 4,height = 4,units = "in",dpi = 300)
# ggsave(fig,filename = "~/cluster_wrk/drug_moa/predicting_prism/fig_res/fig6.pdf",device = "pdf",width = 4,height = 4)
```



Showing how target of noncancer drugs overlapped poorly with cancer drugs
```{r,fig.width=3.5,fig.height=3.5}
# Distribution of number of drugs with at least one shared target
tmp <- inner_join(prism_target_binary, prism_268_all %>% select(drug, Drug_category))
tmp1 <- prism_268_all %>% 
  # select(drug, Drug_category) %>% 
  mutate(N_shared= map_int(prism_good_fitted_drugs_annotated, function(x){
    gene <- tmp %>% filter(drug == x) %>% pull(target)
    N= tmp %>% filter(!(drug %in% x)) %>% filter(target %in% gene) %>% select(drug) %>% distinct() %>% nrow()
    return(N)
  }))

fig <- tmp1 %>% 
  ggplot(aes(x= N_shared, fill= Drug_category))+
  geom_density(alpha=0.5)+
  theme_classic()+
  theme(
    legend.position = c(1, 0.5),
    legend.justification = c("right", "bottom"),
    legend.box.just = "right"
    )+
  ggsci::scale_fill_npg()+
  xlab("No.drugs with shared targets")
fig
# ggsave(fig,filename = "~/cluster_wrk/drug_moa/predicting_prism/fig_res/fig6b.tiff",device = "tiff",width = 3.5,height = 3.5,units = "in",dpi = 300)
# ggsave(fig,filename = "~/cluster_wrk/drug_moa/predicting_prism/fig_res/fig6b.pdf",device = "pdf",width = 3.5,height = 3.5)
```


```{r, fig.width=3,fig.height=3.5}
fig <- tmp1 %>% 
  # ggplot() +
  # geom_point(aes(x= N_shared, y= acc))
  # mutate(bin = cut_width(N_shared, width = 10,boundary = 0)) %>% 
  mutate(bin= case_when(N_shared<1 ~ "0",
                        between(N_shared, 1,5)~"1-5",
                         between(N_shared, 6,20)~"6-20",
                        TRUE~">20")) %>% 
  mutate(bin= fct_relevel(bin, c("0", "1-5", "6-20", ">20")) ) %>% 
  ggplot(aes(x = bin, y = acc)) +
  geom_violin()+
  stat_summary(fun.data = "mean_cl_boot", geom = "pointrange",
             colour = "black",position = position_dodge(width = 0.9))+
  theme_classic()+
  ylab("Supervised target prediction accuracy (AUC)")+
  xlab("No.drugs with shared targets")
fig
# ggsave(fig,filename = "~/cluster_wrk/drug_moa/predicting_prism/fig_res/fig6c.tiff",device = "tiff",width = 3,height = 3.5,units = "in",dpi = 300)
# ggsave(fig,filename = "~/cluster_wrk/drug_moa/predicting_prism/fig_res/fig6c.pdf",device = "pdf",width = 3,height = 3.5)
```


Now use the 268 drugs as the training set to predict the targets for the drugs of interest

```{r}
train_consen_sig <- bind_rows(
    feature_imp_ridge_prism_comb1 %>%
      filter(drug %in% prism_good_fitted_drugs_drhannotated) %>%
      arrange(drug),

    feature_imp_ridge_prism_comb1 %>%
      filter(drug %in% prism_good_fitted_nononcologydrugs) %>%
      arrange(drug)
)

train_cor_mat <- cor(t(train_consen_sig %>% select(-drug)))
colnames(train_cor_mat) <- train_consen_sig$drug
row.names(train_cor_mat) <- train_consen_sig$drug
target_mat_268 <- get_target_mat(
  target_tibble = prism_target_binary %>%
    filter(drug %in% prism_good_fitted_drugs_drhannotated) %>%
    arrange(drug))

pred_63_supervised <- no_tunning_weighted_averaging(
  target_mat = target_mat_268,
  cor_mat = train_cor_mat,
  test_idx = 269:331,pred_new = T)
pred_63_supervised <- t(pred_63_supervised)

pred_268_supervised <- map_dfc(
  .x = 1:268,
  .f = ~no_tunning_weighted_averaging(
    target_mat = target_mat_268,
    cor_mat = train_cor_mat[1:268,1:268],
    test_idx = .x,
    pred_all = T)
  )
# pred_268_supervised <- t(pred_268_supervised)

colnames(pred_268_supervised) <- row.names(target_mat_268)
rownames(pred_268_supervised) <-colnames(target_mat_268)
source("~/cluster_wrk/drug_moa/supervised_target_pred/function/get_target_pred_supervised.R")

prism_drugbank_predictions <- get_predictions(
  sig_data=feature_imp_ridge_prism_comb1,
  train_drugs=prism_good_fitted_drugs_drhannotated,
  pred_drugs=prism_good_fitted_drugs$BROAD_ID, 
  train_label= prism_target_binary)
  
  
```


```{r}
cor_df_predicted_target <- 
  cor(pred_268_supervised, use = "pairwise.complete.obs", method = "spearman") %>%
  as_tibble() %>% 
  mutate(drug1=row.names(target_mat_268)) %>%
  pivot_longer(cols = -drug1,names_to= "drug2") %>% 
  arrange(drug1, drug2)

cor_df_unpred_target <- 
  train_cor_mat[1:268,1:268] %>% 
  as_tibble() %>% 
  mutate(drug1=row.names(target_mat_268)) %>%
  pivot_longer(cols = -drug1,names_to= "drug2") %>% 
  arrange(drug1, drug2)


cor_df_sen <- prism_data %>% filter(BROAD_ID %in% row.names(target_mat_268)) %>% 
  select(BROAD_ID, sensitivity) %>% 
  unnest(sensitivity) %>% 
  select(-ec50) %>% 
  drop_na() %>% 
  pivot_wider(id_cols = depmap_id,names_from= BROAD_ID, values_from=auc) %>% 
  select(-depmap_id) %>% 
  cor(use = "pairwise.complete.obs",method = "spearman") 

colnames(cor_df_sen) <- row.names(cor_df_sen)
cor_df_sen <- as_tibble(cor_df_sen)  %>% 
  # rowid_to_column()
  mutate(drug1= row.names(cor_df_sen)) %>% 
  pivot_longer(cols = -drug1,names_to= "drug2") %>% arrange(drug1,drug2)

tmp <- inner_join(cor_df_predicted_target,cor_df_sen,by=c("drug1", "drug2")) 
fig1 <- tmp %>% 
  ggplot(aes(x=value.x, y=value.y)) +
  geom_point(size=0.2)+
  xlab("Supervised prediction target similiarity")+
  ylab("Sensitivity similiarity")+
  theme_classic()
  # ggtitle("COR 0.74, p<2.2e-16")
# cor.test(tmp$value.x, tmp$value.y) 

tmp1 <- inner_join(cor_df_unpred_target,cor_df_sen,by=c("drug1", "drug2")) 
fig2 <- tmp1 %>% 
  ggplot(aes(x=value.x, y=value.y)) +
  geom_point(size=0.2)+
  xlab("Unsupervised prediction target similiarity")+
  ylab("Sensitivity similiarity")+
  theme_classic()
  # ggtitle("COR 0.88, p<2.2e-16")
  
# cor.test(tmp1$value.x, tmp1$value.y)
fig1 
fig2
setwd("~/cluster_wrk/drug_moa/predicting_prism/fig_res")
ggsave(filename = "figs3.tiff",plot = fig1,device = "tiff",width = 10,height = 10,units = "cm")
ggsave(filename = "figs4.tiff",plot = fig2,device = "tiff",width = 10,height = 10,units = "cm")
```


```{r}
pred_58_supervised <- 
  tibble(
    target= colnames(pred_58_supervised),
    as.data.frame(t(pred_58_supervised))
  ) %>%
  arrange(target)

colnames(pred_58_supervised )[2:59] <-  sort(prism_good_fitted_nononcologydrugs)

# write_csv(pred_58_supervised, "~/cluster_wrk/drug_moa/pred_58_supervised.csv")
# also write out the unsupervised prediction for the 58 drugs
pred_58_unsupervised <- feature_imp_ridge_prism_comb1 %>% 
  filter(drug %in% prism_good_fitted_nononcologydrugs) %>% 
  pivot_longer(-drug, names_to= "target", values_to= "pred") %>% 
  pivot_wider(id_cols = target, names_from= drug, values_from= pred)
# write_csv(pred_58_unsupervised, "~/cluster_wrk/drug_moa/pred_58_unsupervised.csv")
```


Combine the incorrectly predicted drugs and drugs without target info together
include the average sensitivity (perhaps also the number of sensitive cell lines)
as an indicator.

Think about how accurate is accurate? for an AUC of 0.8 /0.9 is quite high but the
putative target is still not the top one prediction.

now we have both supervised and unsupervised prediction accuracy! Despite there are some 
NA due to the lack of cover of existing target from ConSen-sig gene. 
(only 8 drugs so not so worrying)

report statistics in the manuscript
```{r}
get_auc_mean <- function(df){mean(df$auc, na.rm = T)}
get_auc_variance <- function(df){sd(df$auc, na.rm = T)}
get_nub_sencell <- function(df,thre){sum(df$auc<thre, na.rm = T)}
Sen_sum <- prism_data %>% 
  select(BROAD_ID, sensitivity) %>% 
  mutate(
    sen_mean=map_dbl(.x = sensitivity, .f = get_auc_mean),
    sen_sd=map_dbl(.x = sensitivity, .f = get_auc_variance),
    nub_sencell_0.8=map_dbl(.x = sensitivity, .f = ~get_nub_sencell(df = .x, thre = 0.8)),
    nub_sencell_0.7=map_dbl(.x = sensitivity, .f = ~get_nub_sencell(df = .x, thre = 0.7))
         ) %>% 
  select(-sensitivity)
```


for non-oncology drugs listed in the 305 prism
```{r}
prism_good_fitted_nononcologydrugs_notannotated_df <- prism_sc_drug %>% 
  filter(broad_id %in% setdiff(prism_good_fitted_drugs, prism_good_fitted_drugs_annotated)) %>% 
  filter(drug_category== "noncancer") %>% 
  inner_join(
    prism_data %>% 
      select(-target, - sensitivity, -moa, -drug_category), by=c("broad_id"= "BROAD_ID") 
    ) %>% 
  mutate(acc=NaN) %>% 
  mutate(auc=NaN) %>% 
  mutate(target=NA) %>% 
  # rename(drug_category=Drug_category) %>% 
  rename(drug=broad_id)


prism_good_fitted_nononcologydrugs_annotated_df <- prism_268_all %>% 
  filter(drug_category=="noncancer") %>% 
  select(-Drug_category) %>% 
  select(-test_idx) %>% 
  left_join(prism_sc_drug %>% select(broad_id, target), by= c("drug" = "broad_id")) 

prism_nononcology_df <- union(prism_good_fitted_nononcologydrugs_notannotated_df,
                              prism_good_fitted_nononcologydrugs_annotated_df) %>% 
  inner_join(Sen_sum,by=c("drug"= "BROAD_ID")) %>% 
  # inner_join(bimodality ,by="drug") %>% 
  select(-drug_category, -smiles) %>% 
  relocate(name)



# get the combined table for 58 nononcology drugs

get_top_n_target <- function(pred_tibble, res_type="short_table", n_pred= 5){
  
  tmp <- pred_tibble %>% 
    pivot_longer(cols = -target, values_to= "pred", names_to= "drug") %>% 
    group_by(drug) %>% 
    slice_max(order_by = pred, n= n_pred) %>% 
    ungroup() %>% 
    select(-pred)
    
  tmp1 <- tmp %>% 
    group_by(drug) %>%
    summarise(target=paste(target,collapse = ",")) %>% 
    ungroup() 
  
  if (res_type== "long_table"){return(tmp)}
  if (res_type== "short_table"){return(tmp1)}
  
}


# supervised_top5 <- get_top_n_target(pred_tibble = pred_58_supervised)
# unsupervised_top5 <- get_top_n_target(pred_tibble = pred_58_unsupervised)
# 
# prism_nononcology_df <- prism_nononcology_df %>% 
#   inner_join(supervised_top5 %>% rename(supervised_target= target)) %>% 
#   inner_join(unsupervised_top5 %>% rename(unsupervised_target= target)) %>% 
#   inner_join(bimodality_df, by=c("drug"= "BROAD_ID")) %>% 
#   rename(putative_target=target) %>% 
#   rename(supervised_pred_accuracy= acc) %>% 
#   rename(unsupervised_pred_accuracy= auc) 
# write_csv(prism_nononcology_df, "prism_nononcology_df.csv")  
```

plot the sensitivity distributions for the 58 drugs!
```{r,fig.width=10,fig.height=1.5}
plot_hist_sen <- function(drug_id, add_title= T){
  df <- prism_data %>% 
    filter(BROAD_ID %in%  drug_id) %>% 
    pull(sensitivity)

  df <- df[[1]]
  
  fig <- df %>% 
    ggplot() +
    geom_histogram(aes(x= auc),binwidth = 0.02)
  
  if (add_title== T){
    title <- prism_nononcology_df %>% 
    filter(drug==drug_id) %>% select(drug, name, bi_coef) %>% 
    mutate(bi_coef= round(bi_coef,digits = 3)) %>% 
    unlist() %>% paste(collapse = ";")
   fig <- fig+ ggtitle(title)
  }
  return(fig)
}

# plot_hist_sen(drug_id = "BRD-K37865504") 
# plot_hist_sen(drug_id = "BRD-K72815923")+xlim(c(0,2.4))
plot_hist_sen(drug_id = "BRD-K69726342")+xlim(c(0,2.2))
# for (drug in prism_good_fitted_nononcologydrugs){
#   fig <- plot_hist_sen(drug_id = drug)
#   ggsave(
#     device = "tiff",
#     plot = fig,
#     # width = 3,
#     # height = 3,
#     filename = paste("~/cluster_wrk/drug_moa/predicting_prism/fig_sen_distribution/", drug, ".tiff",collapse = "",sep="")
#   )
#   }
```


get sensitivity data and summarize by cell
```{r}

```



sanity check:
for 268 drugs, predict their target. 
for 268 drugs, get sensitivity matrix.

```{r}

# prism268_non_oncology_druglist <- prism_268_all %>% 
#   # filter(phase == "Launched") %>%
#   filter(drug_category=="noncancer") %>%
#   pull(drug) 
# 
# prism268_non_oncology_druglist_poorlypredicted <- prism_268_all %>% 
#   filter(phase=="Launched") %>% 
#   filter(drug_category=="noncancer") %>%
#   filter(acc< 0.8) %>%
#   filter(auc<0.8) %>% 
#   pull(drug)

#top and bottom 50 drugs
# top_50pair_prism <-   get_drug_frac(
#   dataset= PRISM_binary_PPIold_data,
#   top_n=50, res_type = "toppair",
#   top_method = "top_both"
#   ) %>%
#   filter(imptype== "ConSen-Sig")

# only top 10
# top_10pair_prism <-  get_drug_frac(
#   dataset= PRISM_binary_PPIold_data,
#   top_n=10, res_type = "toppair",
#   top_method = "top_both"
#   ) %>%
#   filter(imptype== "ConSen-Sig") %>% 
#   filter(impdef== "toppos gene") %>% 
#   group_by(drug) %>% 
#   mutate(rank= rank(-imp)) %>% 
#   ungroup()

# and last, explore only the poorly predicted non-oncology drugs
# tmp1 <- prism_268_all %>%
#   filter(drug_category=="noncancer") %>%
#   filter(acc< 0.7) %>%
#   filter(auc<0.6) %>%


# top_50pair_prism %>%
#   filter(impdef== "toppos gene") %>% 
#   ungroup() %>%
#   group_by(gene) %>%
#   summarise(N=n()) %>%
#   arrange(desc(N))
# 
# top_50pair_prism %>%
#   filter(impdef== "topneg gene") %>% 
#   ungroup() %>%
#   group_by(gene) %>%
#   summarise(N=n()) %>%
#   arrange(desc(N))

# top_10pair_prism %>%
#   ungroup() %>%
#   group_by(gene) %>%
#   summarise(N=n()) %>%
#   arrange(desc(N))

# top_10pair_prism %>%
#   filter(impdef== "topneg gene") %>% 
#   ungroup() %>%
#   group_by(gene) %>%
#   summarise(N=n()) %>%
#   arrange(desc(N))
# 
# # top and bottom pair, what about non-oncology drugs?
# top_10pair_prism %>% 
#   filter(drug %in% prism268_non_oncology_druglist) %>% 
#   filter(impdef== "toppos gene") %>% 
#   ungroup() %>%
#   group_by(gene) %>%
#   summarise(N=n()) %>%
#   arrange(desc(N))
# 
# top_10pair_prism %>% 
#   filter(drug %in% prism268_non_oncology_druglist) %>% 
#   filter(impdef== "topneg gene") %>% 
#   ungroup() %>%
#   group_by(gene) %>%
#   summarise(N=n()) %>%
#   arrange(desc(N))
# 
# top_10pair_prism %>% 
#   filter(drug %in% prism268_non_oncology_druglist) %>% 
#   filter(impdef== "toppos gene") %>% 
#   ungroup() %>%
#   group_by(gene) %>%
#   summarise(N=n()) %>%
#   arrange(desc(N))

# top_10pair_prism %>% 
#   filter(drug %in% prism268_non_oncology_druglist_poorlypredicted) %>% 
#   ungroup() %>%
#   group_by(gene) %>%
#   summarise(N=n()) %>%
#   arrange(desc(N))
# 
# 
# pred1 <- top_10pair_prism %>% 
#   filter(drug %in% prism268_non_oncology_druglist_poorlypredicted) %>% 
#   select(-dataset, -imptype, -imp,-impdef, -anno_type1) %>% 
#   left_join(prism_sc_drug, by= c("drug" = "broad_id")) %>% 
#   # group_by(drug) %>%
#   # arrange(desc(imp), .by_group = TRUE) %>% 
#   mutate(DTC_panel=gene %in% targetpanel_dtc) %>% 
#   left_join(targetpanel_drh_genelevel %>% rename(prism_targeted_drug= drug), by= c("gene"= "target")) %>%
#   rename(top_pos_gene= gene, nominal_target =target ) %>% 
#   left_join(prism_data %>% select(BROAD_ID, sensitivity), by= c("drug" = "BROAD_ID"))  %>% 
#   # mutate(top_sen_cell= map(sensitivity,function(x){x %>%filter(auc < 0.7) %>%  pull(depmap_id)})) %>% 
#   # select(-sensitivity) %>%
#   filter(DTC_panel) %>%
#   left_join(prism_data %>% select(BROAD_ID, name),by=c("drug"= "BROAD_ID")) %>% 
#   select(drug, name, nominal_target, moa, top_pos_gene, rank,DTC_panel, prism_targeted_drug,sensitivity ) %>% filter(drug!="BRD-K93779381")
#   
# 
# 
# # add cell line info..   
# pred1_celllevel <- pred1 %>% 
#   select(drug) %>% 
#   distinct() %>% 
#   left_join(prism_data %>% select(BROAD_ID, sensitivity), by= c("drug" = "BROAD_ID"))  %>% 
#   # mutate(sensitivity= map( sensitivity, function(df){df %>% filter(auc < 0.7) })) %>% 
#   mutate(top_sen_cell= map(sensitivity,function(x){x %>%filter(auc < 0.8) %>%  pull(depmap_id)})) %>% 
#   select(-sensitivity) %>% 
#   unnest()  %>% 
#   inner_join(cell_line_info, by= c("top_sen_cell"= "DepMap_ID"))
# 
# # sum(tmp$gene %in% targetpanel)
# setwd("~/cluster_wrk/drug_moa/predicting_prism")
# pred1  %>% select(-sensitivity) %>% write_csv("incorrectdrug_druglevel.csv" )
# # write_csv(pred1_celllevel, "incorrectdrug_celllevel.csv" )
```

get the top 10 target for supervised prediction
```{r}
# source('~/cluster_wrk/drug_moa/supervised_target_pred/no_tunning_weighted_averaging.R')
# 
# predictors_mat <- feature_imp_ridge_prism_comb1 %>% 
#   filter(drug %in% prism_good_fitted_drugs_annotated) %>% 
#   arrange(drug) %>% 
#   select(-drug) %>% 
#   mutate_all(.funs = scale)
# test_idx <- which(prism_good_fitted_drugs_annotated %in%  unique(tmp1$drug) )
# cor_mat = cor(t(predictors_mat),method = "spearman") %>% replace(is.na(.), 0)
# cor_mat[cor_mat< 0 ] <- 0 
# 
# target_mat <- get_target_mat(target_tibble = 
#                                prism_target_binary %>% 
#                                filter(drug %in% prism_good_fitted_drugs_annotated) %>% 
#                                filter(!(drug %in% unique(tmp1$drug))) %>% 
#                                arrange(drug))
# 
#   
# tmp2 <-   no_tunning_weighted_averaging(
#   
#   target_mat = target_mat,
#   cor_mat = cor_mat,
#   test_idx = test_idx,
#   pred_new=T
#   )
# 
# # row.names(tmp2) <- prism_good_fitted_drugs_annotated[test_idx]
# tmp3 <- bind_cols(drug=prism_good_fitted_drugs_annotated[test_idx],  as_tibble(tmp2)) %>% 
#   pivot_longer(cols = -drug, names_to= "gene",values_to= "pred") %>% 
#   group_by(drug) %>% 
#   slice_max(order_by = pred, n=5) %>% 
#   arrange(desc(pred), .by_group = TRUE)
# 
# 
# # join supervised and unsupervised prediction result
# 
# tmp4 <- inner_join(top_pair_prism, tmp3, by= c("drug","gene"))
# 
# # no good overlapping result!
```



also get the proved, non-oncology drugs that no nominal target info is available
```{r}
# prism_good_fitted_nononcologydrugs_notannotated <- prism_sc_drug %>% 
#   filter(broad_id %in% setdiff(prism_good_fitted_drugs, prism_good_fitted_drugs_annotated)) %>% 
#   filter(phase=="Launched") %>% 
#   filter(drug_category== "noncancer")
# 
# pred2 <- feature_imp_ridge_prism_comb1 %>% 
#   filter(drug %in% prism_good_fitted_nononcologydrugs_notannotated$broad_id) %>% 
#   pivot_longer(cols= - drug, names_to= "gene", values_to = "imp") %>% 
#   group_by(drug) %>% 
#   slice_max(order_by = imp,n=10) %>% 
#   group_by(drug) %>% 
#   mutate(rank= rank(-imp)) %>% 
#   ungroup() %>% 
#   inner_join(prism_good_fitted_nononcologydrugs_notannotated, by= c("drug" = "broad_id")) %>%
#   inner_join(prism_data %>% select(-target, - sensitivity, -moa, -drug_category), by=c("drug"= "BROAD_ID") )%>% 
#   mutate(DTC_panel=gene %in% targetpanel_dtc) %>% 
#   left_join(targetpanel_drh_genelevel %>% rename(prism_targeted_drug= drug), by= c("gene"= "target")) %>%
#   rename(top_pos_gene= gene, nominal_target =target ) %>% 
#   left_join(prism_data %>% select(BROAD_ID, sensitivity), by= c("drug" = "BROAD_ID"))  %>% 
#   # mutate(top_sen_cell= map(sensitivity,function(x){x %>%filter(auc < 0.7) %>%  pull(depmap_id)})) %>% 
#   filter(DTC_panel ) %>% 
#   select(drug, name, moa, top_pos_gene, rank,DTC_panel, prism_targeted_drug,sensitivity ) 
#   
# pred2_celllevel <- pred2 %>%
#   select(drug) %>% 
#   distinct() %>% 
#   left_join(prism_data %>% select(BROAD_ID, sensitivity), by= c("drug" = "BROAD_ID"))  %>% 
#   # mutate(sensitivity= map( sensitivity, function(df){df %>% filter(auc < 0.7) })) %>% 
#   mutate(top_sen_cell= map(sensitivity,function(x){x %>%filter(auc < 0.7) %>%  pull(depmap_id)})) %>% 
#   select(-sensitivity) %>% 
#   unnest()  %>% 
#   inner_join(cell_line_info, by= c("top_sen_cell"= "DepMap_ID"))
# 
# pred2 %>%  select(-sensitivity) %>% write_csv("notargetdrug_druglevel.csv")
# 
# cell_level <- bind_rows(pred1_celllevel, pred2_celllevel)%>% 
#   distinct()
#   # add_count(top_sen_cell) %>%select(-drug)%>%
#   # arrange(desc(n))
#   
#   
# # write_csv(cell_level, "cell_level.csv")
# 
# # sum(tmp$gene %in% targetpanel)
# # sum(top_10pair_prism$gene %in% targetpanel)
```


```{r}
# tmp <- feature_imp_ridge_prism_comb1 %>% 
#   filter(drug %in% c("BRD-K75958547", "BRD-K66296774", "BRD-K69726342")) %>% 
#   pivot_longer(cols= -drug,names_to = "gene",values_to = "value") %>% 
#   pivot_wider(id_cols = gene, names_from= drug, values_from= value)
# 
# tmp %>% select(-gene) %>% cor(method = "spearman")
# 
# tmp1= feature_imp_ridge_prism_comb1 %>% 
#   filter(drug %in% prism_good_fitted_drugs_annotated) %>% 
#   pivot_longer(cols= -drug,names_to = "gene",values_to = "value") %>% 
#   pivot_wider(id_cols = gene, names_from= drug, values_from= value)
# tmp2 = cor(tmp$`BRD-K66296774`, tmp1 %>% select(-gene),method = "spearman" )
# hist(tmp2)
```

