---
title: "Non-oncology drug exploration"
output: html_document
---

```{r, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
load("~/cluster_scratch/forward_modelling/targetpred_output_simplefiltering.RData")
rm(get_target_mat)
rm(no_tunning_weighted_averaging)
rm(get_target_pred_accuracy_batch)
rm(return_acc_estimate_cv)
# note the unsupervised auc is precalculated in get_unsupervised_target_prediction_auc.R code
load("~/cluster_scratch/unsupervised_target_pred/unsupervised_target_pred_ConSenSig.RData")

library(tidyverse)
library(ggsci)
source("./function/get_drug_frac.R")
prism_sc_drug <- read_csv("~/cluster_scratch/prism/drug_repurposing_scdrugsmeta.csv")

targetpanel_dtc <- data.table::fread("~/cluster_scratch/prior/DTC_data_all.csv",
                                 select = c("gene_names")) %>% distinct() %>% pull(gene_names)

cell_line_info <- data.table::fread("~/cluster_scratch/depmap_21q1/sampleinfo")

targetpanel_drh <- read_tsv("~/cluster_scratch/prior/repurposing_drugs_20200324.txt") %>% 
  select(-disease_area, -indication) %>% 
  drop_na() %>% 
  separate_rows(target) %>% 
  distinct() 

targetpanel_drh_genelevel <- targetpanel_drh %>% 
  select(pert_iname, target) %>% 
  group_by(target) %>% 
  summarise(drug= paste(pert_iname,collapse = ","))

length(unique(targetpanel_drh$target))   # 1943 genes

cellline_hgsoc <- cell_line_info %>% 
  filter(primary_disease== "Ovarian Cancer") %>% 
  filter(Subtype== "Adenocarcinoma, high grade serous")

senvalid_20drugs <- read_csv("~/cluster_wrk/drug_moa/predicting_prism/res_final.csv")
```


Supplementary figure. Plot the model fitness for PRISM drug sensitivity.
```{r,fig.width=3, fig.height=2}
res_prism2_long <- res_prism2
res_prism2 <- res_prism2_long %>%
  select(-variance) %>% 
  filter(.metric== "spearman coef") %>%
  pivot_wider(names_from = input, values_from= estimate) %>%
  mutate(acc_sen= (ceres+ces+demeter2)/3) %>%
  distinct() 
# distribution of acc for 1448 drugs
# res_prism2 %>% 
#   ggplot(aes(x= reorder(drug_id, acc_sen), y= acc_sen))+
#   geom_point(size=0.1)+
#   geom_hline(yintercept = 0.2, color="red", lty=2)+
#   theme_classic()+
#   ylab("Model Fitness (Spearman COR)")+
#   theme(axis.ticks.x = element_blank(),
#         axis.title.x = element_blank(),
#         axis.text.x = element_blank())

fig <- res_prism2 %>% 
  ggplot(aes(x= acc_sen))+
  geom_histogram(size=0.1)+
  geom_vline(xintercept = 0.2, color="red", lty=2)+
  theme_classic()+
  xlab("Model Fitness (Spearman COR)")+
  ylab("Number of drugs")
  # theme(axis.ticks.x = element_blank(),
  #       axis.title.x = element_blank(),
  #       axis.text.x = element_blank())
fig
ggsave(plot = fig, filename = "./fig_res/supplmentary_figure6.pdf",width = 3,height = 2)
ggsave(plot = fig, filename = "./fig_res/supplmentary_figure6.png",width = 3,height = 2,dpi = 500)
```


```{r}
prism_good_fitted_drugs <- res_prism2 %>%
  filter(sample_size>100) %>%
  filter(acc_sen>0.2) %>%
  arrange(BROAD_ID)
# n=312, 199 targeted cancer drugs, 50 chemo drugs and 63 noncancer drugs.

# how many non-oncology drugs? N= 63
prism_good_fitted_nononcologydrugs <-  prism_good_fitted_drugs %>% 
  filter(drug_category== "noncancer") %>% 
  arrange(BROAD_ID ) %>% 
  pull(BROAD_ID) %>% 
  unique()

# drh annotation include both MOA and target info N=268, this will be my train set
prism_good_fitted_drugs_drhannotated <- prism_good_fitted_drugs %>% 
  select(BROAD_ID, moa) %>% 
  drop_na() %>% 
  filter(BROAD_ID %in% prism_target_binary$drug) %>% 
  pull(BROAD_ID)
  
# DTC only care about target gene but not moa annotation: N= 52
prism_good_fitted_drugs_dtcannotated <- prism_good_fitted_drugs %>% 
  filter(BROAD_ID %in% prism_target_dtc$drug) %>% 
  pull(BROAD_ID)

# 46 = 58-13 +1 1 drug no moa but have target.
# prism_good_fitted_nononcologydrugs_drhannotated <- intersect(prism_good_fitted_drugs_drhannotated, prism_good_fitted_nononcologydrugs)
# 
# prism_good_fitted_nononcologydrugs_drhnotannotated <- setdiff(prism_good_fitted_drugs_drhannotated, prism_good_fitted_nononcologydrugs)

# prism_good_fitted_nononcologydrugs <-  prism_good_fitted_drugs %>% 
#   filter(drug_category== "noncancer") %>% 
#   arrange(BROAD_ID ) %>% 
#   filter(is.na(moa))
```


Get supervised and nonsupervised prediction accuracy
```{r}

acc_unsupervised_prism268 <- prism_unsupervised_auc %>% 
  filter(drug %in% prism_good_fitted_drugs_drhannotated) 

setwd("~/cluster_wrk/drug_moa/supervised_target_pred/function/")
source('return_acc_estimate_loocv.R') 
acc_supervised_prism268 <- return_acc_estimate_cv(
  target_tibble = prism_target_binary %>% 
    filter(drug %in% prism_good_fitted_drugs_drhannotated) %>% 
    arrange(drug),
  predictors_tibble = feature_imp_ridge_prism_comb1 %>% 
    filter(drug %in% prism_good_fitted_drugs_drhannotated)%>% 
    arrange(drug)
  )

prism_268_all <- acc_supervised_prism268 %>% 
  left_join(acc_unsupervised_prism268) %>% 
  left_join(prism_data %>% select_at(c(1:5,8)),by= c("drug" = "BROAD_ID") ) %>%
  mutate(Drug_category= case_when(drug_category== "noncancer"~ drug_category,
                                  TRUE ~ "cancer") ) %>% 
  left_join(prism_sc_drug %>% select_at(c(1,2,4)),by= c("drug" = "broad_id")) %>% 
  rename(supervised_auc= acc) %>% 
  rename(unsupervised_auc = auc) %>% 
  rename(sample_size= n_forward_modelling) %>% 
  select(drug, name, drug_category,Drug_category, moa,target,phase, supervised_auc, unsupervised_auc,sample_size)

```

check the median accuracy and significance
```{r}
prism_268_all %>% 
  group_by(drug_category) %>%
  summarise(
    N= n(),
    median_unsupervised= round(median(unsupervised_auc, na.rm = T),2),
    median_supervised= round(median(supervised_auc),2),
    ) 

prism_268_all %>% 
  group_by(Drug_category) %>%
  summarise(
    N= n(),
    median_unsupervised= round(median(unsupervised_auc, na.rm = T),2),
    median_supervised= round(median(supervised_auc),2),
    ) 

prism_268_all %>% 
  t_test(supervised_auc~Drug_category)
prism_268_all %>% 
  t_test(unsupervised_auc~Drug_category)
```

```{r,fig.width=3,fig.height=3.6}
# fig <- prism_268_all %>% 
#   ggplot(aes(x= supervised_auc, y= unsupervised_auc, color= drug_category)) + 
#   geom_point(size = 0.5)+
#   theme_classic()+
#   ylab("Supervised prediction accuracy (AUC)")+
#   xlab("Unsupervised prediction accuracy (AUC)")+
#   guides(color= guide_legend(title = "Drug Category"))+
#   theme(legend.position="bottom")+
#   # theme(
#   #   legend.position = c(1, 0.00),
#   #   legend.justification = c("right", "bottom"),
#   #   legend.box.just = "right"
#   #   )+
#   ggsci::scale_color_aaas()
# fig <- ggExtra::ggMarginal(fig,type= "boxplot",groupColour = T,groupFill = T)
# fig

fig <- prism_268_all %>%
  mutate(Drug_category= factor(Drug_category,
                               levels= c("noncancer", "cancer"),
                               labels = c("Noncancer", "Cancer"))) %>% 
  ggplot(aes(x= supervised_auc, y= unsupervised_auc, color= Drug_category)) +
  geom_point(size = 0.5)+
  theme_classic()+
  ylab("Unsupervised prediction accuracy (AUC)")+
  xlab("Supervised prediction accuracy (AUC)")+
  guides(color= guide_legend(title = "Drug Category"))+
  theme(legend.position="bottom",legend.title = element_blank())+
  # theme(
  #   legend.position = c(1, 0.00),
  #   legend.justification = c("right", "bottom"),
  #   legend.box.just = "right"
  #   )+
  ggsci::scale_color_npg()
fig <- ggExtra::ggMarginal(fig,type= "boxplot",groupColour = T,groupFill = T)
fig
ggsave(fig,filename = "./fig_res/fig6a.png",width = 3,height = 3.6,dpi = 500)
ggsave(fig,filename = "./fig_res/fig6a.pdf",device = "pdf",width = 3,height = 3.6)
```



Showing how target of noncancer drugs overlapped poorly with cancer drugs
```{r,fig.width=3,fig.height=3}
# Distribution of number of drugs with at least one shared target
tmp <- inner_join(prism_target_binary, prism_268_all %>% select(drug, Drug_category))
tmp1 <- prism_268_all %>% 
  # select(drug, Drug_category) %>% 
  mutate(N_shared= map_int(prism_good_fitted_drugs_drhannotated, function(x){
    gene <- tmp %>% filter(drug == x) %>% pull(target)
    N= tmp %>% filter(!(drug %in% x)) %>% filter(target %in% gene) %>% select(drug) %>% distinct() %>% nrow()
    return(N)
  }))

fig <- tmp1 %>% 
  mutate(Drug_category= factor(Drug_category,
                               levels= c("noncancer", "cancer"),
                               labels = c("Noncancer", "Cancer"))) %>% 
  ggplot(aes(x= N_shared, fill= Drug_category))+
  geom_density(alpha=0.5)+
  theme_classic()+
  theme(
    legend.position = c(1, 0.5),
    legend.justification = c("right", "bottom"),
    legend.box.just = "right"
    )+
  ggsci::scale_fill_npg()+
  xlab("Number of drugs with shared targets")+
  ylab("Density")+
  guides(color= guide_legend(title = "Drug Category"))+
  theme(legend.title = element_blank())
fig
ggsave(fig,filename = "./fig_res/fig6b.png",width = 3,height = 3,dpi = 500)
ggsave(fig,filename = "./fig_res/fig6b.pdf",device = "pdf",width = 3,height = 3)
```


```{r,fig.width=3,fig.height=3}
fig <- tmp1 %>% 
  mutate(bin= case_when(N_shared<1 ~ "0",
                        between(N_shared, 1,5)~"1-5",
                        between(N_shared, 6,10)~"6-10",
                       between(N_shared, 10,20)~"10-20",
                        TRUE~">20")) %>% 
  mutate(bin= fct_relevel(bin, c("0", "1-5", "6-10","10-20", ">20")) ) %>%
  ggplot(aes(x = bin, y = supervised_auc)) +
  geom_violin(trim = T)+
  ggpubr::stat_compare_means(
    aes(group=bin),label = "p.signif",vjust = 0.4,
    method = "t.test",ref.group = "0")+
  stat_summary(fun.data = "mean_cl_boot", geom = "pointrange",
             colour = "red",fatten=0.5,
             # size= 0.1,
             position = position_dodge(width = 0.9))+
  theme_classic()+
  ylab("Supervised prediction accuracy (AUC)")+
  xlab("Number of drugs with shared targets")+
  guides(fill= guide_legend(title = "prediction method"))

fig
ggsave(fig,filename = "./fig_res/fig6c.png",width = 3,height = 3,dpi = 500)
ggsave(fig,filename = "./fig_res/fig6c.pdf",device = "pdf",width = 3,height = 3)
```


```{r,fig.width=3,fig.height=3}
# fig <- tmp1 %>% 
#   # ggplot() +
#   # geom_point(aes(x= N_shared, y= acc))
#   # mutate(bin = cut_width(N_shared, width = 10,boundary = 0)) %>% 
#   mutate(bin= case_when(N_shared<1 ~ "0",
#                         between(N_shared, 1,5)~"1-5",
#                          between(N_shared, 6,20)~"6-20",
#                         TRUE~">20")) %>% 
#   mutate(bin= fct_relevel(bin, c("0", "1-5", "6-20", ">20")) ) %>%
#   pivot_longer(cols= supervised_auc:unsupervised_auc, 
#                names_to= "prediction_method",
#                values_to= "AUC") %>% 
#   ggplot(aes(x = bin, y = AUC, fill= prediction_method)) +
#   geom_violin()+
#   stat_summary(fun.data = "mean_cl_boot", geom = "pointrange",
#              # colour = "black",
#              size= 0.2,
#              position = position_dodge(width = 0.9))+
#   theme_classic()+
#   # ylab("Supervised target prediction accuracy (AUC)")+
#   ylab("AUC")+
#   xlab("Number of drugs with shared targets")+
#   guides(fill= guide_legend(title = "prediction method"))
# 
# fig
# ggsave(fig,filename = "~/cluster_wrk/drug_moa/predicting_prism/fig_res/fig6c.tiff",device = "tiff",width = 3,height = 3.5,units = "in",dpi = 300)
# ggsave(fig,filename = "~/cluster_wrk/drug_moa/predicting_prism/fig_res/fig6c.pdf",device = "pdf",width = 3,height = 3.5)


# tmp1 %>% 
#   filter(Drug_category== "noncancer") %>% 
#     mutate(bin= case_when(N_shared<1 ~ "0",
#                         between(N_shared, 1,5)~"1-5",
#                          between(N_shared, 6,20)~"6-20",
#                         TRUE~">20")) %>% 
#   mutate(bin= fct_relevel(bin, c("0", "1-5", "6-20", ">20")) ) %>%
#   pivot_longer(cols= supervised_auc:unsupervised_auc, 
#                names_to= "prediction_method",
#                values_to= "AUC") %>% 
#   ggplot(aes(x = bin, y = AUC, fill= prediction_method)) +
#   geom_boxplot()+
#   facet_wrap(~Drug_category)
  
```



filter or not filter to category of interest before tSNE?

(filter out small category and keep the big ones)
tSNE parameters

finetuning based on large categories of cancer drugs.

think about conclusion to be made from this plot

 
```{r}
cancer_drug_category <- prism_268_all %>% 
  filter(Drug_category=="cancer") %>% 
  add_count(moa) %>% 
  ungroup() %>% 
  filter(n>4) %>% 
  arrange(drug)

noncancer_category <- prism_data %>% 
  drop_na() %>% 
  select(-target, -sensitivity) %>% 
  filter(BROAD_ID  %in% prism_good_fitted_drugs$BROAD_ID) %>% 
  filter(drug_category=="noncancer") %>% 
  add_count(moa) %>% 
  ungroup() %>% 
  filter(n>2)
```

tSNE
```{r}
# 
# set.seed(1234)
# dimreduction_df <- feature_imp_ridge_prism_comb1 %>% 
#   filter(drug %in% prism_good_fitted_drugs_drhannotated) %>%
#     # filter(drug %in% cancer_drug_category$drug) %>%
#   arrange(drug) %>% 
#   column_to_rownames("drug") %>%
#   scale() %>% 
#   Rtsne::Rtsne(
#     perplexity = 10,
#     theta = 0.5,
#     check_duplicates = TRUE,
#     pca = TRUE,
#     partial_pca = FALSE
#   ) %>% 
#   pluck(2) %>% 
#   as.data.frame() %>%
#   rename(tSNE1="V1",
#          tSNE2="V2") %>% 
#   # bind_cols(cancer_drug_category)
#   bind_cols(prism_268_all)
#   
# ggplot()+
#   geom_point(data = dimreduction_df %>% 
#                filter( Drug_category !="noncancer") %>% 
#                filter(moa %in% cancer_drug_category$moa),
#              mapping = aes(x = tSNE1, y = tSNE2, color = moa), 
#              shape= 2)+
#   geom_point(data =  dimreduction_df %>% filter( Drug_category =="noncancer"),
#              mapping = aes(x = tSNE1, y = tSNE2, shape= Drug_category)
#              )+
#   theme_classic()
```

how about UMAP
predicted target include the primary target of the category_
whether it is tested in our further experiment.

```{r}
set.seed(1234)
dimreduction_df <- feature_imp_ridge_prism_comb1 %>% 
  filter(drug %in% prism_good_fitted_drugs_drhannotated) %>% 
  filter(drug %in% prism_good_fitted_drugs$BROAD_ID) %>% 
  arrange(drug) %>% 
  column_to_rownames("drug") %>%
  scale() %>% 
  umap::umap() %>% 
  pluck(1) %>% 
  as.data.frame() %>%
  rename(umap1="V1",
         umap2="V2") %>% 
  rownames_to_column(var = "drug") %>% 
  inner_join(prism_data %>% select_at(1:4), by= c("drug"= "BROAD_ID")) %>% 
  mutate(validated= drug %in% senvalid_20drugs$drugid) %>% 
  mutate(interested= name %in% c("CGS-15943","MRS-1220", 
                                 "domperidone", "pardoprunox",
                                 "sirolimus", "LY2183240", 
                                 "podophyllotoxin","albendazole","parbendazole" ))  %>% 
  mutate(interested2= (moa == "HMGCR inhibitor") ) 

dimreduction_df$moa[dimreduction_df$name== "pardoprunox"] <-  "dopamine receptor agonist"
dimreduction_df$moa[dimreduction_df$name== "podophyllotoxin"] <-  "tubulin polymerization inhibitor"
dimreduction_df$moa[dimreduction_df$name== "LY2183240"] <-  "FAAH inhibitor"

```

Figure 6D
```{r, fig.width=9,fig.height=4.5}
fig <- ggplot()+
  geom_point(data = dimreduction_df %>% 
               filter( drug_category !="noncancer") %>% 
               filter(moa %in% cancer_drug_category$moa),
             mapping = aes(x = umap1, y = umap2, color = moa), 
             shape= 2)+
  geom_point(data =  dimreduction_df %>% filter( drug_category =="noncancer"),
             mapping = aes(x = umap1, y = umap2, shape= drug_category) 
             )+
  ggrepel::geom_text_repel(
    data =  dimreduction_df %>% 
      filter(name %in% c("sirolimus", "LY2183240")),
           mapping = aes(x = umap1, y = umap2, label= name) ,color= "black"
           )+
  # ggrepel::geom_text_repel(
  #   data =  dimreduction_df %>%
  #     filter(name %in% c("CGS-15943","MRS-1220",
  #                        "domperidone", "pardoprunox",
  #                        "podophyllotoxin","albendazole","parbendazole" )),
  #          mapping = aes(x = umap1, y = umap2, label= name, color= moa) ,legend = FALSE
  #          )+
    ggrepel::geom_text_repel(data =  dimreduction_df %>%
                               filter(name %in% c("domperidone", "pardoprunox")),
           mapping = aes(x = umap1, y = umap2, label= name) ,color= "red"
           )+
    ggrepel::geom_text_repel(data =  dimreduction_df %>%
                               filter(name %in% c("parbendazole", "albendazole", "podophyllotoxin")),
           mapping = aes(x = umap1, y = umap2, label= name) ,color= "deepskyblue4"
           )+
    ggrepel::geom_text_repel(data =  dimreduction_df %>%
                                 filter(name %in% c("CGS-15943", "MRS-1220")),
           mapping = aes(x = umap1, y = umap2, label= name) ,color= "green"
           )+
    ggrepel::geom_label_repel(data =  dimreduction_df %>%
                                 filter(moa %in% "HMGCR inhibitor"),
           mapping = aes(x = umap1, y = umap2, label= name) ,color= "cornsilk4"
           )+
  theme_classic()+
  theme(legend.title = element_blank())+
  xlab("UMAP1")+
  ylab("UMAP2")

fig

ggsave(fig,filename = "./fig_res/fig6d.png",width = 9,height = 4.5,dpi = 500)
ggsave(fig,filename = "./fig_res/fig6d.pdf",device = "pdf",width = 9,height = 4.5)
```


lets do a supervised umap to see if we get better results
```{r}
# library(embed)
# 
# tr <- feature_imp_ridge_prism_comb1 %>% 
#   filter(drug %in% cancer_drug_category$drug) %>%
#   # filter(drug %in% prism_268_all$drug) %>% 
#   inner_join(prism_data %>% select(BROAD_ID, moa), by =c("drug"= "BROAD_ID")) %>% 
#   arrange(drug) %>%   
#   column_to_rownames("drug") 
# 
# te <- feature_imp_ridge_prism_comb1 %>% 
#   filter(drug %in% prism_good_fitted_nononcologydrugs) %>%
#   # inner_join(prism_data %>% select(BROAD_ID, moa), by =c("drug"= "BROAD_ID")) %>% 
#   mutate(moa= "noncancer_drugs") %>% 
#   arrange(drug) %>%   
#   column_to_rownames("drug") 
# 
# set.seed(1234)
# supervised <- recipe(moa ~ ., data = tr) %>%
#   step_normalize(all_predictors()) %>% 
#   step_umap(all_predictors(), outcome = vars(moa), num_comp = 2
#             # ,  learn_rate = 0.05,epochs = 10000
#             ) %>% 
#   prep(training = tr)
# 
# # tr_umap <- bake(supervised, new_data = tr, moa, starts_with("umap"))
# tr_umap <- juice(supervised) %>% mutate(drug= rownames(tr)) %>% 
#     inner_join(prism_268_all) %>% 
#   mutate(validated= drug %in% senvalid_20drugs$drugid)
# 
# te_umap <- bake(supervised, new_data = te, starts_with("umap"))%>% mutate(drug= rownames(te)) %>% 
#     inner_join(prism_data %>% select_at(1:4), by= c("drug"= "BROAD_ID")) %>% 
#   mutate(validated= drug %in% senvalid_20drugs$drugid)
# 
# ggplot() + 
#   geom_point(
#     data = tr_umap %>% filter(moa %in% cancer_drug_category$moa) ,
#     mapping = aes(x = UMAP1, y = UMAP2,color= moa),
#     shape=2,
#     alpha = 1)+
#   # geom_text(data = tr_umap %>% filter(moa %in% cancer_drug_category$moa),
#   #           aes(x = UMAP1, y = UMAP2,label= moa),check_overlap = TRUE, hjust = "inward") +
#   geom_point(data = te_umap, mapping = aes(x = UMAP1, y = UMAP2), size=0.7) +
#   theme_classic()

```

```{r}
# set.seed(1234)
# dimreduction_df <- feature_imp_ridge_prism_comb1 %>% 
#   # filter(drug %in% prism_good_fitted_drugs$BROAD_ID) %>% 
#   filter(drug %in% prism_268_all$drug) %>% 
#   arrange(drug) %>% 
#   column_to_rownames("drug") %>% 
#   umap::umap() %>% 
#   pluck(1) %>% 
#   as.data.frame() %>%
#   rename(DIM1="V1",
#          DIM2="V2") %>% 
#   rownames_to_column(".rownames")
# 
# ggplot()+
#   geom_point(data = dimreduction_df %>% 
#                filter( Drug_category !="noncancer") %>% 
#                filter(moa %in% cancer_drug_category$moa),
#              mapping = aes(x = tSNE1, y = tSNE2, color = moa), 
#              shape= 2)+
#   geom_point(data =  dimreduction_df %>% filter( Drug_category =="noncancer"),
#              mapping = aes(x = tSNE1, y = tSNE2, shape= Drug_category) 
#              )+
#   theme_classic()+
#   xlab("UMAP1")+
#   ylab("UMAP2")
```



Jing proposed 4 changes
1) use all 312 drugs rather than the 268 drugs
2) filter down to 1k most variable genes
3) PCA to 50 - 100 pc
4) plot either first two PC, or do additional dim reduction with tSNE or UMAP

```{r}
# cancer_drug_category1 <- prism_data %>% 
#   select(-target, -sensitivity) %>% 
#   filter(BROAD_ID %in% prism_good_fitted_drugs_drhannotated) %>% 
#   filter(drug_category != "nonancer") %>% 
#   add_count(moa) %>% 
#   ungroup() %>% 
#   filter(n>4) %>% 
#   select(-n) %>% 
#   mutate(category= moa)
# 
# cancer_drug_category2 <- prism_data %>% 
#   select(-target, -sensitivity) %>% 
#   filter(BROAD_ID  %in% prism_good_fitted_drugs$BROAD_ID) %>% 
#   filter(drug_category=="noncancer") %>% 
#   mutate(category= moa)
# 
# noncancer_categoryofinterest = names(sort(table(cancer_drug_category2$category),decreasing = T)[1:7])
# 
# 
# # cancer_drug_category3 <- union(cancer_drug_category1,cancer_drug_category2)
# 
# # cancer_drug_category_ploting <- cancer_drug_category3 %>% select(BROAD_ID, moa,category)
# 
# # dimreduction_df <- feature_imp_ridge_prism_comb1 %>% 
# #   filter(drug %in% prism_good_fitted_drugs$BROAD_ID) %>% 
# #   arrange(drug) %>% 
# #   column_to_rownames("drug") #%>%
#   # scale()
# 
# # top1kgene <- names(sort(apply(dimreduction_df,2, var),decreasing = T))[1:1000]
# 
# dimreduction_df <- feature_imp_ridge_prism_comb1 %>% 
#   # filter(drug %in% prism_good_fitted_drugs$BROAD_ID) %>% 
#   filter(drug %in% prism_268_all$drug) %>% 
#   arrange(drug) %>% 
#   column_to_rownames("drug")# %>% 
#   # select(one_of(top1kgene)) %>%
#   # select_at(1:101)
# 
# set.seed(1234)
# # dimreduction_df_PCA <- dimreduction_df %>% 
# #   scale() %>% 
# #   prcomp() %>% 
# #   augment() %>% 
# #   select_at(1:3) %>% 
# #   rename(DIM1=".fittedPC1",
# #          DIM2=".fittedPC2")
# 
# dimreduction_df_tsne <-dimreduction_df %>% 
#   # column_to_rownames(".rownames") %>%
#   # scale() %>% 
#   Rtsne::Rtsne() %>% 
#   pluck(2) %>% 
#   as.data.frame() %>%
#   rename(DIM1="V1",
#          DIM2="V2") %>%
#   mutate(`.rownames` = row.names(dimreduction_df))
#   # bind_cols(dimreduction_df %>% select(`.rownames`) )
# 
# 
# dimreduction_df_umap  <-dimreduction_df %>% 
#   # column_to_rownames(".rownames") %>%
#   # scale() %>% 
#   umap::umap() %>% 
#   pluck(1) %>% 
#   as.data.frame() %>%
#   rename(DIM1="V1",
#          DIM2="V2") %>% 
#   rownames_to_column(".rownames")
#   
```



```{r,fig.height=15, fig.width=5}
# p1 <- ggplot()+
#   geom_point(data =  dimreduction_df_PCA %>% 
#                inner_join( cancer_drug_category2, by= c(".rownames"= "BROAD_ID")),
#              mapping = aes(x = DIM1, y = DIM2) ,
#              shape= 1)+
#   geom_point(data = dimreduction_df_PCA %>% 
#                inner_join( cancer_drug_category1, by= c(".rownames"= "BROAD_ID")),
#              mapping = aes(x = DIM1, y = DIM2, color = category), 
#              shape= 2)+
#   theme_classic()+
#   ggtitle("PCA")
# 
# p2 <- ggplot()+
#   geom_point(data =  dimreduction_df_tsne %>% 
#                inner_join( cancer_drug_category2, by= c(".rownames"= "BROAD_ID")),
#              mapping = aes(x = DIM1, y = DIM2) ,
#              shape= 1)+
#   geom_point(data = dimreduction_df_tsne %>% 
#                inner_join( cancer_drug_category1, by= c(".rownames"= "BROAD_ID")),
#              mapping = aes(x = DIM1, y = DIM2, color = category), 
#              shape= 2)+
#   theme_classic()+
#   ggtitle("tsne")
# 
# p3 <- ggplot()+
#   geom_point(data =  dimreduction_df_umap %>% 
#                inner_join( cancer_drug_category2, by= c(".rownames"= "BROAD_ID")),
#              mapping = aes(x = DIM1, y = DIM2) ,
#              shape= 1)+
#   geom_point(data = dimreduction_df_umap %>% 
#                inner_join( cancer_drug_category1, by= c(".rownames"= "BROAD_ID")),
#              mapping = aes(x = DIM1, y = DIM2, color = category), 
#              shape= 2)+
#   theme_classic()+
#   ggtitle("umap")
# 
# p <- ggpubr::ggarrange(p1, p2, p3,ncol = 1,nrow = 3, common.legend = T,widths = 10,heights = 15)
# p
```


sanity check:
for 268 drugs, predict their target. 
for 268 drugs, get sensitivity matrix.

```{r}

# prism268_non_oncology_druglist <- prism_268_all %>% 
#   # filter(phase == "Launched") %>%
#   filter(drug_category=="noncancer") %>%
#   pull(drug) 
# 
# prism268_non_oncology_druglist_poorlypredicted <- prism_268_all %>% 
#   filter(phase=="Launched") %>% 
#   filter(drug_category=="noncancer") %>%
#   filter(acc< 0.8) %>%
#   filter(auc<0.8) %>% 
#   pull(drug)

#top and bottom 50 drugs
# top_50pair_prism <-   get_drug_frac(
#   dataset= PRISM_binary_PPIold_data,
#   top_n=50, res_type = "toppair",
#   top_method = "top_both"
#   ) %>%
#   filter(imptype== "ConSen-Sig")

# only top 10
# top_10pair_prism <-  get_drug_frac(
#   dataset= PRISM_binary_PPIold_data,
#   top_n=10, res_type = "toppair",
#   top_method = "top_both"
#   ) %>%
#   filter(imptype== "ConSen-Sig") %>% 
#   filter(impdef== "toppos gene") %>% 
#   group_by(drug) %>% 
#   mutate(rank= rank(-imp)) %>% 
#   ungroup()

# and last, explore only the poorly predicted non-oncology drugs
# tmp1 <- prism_268_all %>%
#   filter(drug_category=="noncancer") %>%
#   filter(acc< 0.7) %>%
#   filter(auc<0.6) %>%


# top_50pair_prism %>%
#   filter(impdef== "toppos gene") %>% 
#   ungroup() %>%
#   group_by(gene) %>%
#   summarise(N=n()) %>%
#   arrange(desc(N))
# 
# top_50pair_prism %>%
#   filter(impdef== "topneg gene") %>% 
#   ungroup() %>%
#   group_by(gene) %>%
#   summarise(N=n()) %>%
#   arrange(desc(N))

# top_10pair_prism %>%
#   ungroup() %>%
#   group_by(gene) %>%
#   summarise(N=n()) %>%
#   arrange(desc(N))

# top_10pair_prism %>%
#   filter(impdef== "topneg gene") %>% 
#   ungroup() %>%
#   group_by(gene) %>%
#   summarise(N=n()) %>%
#   arrange(desc(N))
# 
# # top and bottom pair, what about non-oncology drugs?
# top_10pair_prism %>% 
#   filter(drug %in% prism268_non_oncology_druglist) %>% 
#   filter(impdef== "toppos gene") %>% 
#   ungroup() %>%
#   group_by(gene) %>%
#   summarise(N=n()) %>%
#   arrange(desc(N))
# 
# top_10pair_prism %>% 
#   filter(drug %in% prism268_non_oncology_druglist) %>% 
#   filter(impdef== "topneg gene") %>% 
#   ungroup() %>%
#   group_by(gene) %>%
#   summarise(N=n()) %>%
#   arrange(desc(N))
# 
# top_10pair_prism %>% 
#   filter(drug %in% prism268_non_oncology_druglist) %>% 
#   filter(impdef== "toppos gene") %>% 
#   ungroup() %>%
#   group_by(gene) %>%
#   summarise(N=n()) %>%
#   arrange(desc(N))

# top_10pair_prism %>% 
#   filter(drug %in% prism268_non_oncology_druglist_poorlypredicted) %>% 
#   ungroup() %>%
#   group_by(gene) %>%
#   summarise(N=n()) %>%
#   arrange(desc(N))
# 
# 
# pred1 <- top_10pair_prism %>% 
#   filter(drug %in% prism268_non_oncology_druglist_poorlypredicted) %>% 
#   select(-dataset, -imptype, -imp,-impdef, -anno_type1) %>% 
#   left_join(prism_sc_drug, by= c("drug" = "broad_id")) %>% 
#   # group_by(drug) %>%
#   # arrange(desc(imp), .by_group = TRUE) %>% 
#   mutate(DTC_panel=gene %in% targetpanel_dtc) %>% 
#   left_join(targetpanel_drh_genelevel %>% rename(prism_targeted_drug= drug), by= c("gene"= "target")) %>%
#   rename(top_pos_gene= gene, nominal_target =target ) %>% 
#   left_join(prism_data %>% select(BROAD_ID, sensitivity), by= c("drug" = "BROAD_ID"))  %>% 
#   # mutate(top_sen_cell= map(sensitivity,function(x){x %>%filter(auc < 0.7) %>%  pull(depmap_id)})) %>% 
#   # select(-sensitivity) %>%
#   filter(DTC_panel) %>%
#   left_join(prism_data %>% select(BROAD_ID, name),by=c("drug"= "BROAD_ID")) %>% 
#   select(drug, name, nominal_target, moa, top_pos_gene, rank,DTC_panel, prism_targeted_drug,sensitivity ) %>% filter(drug!="BRD-K93779381")
#   
# 
# 
# # add cell line info..   
# pred1_celllevel <- pred1 %>% 
#   select(drug) %>% 
#   distinct() %>% 
#   left_join(prism_data %>% select(BROAD_ID, sensitivity), by= c("drug" = "BROAD_ID"))  %>% 
#   # mutate(sensitivity= map( sensitivity, function(df){df %>% filter(auc < 0.7) })) %>% 
#   mutate(top_sen_cell= map(sensitivity,function(x){x %>%filter(auc < 0.8) %>%  pull(depmap_id)})) %>% 
#   select(-sensitivity) %>% 
#   unnest()  %>% 
#   inner_join(cell_line_info, by= c("top_sen_cell"= "DepMap_ID"))
# 
# # sum(tmp$gene %in% targetpanel)
# setwd("~/cluster_wrk/drug_moa/predicting_prism")
# pred1  %>% select(-sensitivity) %>% write_csv("incorrectdrug_druglevel.csv" )
# # write_csv(pred1_celllevel, "incorrectdrug_celllevel.csv" )
```

get the top 10 target for supervised prediction
```{r}
# source('~/cluster_wrk/drug_moa/supervised_target_pred/no_tunning_weighted_averaging.R')
# 
# predictors_mat <- feature_imp_ridge_prism_comb1 %>% 
#   filter(drug %in% prism_good_fitted_drugs_annotated) %>% 
#   arrange(drug) %>% 
#   select(-drug) %>% 
#   mutate_all(.funs = scale)
# test_idx <- which(prism_good_fitted_drugs_annotated %in%  unique(tmp1$drug) )
# cor_mat = cor(t(predictors_mat),method = "spearman") %>% replace(is.na(.), 0)
# cor_mat[cor_mat< 0 ] <- 0 
# 
# target_mat <- get_target_mat(target_tibble = 
#                                prism_target_binary %>% 
#                                filter(drug %in% prism_good_fitted_drugs_annotated) %>% 
#                                filter(!(drug %in% unique(tmp1$drug))) %>% 
#                                arrange(drug))
# 
#   
# tmp2 <-   no_tunning_weighted_averaging(
#   
#   target_mat = target_mat,
#   cor_mat = cor_mat,
#   test_idx = test_idx,
#   pred_new=T
#   )
# 
# # row.names(tmp2) <- prism_good_fitted_drugs_annotated[test_idx]
# tmp3 <- bind_cols(drug=prism_good_fitted_drugs_annotated[test_idx],  as_tibble(tmp2)) %>% 
#   pivot_longer(cols = -drug, names_to= "gene",values_to= "pred") %>% 
#   group_by(drug) %>% 
#   slice_max(order_by = pred, n=5) %>% 
#   arrange(desc(pred), .by_group = TRUE)
# 
# 
# # join supervised and unsupervised prediction result
# 
# tmp4 <- inner_join(top_pair_prism, tmp3, by= c("drug","gene"))
# 
# # no good overlapping result!
```



also get the proved, non-oncology drugs that no nominal target info is available
```{r}
# prism_good_fitted_nononcologydrugs_notannotated <- prism_sc_drug %>% 
#   filter(broad_id %in% setdiff(prism_good_fitted_drugs, prism_good_fitted_drugs_annotated)) %>% 
#   filter(phase=="Launched") %>% 
#   filter(drug_category== "noncancer")
# 
# pred2 <- feature_imp_ridge_prism_comb1 %>% 
#   filter(drug %in% prism_good_fitted_nononcologydrugs_notannotated$broad_id) %>% 
#   pivot_longer(cols= - drug, names_to= "gene", values_to = "imp") %>% 
#   group_by(drug) %>% 
#   slice_max(order_by = imp,n=10) %>% 
#   group_by(drug) %>% 
#   mutate(rank= rank(-imp)) %>% 
#   ungroup() %>% 
#   inner_join(prism_good_fitted_nononcologydrugs_notannotated, by= c("drug" = "broad_id")) %>%
#   inner_join(prism_data %>% select(-target, - sensitivity, -moa, -drug_category), by=c("drug"= "BROAD_ID") )%>% 
#   mutate(DTC_panel=gene %in% targetpanel_dtc) %>% 
#   left_join(targetpanel_drh_genelevel %>% rename(prism_targeted_drug= drug), by= c("gene"= "target")) %>%
#   rename(top_pos_gene= gene, nominal_target =target ) %>% 
#   left_join(prism_data %>% select(BROAD_ID, sensitivity), by= c("drug" = "BROAD_ID"))  %>% 
#   # mutate(top_sen_cell= map(sensitivity,function(x){x %>%filter(auc < 0.7) %>%  pull(depmap_id)})) %>% 
#   filter(DTC_panel ) %>% 
#   select(drug, name, moa, top_pos_gene, rank,DTC_panel, prism_targeted_drug,sensitivity ) 
#   
# pred2_celllevel <- pred2 %>%
#   select(drug) %>% 
#   distinct() %>% 
#   left_join(prism_data %>% select(BROAD_ID, sensitivity), by= c("drug" = "BROAD_ID"))  %>% 
#   # mutate(sensitivity= map( sensitivity, function(df){df %>% filter(auc < 0.7) })) %>% 
#   mutate(top_sen_cell= map(sensitivity,function(x){x %>%filter(auc < 0.7) %>%  pull(depmap_id)})) %>% 
#   select(-sensitivity) %>% 
#   unnest()  %>% 
#   inner_join(cell_line_info, by= c("top_sen_cell"= "DepMap_ID"))
# 
# pred2 %>%  select(-sensitivity) %>% write_csv("notargetdrug_druglevel.csv")
# 
# cell_level <- bind_rows(pred1_celllevel, pred2_celllevel)%>% 
#   distinct()
#   # add_count(top_sen_cell) %>%select(-drug)%>%
#   # arrange(desc(n))
#   
#   
# # write_csv(cell_level, "cell_level.csv")
# 
# # sum(tmp$gene %in% targetpanel)
# # sum(top_10pair_prism$gene %in% targetpanel)
```


```{r}
# tmp <- feature_imp_ridge_prism_comb1 %>% 
#   filter(drug %in% c("BRD-K75958547", "BRD-K66296774", "BRD-K69726342")) %>% 
#   pivot_longer(cols= -drug,names_to = "gene",values_to = "value") %>% 
#   pivot_wider(id_cols = gene, names_from= drug, values_from= value)
# 
# tmp %>% select(-gene) %>% cor(method = "spearman")
# 
# tmp1= feature_imp_ridge_prism_comb1 %>% 
#   filter(drug %in% prism_good_fitted_drugs_annotated) %>% 
#   pivot_longer(cols= -drug,names_to = "gene",values_to = "value") %>% 
#   pivot_wider(id_cols = gene, names_from= drug, values_from= value)
# tmp2 = cor(tmp$`BRD-K66296774`, tmp1 %>% select(-gene),method = "spearman" )
# hist(tmp2)
```

