---
title: "Noncancer drug target validation"
author: "Wenyu"
date: "5/11/2023"
output: html_document
---

This notebook is used to evaluate whether PISA drug target experiment replicates the predicted target for noncancer drugs. Knitting takes around 174 seconds

```{r }
library(furrr)
library(tidyverse)
library(ggsci)
```


```{r,include=FALSE,echo=FALSE,eval=FALSE}
load("~/cluster_scratch/forward_modelling/targetpred_output_simplefiltering.RData")
rm(get_target_mat)
rm(no_tunning_weighted_averaging)
rm(get_target_pred_accuracy_batch)
rm(return_acc_estimate_cv)
# note the unsupervised auc is precalculated in get_unsupervised_target_prediction_auc.R code

load("~/cluster_scratch/unsupervised_target_pred/unsupervised_target_pred_ConSenSig.RData")

cell_line_info <- data.table::fread("~/cluster_scratch/depmap_21q1/sampleinfo")
# targetpanel_dtc <- data.table::fread("~/cluster_scratch/prior/DTC_data_all.csv",
#                                  select = c("gene_names")) %>% distinct() %>% pull(gene_names)

cell_line_info <- data.table::fread("~/cluster_scratch/depmap_21q1/sampleinfo")

cellline_hgsoc <- cell_line_info %>% 
  filter(primary_disease== "Ovarian Cancer") %>% 
  filter(Subtype== "Adenocarcinoma, high grade serous")

res_prism2_long <- res_prism2
res_prism2 <- res_prism2_long %>%
  select(-variance) %>% 
  filter(.metric== "spearman coef") %>%
  pivot_wider(names_from = input, values_from= estimate) %>%
  mutate(acc_sen= (ceres+ces+demeter2)/3) %>%
  distinct() 
prism_good_fitted_drugs <- res_prism2 %>%
  filter(sample_size>100) %>%
  filter(acc_sen>0.2) %>%
  arrange(BROAD_ID)
# n=312, 199 targeted cancer drugs, 50 chemo drugs and 63 noncancer drugs.

# how many non-oncology drugs? N= 63
prism_good_fitted_nononcologydrugs <-  prism_good_fitted_drugs %>% 
  filter(drug_category== "noncancer") %>% 
  arrange(BROAD_ID ) %>% 
  pull(BROAD_ID) %>% 
  unique()


# drh annotation include both MOA and target info N=268, this will be my train set
prism_good_fitted_drugs_drhannotated <- prism_good_fitted_drugs %>% 
  select(BROAD_ID, moa) %>% 
  drop_na() %>% 
  filter(BROAD_ID %in% prism_target_binary$drug) %>% 
  pull(BROAD_ID)
  
# DTC only care about target gene but not moa annotation: N= 52
prism_good_fitted_drugs_dtcannotated <- prism_good_fitted_drugs %>% 
  filter(BROAD_ID %in% prism_target_dtc$drug) %>% 
  pull(BROAD_ID)

# 46 = 58-13 +1 1 drug no moa but have target.
# prism_good_fitted_nononcologydrugs_drhannotated <- intersect(prism_good_fitted_drugs_drhannotated, prism_good_fitted_nononcologydrugs)
# 
# prism_good_fitted_nononcologydrugs_drhnotannotated <- setdiff(prism_good_fitted_drugs_drhannotated, prism_good_fitted_nononcologydrugs)

# prism_good_fitted_nononcologydrugs <-  prism_good_fitted_drugs %>% 
#   filter(drug_category== "noncancer") %>% 
#   arrange(BROAD_ID ) %>% 
#   filter(is.na(moa))

# save(list = c("prism_data", "prism_target_binary", "prism_target_dtc"), file= "./fig_res/putative_targetinfo.RData")


# get hgsoc sensitivity for all 63 noncancer drugs
# prism_63_sen <- prism_data %>% 
#   filter(BROAD_ID %in%  prism_good_fitted_nononcologydrugs) %>% 
#   select(BROAD_ID ,sensitivity) %>% 
#   unnest(cols=sensitivity) %>% 
#   drop_na()
# 
# 
# # list auc of HGSOC, and the number of sen HGSOC cells for that drugs
# prism_63_sen_hgsoc <- full_join(
#     x= prism_63_sen %>% filter(depmap_id %in% cellline_hgsoc$DepMap_ID),
#     y= cellline_hgsoc %>% select(DepMap_ID, cell_line_name), 
#     by=c("depmap_id"= "DepMap_ID")
#   ) %>% 
#   select(-ec50) %>% 
#   # filter(auc< 0.8) %>%
#   group_by(BROAD_ID) %>% 
#   summarise(n_total= n(),n_0.8= sum(auc<0.8)  ) %>% 
#   drop_na() %>% 
#   ungroup() %>% 
#   full_join(
#   y = prism_63_sen %>% filter(depmap_id == "ACH-000524")
    )
# write_csv(prism_63_sen_hgsoc, path = "~/cluster_wrk/drug_moa/predicting_prism/prism_63_sen_hgsoc.csv")

# tmp <- prism_data %>% filter(BROAD_ID %in% prism_good_fitted_nononcologydrugs) %>% 
#   filter(!(BROAD_ID  %in% prism_good_fitted_drugs_drhannotated )) %>%  select(BROAD_ID, moa)

# Now use the 268 drugs as the training set to predict the targets for the drugs of interest

# source("~/cluster_wrk/drug_moa/supervised_target_pred/function/get_target_pred_supervised.R")
# source('~/cluster_wrk/drug_moa/supervised_target_pred/function/return_acc_estimate_loocv.R')
# prism_drh_predictions <- get_predictions(
#   sig_data=feature_imp_ridge_prism_comb1,
#   train_drugs=prism_good_fitted_drugs_drhannotated,
#   pred_drugs=prism_good_fitted_drugs$BROAD_ID,
#   train_label= prism_target_binary) %>%
#   as_tibble(rownames= "target")
# 
# prism_unsupervised <- feature_imp_ridge_prism_comb1 %>%
#   filter(drug %in% prism_good_fitted_drugs$BROAD_ID) %>%
#   pivot_longer(-drug, names_to= "target", values_to= "pred") %>%
#   pivot_wider(id_cols = target, names_from= drug, values_from= pred)
# 
# setwd("~/cluster_wrk/drug_moa/predicting_prism")
# write_csv(prism_drh_predictions, "./fig_res/prism312_drh_predictions.csv")
# write_csv(prism_unsupervised,path = "./fig_res/prism312_unsupervised.csv")
```

```{r}
rm(list= ls())
load("./fig_res/putative_targetinfo.RData")
prism_drh_predictions <- read_csv("../predicting_prism/fig_res/prism312_drh_predictions.csv")
prism_unsupervised <- read_csv("../predicting_prism/fig_res/prism312_unsupervised.csv")

senvalid_20drugs <- read_csv("../predicting_prism/fig_res/res_final.csv")
PISA_summary <- read_csv( "~/cluster_wrk/sen_tar_validation/data/inputdata/pisa_summary.csv")

# intersect(senvalid_20drugs$Drug_name, unique(PISA_summary$drug_name) )
# setdiff(senvalid_20drugs$Drug_name, unique(PISA_summary$drug_name))
# setdiff(unique(PISA_summary$drug_name),senvalid_20drugs$Drug_name)

# Note for drug gene binding with more than one value, the one with lowest p-value is selected.
PISA_summary <- PISA_summary %>% 
  janitor::clean_names() %>% 
  select(-one_of(c("biological_process", "cellular_component", "molecular_function"))) %>% 
  filter(!is.na(gene_symbol))%>%  
  inner_join(senvalid_20drugs %>% select(Drug_name, drugid),  by=c("drug_name"="Drug_name")) %>% 
  group_by(drugid, drug_name, gene_symbol) %>%
  slice_min(p_value) %>%
  ungroup() %>% 
  mutate(p_adj=p.adjust(p_value, method = "fdr")) %>% 
  mutate(log10_padj= -log10(p_adj))

prism_drh_pred20 <- prism_drh_predictions %>% 
  select(one_of(c("BROAD_ID", senvalid_20drugs$drugid))) %>% 
  pivot_longer(cols= 2:21,names_to="drug_id", values_to="sup_pred_score") %>% 
  rename(target=BROAD_ID)

prism_unsupervised_pred20 <- prism_unsupervised %>% 
  select(one_of(c("target", senvalid_20drugs$drugid))) %>% 
  pivot_longer(cols= 2:21,names_to="drug_id", values_to="unsup_pred_score")
# write_csv(PISA_summary, "./fig_res/PISA_summary.csv")
```


```{r}
# get gene expression for kuramochi cell line
# log2(TPM+1) psedo count
exp_seq_kuramochi <- read_csv("~/cluster_scratch/ces_21q1_io/exp_seq_tidy.csv") %>% 
  filter(DepMap_ID== 'ACH-000524') %>% 
  pivot_longer(cols = - DepMap_ID, names_to= "gene", values_to="exp_tpm_rsem") 

exp_gene_c2 <- exp_seq_kuramochi%>% 
  filter(exp_tpm_rsem>2) %>% 
  pull(gene)
```


```{r,include=FALSE,eval=FALSE,echo=FALSE}
# Check PISA result with expression
# # filter out the non expressing genes from PISA as they are false positive result.
# # use threshold 2 for log2(TPM+1) play with this threshold to get better results.
# 
# # in general pisa result is not correlated with gene expression
# inner_join(exp_seq_kuramochi, PISA_summary, by=c("gene"= "gene_symbol")) %>% 
#   nest_by(drug_name, drugid) %>% 
#   ungroup() %>% 
#   mutate(cor= map_dbl(.x = data, 
#                       .f = function(df){cor(df$exp_tpm_rsem, df$score, use = "complete.obs")})) %>% 
#   select(-data) %>%
#   mutate(cor= round(cor,2)) %>% 
#   arrange(desc(cor)) %>% 
#   View()
# 
# #however there is still false positive result which should be removed.
# 
# inner_join(exp_seq_kuramochi,  <- , by=c("gene"= "gene_symbol")) %>% 
#   mutate(exp_status= (exp_tpm_rsem>2)) %>% 
#   ggplot(aes(exp_status, log10(score)))+
#   geom_violin()+
#   ggpubr::stat_compare_means(method = "t.test")
```



```{r,include=FALSE,eval=FALSE,echo=FALSE}
# check whether PISA result recapulate putative targets
# pisa_drh <- prism_target_binary %>% 
#   filter(drug %in% prism_drh_pred20$drug_id) %>% 
#   left_join(PISA_summary, by= c("drug"="drugid", "target"= "gene_symbol"))
# 
# t.test(pisa_drh$score, PISA_summary$score)
# 
# prism_target_binary %>% 
#   mutate(binding_score=1) %>% 
#   filter(drug %in% prism_drh_pred20$drug_id) %>% 
#   right_join(PISA_summary, by= c("drug"="drugid", "target"= "gene_symbol")) %>% 
#   mutate(putative= !(is.na(binding_score))) %>% 
#   ggplot(aes(putative, log10(score)))+
#   geom_boxplot()+
#   ggpubr::stat_compare_means(method = "t.test")
#  
# pisa_dtc <- prism_target_dtc %>% 
#   filter(drug %in% prism_drh_pred20$drug_id) %>% 
#   left_join(PISA_summary, by= c("drug"="drugid", "target"= "gene_symbol"))
# 
# cor.test(pisa_dtc$score, pisa_dtc$binding_score, use="complete.obs", method = "pearson")
# 
# pisa_dtc %>% 
#   drop_na() %>% 
#   ggplot(aes(score, binding_score))+
#   geom_point()+
#   ylab("dtc_score")+
#   xlab("pisa_score")
# 
# # only one drug are widely avaliable BMS-387032
# 
# prism_target_dtc %>% 
#   filter(drug == "BRD-K43389698") %>%
#   # filter(drug %in% pisa_dtc$drug) %>%  
#   right_join(PISA_summary, by= c("drug"="drugid", "target"= "gene_symbol")) %>% 
#   mutate(putative= case_when(binding_score>0.4~ "yes",
#                              (binding_score <= 0.4)|(is.na(binding_score))~ "no")) %>% 
#   ggplot(aes(putative, log10(score)))+
#   geom_boxplot()+
#   ggpubr::stat_compare_means(method = "t.test")
# 
# cor.test(pisa_dtc$score, pisa_dtc$binding_score, use="complete.obs", method = "pearson")
# 
# cor.test(pisa_dtc$score, pisa_dtc$binding_score, use="complete.obs", method = "kendall")
# 
# # whether the primary targets are  prioritized in PISA result
# # cannot do enrichment analysis since there are too little
```

Join PISA result with prediction result
```{r}
PISA_summary_augmented= PISA_summary %>%
  mutate(exp_status= gene_symbol %in% exp_gene_c2) %>%
  mutate(score1= log10_p*abs(log2_fc)) %>% 
  mutate(score2= log10_p) %>%
  mutate(score3= abs(log2_fc)) %>% 
  select(exp_id:gene_symbol,drugid,p_value,p_adj, exp_status,score1:score3) %>% 
  full_join(prism_drh_pred20, by=c("drugid"="drug_id", "gene_symbol"="target")) %>%
  full_join(prism_unsupervised_pred20, by=c("drugid"="drug_id", "gene_symbol"="target")) %>% 
  filter(!is.na(exp_id))

PISA_summary_augmented_drug_level <- PISA_summary_augmented %>%
  nest_by(drug_id,drug_name,drugid, exp_id) %>%
  ungroup()
```

score rank based filtering

supervised prediction
```{r}
cor_res_sup <- tibble(score_type=1:3) %>% 
  mutate(res= map(
  .x=1:3, 
  .f= function(x){
    df= PISA_summary_augmented %>% 
      select(exp_id, drug_name, drug_id, gene_symbol,exp_status,p_value,one_of(paste0("score", x)),"sup_pred_score")
    colnames(df)[which(colnames(df)==(paste0("score", x)))] <- "score"
  
    df1 <- df %>% 
      nest_by(exp_id,drug_id, drug_name) %>%
      ungroup() %>%
      mutate(data= map(
        .x= data,
        .f = function(df2){
          df_row <- nrow(df2) 
          df2 %>%
            arrange(desc(score)) %>%
            mutate(score_0.05= score>nth(score,n = df_row*(0.05))) %>%
            mutate(score_0.1= score>nth(score,n = df_row*(0.1))) %>%
            mutate(score_0.15= score>nth(score,n = df_row*(0.15))) %>%
            mutate(score_0.2= score>nth(score,n = df_row*(0.2))) %>%
            mutate(score_0.25= score>nth(score,n = df_row*(0.25))) %>%
            mutate(score_0.3= score>nth(score,n = df_row*(0.3))) %>%
            mutate(score_0.35= score>nth(score,n = df_row*(0.35))) %>%
            mutate(score_0.4= score>nth(score,n = df_row*(0.4))) %>%
            mutate(score_0.45= score>nth(score,n = df_row*(0.45))) %>%
            mutate(score_0.50= score>nth(score,n = df_row*(0.5))) %>%
            mutate(score_1= T) %>% 
            pivot_longer(cols= score_0.05:score_1, names_to="threshold_type", values_to= "binaryvalue") %>%
            nest_by(threshold_type) %>% 
            ungroup() %>%
            mutate(res= map(data, .f=function(df){
              df1= df %>%
                filter(binaryvalue) 

              cor_sup=  tryCatch(
                  expr = cor(df1$sup_pred_score, df1$score, use = "complete.obs", method= "pearson"),
                  error= function(err) NA)
              res= tibble(cor_type= c("cor_sup"), corvalue=c(cor_sup))
              return(res)
            })) %>%
            select(-data) %>%
            unnest(res)
        })) %>% 
      unnest(data)
    }
  )) %>% unnest(res) %>% 
  mutate(threshold_prop= as.numeric(str_split(threshold_type,"_",n = 2,simplify = T)[,2]))

  
# cor_res1_sup <- cor_res_sup %>% 
#   mutate(across(c(threshold_type),as.factor)) 
# rm(cor_res_sup)
# levels(cor_res1_sup$threshold_type) <- c(1,0.05*1:10)
# cor_res1_sup$threshold_type <- fct_relevel(cor_res1_sup$threshold_type, "1", after = Inf)
# cor_res1_sup <- cor_res1_sup %>% 
#   mutate(threshold_prop= as.numeric(levels(threshold_type))[as.numeric(threshold_type)]) 

# cor_res1_sup %>%
#   # group_by(threshold_type,score_type,exp_id) %>%
#   # summarise(median_corvalue=median(corvalue, na.rm = T)) %>%
#   # ungroup() %>%
#   ggplot(aes(x= threshold_type,y= corvalue))+
#   geom_boxplot()+
#   geom_hline(yintercept=0)+
#   facet_grid(cols = vars(score_type),scale= "free_y")
cor_res_sup_gridlevel <- cor_res_sup %>%
  select( -threshold_type,-cor_type) %>%
  nest_by(score_type, threshold_prop) %>%
  ungroup() %>% 
  mutate(mean_corvalue=map_dbl(data, .f=function(x){round(mean(x$corvalue,na.rm=T),4)})) %>%
  arrange(desc(mean_corvalue))
```


generate random prediction based on permutation
```{r,eval=FALSE,include=FALSE, echo=FALSE}
# set.seed(1234)
# uniform distribtion
# prism_drh_pred20_rdm_uni <- tibble(sample_id=1:1000) %>%
# mutate(sample_df= map(
# .x= 1:1000,
# .f= function(x){
# set.seed(x)
# idx <- runif(6020, min = 0,max = 1)
# prism_drh_pred20_rdm <- prism_drh_pred20 %>%
# mutate(sup_pred_score= idx)}
# ))
# normal distribution
# prism_drh_pred20_rdm_norm <- tibble(sample_id=1:10000) %>%
# mutate(sample_df= map(
# .x= 1:10000,
# .f= function(x){
# set.seed(x)
# idx <- rnorm(6020, mean = 0,sd = 1)
# prism_drh_pred20_rdm <- prism_drh_pred20 %>%
# mutate(sup_pred_score= idx)}
# ))
# permutation
# prism_drh_pred20_rdm_idx <- map(
# .x= 1:1000,
# .f= function(x){
# seed=x
# ridx=sample(1:6020)
# }
# )
# prism_drh_pred20_rdm_perm <- tibble(sample_id=1:1000) %>%
# mutate(sample_df= map(
# .x= 1:1000,
# .f= function(x){
# idx <- prism_drh_pred20_rdm_idx[[x]]
# prism_drh_pred20_rdm <- prism_drh_pred20 %>%
# mutate(sup_pred_score= prism_drh_pred20$sup_pred_score[idx])}
# ))
# rm(prism_drh_pred20_rdm_idx)

```


```{r,eval=FALSE,include=FALSE, echo=FALSE}
# get_cor_res_rdm <- function(perm_num, score_type, threshold_prop,cor_type= "cor_sup",rdm_pred){
#   
#   tibble(sample_df_idx=1:perm_num) %>%
#   mutate(res= map(
#   .x=sample_df_idx,
#   .f= function(x){
#     PISA_summary_augmented_rdm <-  PISA_summary %>%
#       mutate(score_new= case_when(
#         score_type==1~ log10_p*abs(log2_fc),
#         score_type==2~ log10_p,
#         score_type==3~ abs(log2_fc)
#         )) %>%
#       full_join(rdm_pred$sample_df[[x]],
#                 by=c("drugid"="drug_id", "gene_symbol"="target")) %>%
#       filter(!is.na(exp_id)) %>%
#       select(exp_id:gene_symbol,drugid,p_value,score_new,sup_pred_score)
# 
#     df= PISA_summary_augmented_rdm %>%
#       nest_by(exp_id,drug_id, drug_name) %>%
#       ungroup()
# 
#     df1 <- df %>%
#       mutate(data= map(
#         .x= data,
#         .f = function(df2){
#           df_row <- nrow(df2)
#           score_threshold= nth(x = sort(df2$score_new,decreasing = T),
#                                n = df_row*(threshold_prop))
#           scoreb1= df2$score_new > score_threshold
# 
#           df2 <- filter(df2, scoreb1)
# 
#           if(cor_type== "cor_sup"){
#             cor_value=  tryCatch(
#               expr = cor(df2$sup_pred_score, df2$score_new,
#                          use = "complete.obs", method= "pearson"),
#               error= function(err) NA)}
# 
#           res= tibble(cor_type= cor_type, corvalue=cor_value )
#           return(res)
#             })) %>%
#       unnest(data)
#     }
#   )) %>%
#   mutate(mean_cor=map_dbl(res, .f= function(df){mean(df$corvalue, na.rm = T)})) %>%
#   mutate(median_cor=map_dbl(res, .f= function(df){median(df$corvalue, na.rm = T)}))
# }
# 
# get_cor_res_rdm_perm <-function(perm_num, score_type, threshold_prop,cor_type= "cor_sup"){get_cor_res_rdm(perm_num, score_type, threshold_prop,cor_type,rdm_pred = prism_drh_pred20_rdm_perm)}
# 
# get_cor_res_rdm_uni <-function(perm_num, score_type, threshold_prop,cor_type= "cor_sup"){get_cor_res_rdm(perm_num, score_type, threshold_prop,cor_type,rdm_pred= prism_drh_pred20_rdm_uni)}
# 
# get_cor_res_rdm_norm <-function(perm_num, score_type, threshold_prop,cor_type= "cor_sup"){get_cor_res_rdm(perm_num, score_type, threshold_prop,cor_type,rdm_pred= prism_drh_pred20_rdm_norm)}
# 
# 
# tictoc::tic()
# plan(multisession,workers=6)
# par_grid_perm <- expand_grid(
#   perm_num=1000,
#   score_type=c(1,2,3),
#   threshold_prop=c(0.05*1:10, 1)) %>%
#   # slice(1:6) %>%
#   mutate(res= future_pmap(
#     .l = list(perm_num, score_type, threshold_prop),
#     .f = get_cor_res_rdm_perm,
#     .options = furrr_options(seed=0000)
#           ))
# plan(sequential)
# # save(list = c("par_grid_perm"), file = "~/cluster_scratch/forward_modelling/noncancer_drugtarget_validation/null_dist_all.RData")
# tictoc::toc()
# 
# # perm 457s 6 cores 6 grids
# # norm 468 6 cores 6 grids
# 
# # 2200 sec 
# tictoc::tic()
# plan(multisession,workers=6)
# par_grid_uni <- expand_grid(
#   perm_num=1000,
#   score_type=c(1,2,3),
#   threshold_prop=c(0.05*1:10, 1)) %>%
#   # slice(1:6) %>%
#   mutate(res= future_pmap(
#     .l = list(perm_num, score_type, threshold_prop),
#     .f = get_cor_res_rdm_uni,
#     .options = furrr_options(seed=0000)
#           ))
# # save(list = c("par_grid_perm", "par_grid_uni"), file = "~/cluster_scratch/forward_modelling/noncancer_drugtarget_validation/null_dist_all.RData")
# tictoc::toc()
# 
# tictoc::tic()
# plan(multisession,workers=6)
# par_grid_norm <- expand_grid(
#   perm_num=10000,
#   score_type=c(1,2,3),
#   threshold_prop=c(0.05*1:10, 1)) %>%
#   # slice(1:6) %>%
#   mutate(res= future_pmap(
#     .l = list(perm_num, score_type, threshold_prop),
#     .f = get_cor_res_rdm_norm,
#     .options = furrr_options(seed=0000)
#           ))
# 
# plan(sequential)
# tictoc::toc()
# # save(list = c("par_grid_perm", "par_grid_uni","par_grid_norm"), file = "~/cluster_scratch/forward_modelling/noncancer_drugtarget_validation/null_dist_all_1000.RData")
# 
# # 20544 sec
# tictoc::tic()
# plan(multisession,workers=6)
# par_grid_norm1 <- expand_grid(
#   perm_num=10000,
#   score_type=c(1,2,3),
#   threshold_prop=c(0.05*1:10, 1)) %>%
#   # slice(1:6) %>%
#   mutate(res= future_pmap(
#     .l = list(perm_num, score_type, threshold_prop),
#     .f = get_cor_res_rdm_norm,
#     .options = furrr_options(seed=0000)
#           ))
# 
# plan(sequential)
# tictoc::toc()
# save("par_grid_norm1", file = "~/cluster_scratch/forward_modelling/noncancer_drugtarget_validation/null_dist_norm_10000.RData")
```


calculate overall p-value and drug specific p-values
```{r}
# load("~/cluster_scratch/forward_modelling/noncancer_drugtarget_validation/null_dist_all_1000.RData")
load("~/cluster_scratch/forward_modelling/noncancer_drugtarget_validation/null_dist_norm_10000.RData")
# floating point issue.
# par_grid_perm$threshold_prop <- round(par_grid_perm$threshold_prop,2)
# par_grid_uni$threshold_prop <- round(par_grid_uni$threshold_prop,2)
# par_grid_norm$threshold_prop <- round(par_grid_norm$threshold_prop,2)
par_grid_norm1$threshold_prop <- round(par_grid_norm1$threshold_prop,2)

get_p_twoside <- function(x,y,z=1000){sum( abs(y)>=abs(x), na.rm = T )/z}
get_p_twoside1 <- function(x,y,z=10000){sum( abs(y)>=abs(x), na.rm = T )/z}

overall_sup <- cor_res_sup_gridlevel %>%
  arrange(score_type,threshold_prop) %>% 
  # inner_join(
  #   par_grid_perm %>% mutate(score_type=as.numeric(score_type)) %>% select(-perm_num), 
  #   by=c("threshold_prop", "score_type")) %>% 
  # rename(data_perm=res) %>% 
  # inner_join(
  #   par_grid_uni %>% mutate(score_type=as.numeric(score_type))%>% select(-perm_num), 
  #   by=c("threshold_prop", "score_type")) %>%   
  # rename(data_uni=res) %>% 
  # inner_join(
  #   par_grid_norm %>% mutate(score_type=as.numeric(score_type))%>% select(-perm_num), 
  #   by=c("threshold_prop", "score_type")) %>%   
  # rename(data_norm=res) %>%
  inner_join(
    par_grid_norm1 %>% mutate(score_type=as.numeric(score_type))%>% select(-perm_num), 
    by=c("threshold_prop", "score_type")) %>%   
  rename(data_norm1=res) %>% 
  mutate(mean_real= map_dbl(data, .f= function(x){mean(x$corvalue,na.rm = T)})) %>%
  # mutate(mean_perm_vector=map(data_perm, .f= function(x){x %>% pull(mean_cor)}))  %>%
  # mutate(mean_uni_vector=map(data_uni, .f= function(x){x %>% pull(mean_cor)}))  %>%
  # mutate(mean_norm_vector=map(data_norm, .f= function(x){x %>% pull(mean_cor)}))  %>%
  mutate(mean_norm_vector1=map(data_norm1, .f= function(x){x %>% pull(mean_cor)}))  %>%
  # mutate(perm_num= 1000) %>% 
  # mutate(mean_perm= map_dbl(mean_perm_vector, mean)) %>%
  # mutate(mean_uni= map_dbl(mean_uni_vector, mean)) %>%
  # mutate(mean_norm= map_dbl(mean_norm_vector, mean)) %>%
  mutate(mean_norm1= map_dbl(mean_norm_vector1, mean)) %>%
  # mutate(p_perm=map2_dbl(mean_real, mean_perm_vector,
  #                        .f= get_p_twoside)) %>%
  # mutate(p_uni=map2_dbl(mean_real, mean_uni_vector,
  #                        .f= get_p_twoside)) %>%
  # mutate(p_norm=map2_dbl(mean_real, mean_norm_vector,
  #                      .f= get_p_twoside)) %>% 
  mutate(p_norm1=map2_dbl(mean_real, mean_norm_vector1,
                       .f= get_p_twoside1)) %>% 
  arrange(p_norm1)

tmp <- overall_sup %>% 
  select(!starts_with("data")) %>% 
  select(!contains("vector"))

# write_csv(tmp, "./fig_res/foverall_p_value_supervised_prediction.csv")
```

get drug specific p-value (dist is not preseverd for drug level)
```{r}
get_drugspecific_sig <- function(null_dist,p_fun=get_p_twoside){
  drugspecfic_sup_norm <- inner_join(
  x= cor_res_sup %>%
    select( -threshold_type, -cor_type) 
  ,
  y= null_dist %>%
    unnest(res) %>%
    unnest(res) %>%
    select(drug_id, drug_name,score_type, threshold_prop, corvalue)%>%
    nest_by(drug_id, drug_name,score_type, threshold_prop) %>%
    ungroup() %>%
    mutate(cor_null= map(data, ~.x$corvalue)) %>%
    select(-data),
  by= c("drug_id", "drug_name","score_type", "threshold_prop")
) %>%
  mutate(mean_null= map_dbl(cor_null,~mean(.x,na.rm = T))) %>%
  mutate(p_null= map2_dbl(corvalue, cor_null,
                          .f=p_fun)) %>%
  
  arrange(p_null) %>% 
  select(-cor_null) %>%
  nest_by(score_type, threshold_prop) %>%
  ungroup() %>% 
  mutate(data= map(.x = data, .f= function(x){
                 x$p_adj <- p.adjust(x$p_null,method="fdr")
                 x= as_tibble(x) %>% arrange(p_adj)
                 return(x)}
               ))
}

all_sup <- overall_sup %>% 
  select(!starts_with("data")) %>%
  select(!ends_with("vector")) %>%
  select(!ends_with("vector1")) %>%
  # inner_join(get_drugspecific_sig(null_dist = par_grid_norm) %>% rename(data_norm=data),by=c("score_type", "threshold_prop")) %>%
  inner_join(get_drugspecific_sig(null_dist = par_grid_norm1,p_fun=get_p_twoside1) %>% rename(data_norm1=data),by=c("score_type", "threshold_prop")) 
  # inner_join(get_drugspecific_sig(null_dist = par_grid_uni) %>% rename(data_uni=data),by=c("score_type", "threshold_prop")) %>%
  # inner_join(get_drugspecific_sig(null_dist = par_grid_perm) %>% rename(data_perm=data),by=c("score_type", "threshold_prop")) # %>% 
```



overall comparison
```{r}
# withdraw druglevel dist from the null_dist object
plot_dist_from_all_sup <- function(st, tp, null_type, null_df){
  tmp <- overall_sup %>%
    filter(score_type==st & threshold_prop==tp) %>% 
    select(mean_corvalue, mean_real, ends_with(null_type) )

  dens <- density(tmp %>% unnest(one_of(paste0("data_",null_type)))  %>% pull(mean_cor))
  data <- tibble(x = dens$x, y = dens$y) %>%
      mutate(variable = case_when(
        (x > tmp$mean_real) ~ "On",
        TRUE ~ "off"))
  # 
  overall_plot <- ggplot(data, aes(x, y)) + geom_line() +
    geom_area(data = filter(data, variable == 'On'), fill = 'grey') +
    geom_vline(xintercept = unlist(tmp[1,4]), lty= 2, color= "black")+
    geom_vline(xintercept = unlist(tmp[1,1]), lty= 2, color= "red")+
    theme_classic()+
    xlab("Pearson correlation")+
    ylab("")+
    ggtitle(paste0("Overall, P-value =", unlist(tmp[1,5])))
  
  # showing the same plot with FDR value as heading, highlight how predictions has been improved compraring to random predictions.
  
  tmp1 <- all_sup %>% 
    filter(score_type==st & threshold_prop== tp) %>% 
    select(one_of(paste0("data_", null_type))) %>% 
    unnest(one_of(paste0("data_", null_type))) %>% 
    arrange(p_adj) %>% 
    # inner_join(all_sup1[[3]][[1]] %>% select(drug_id, p_adj)) %>% 
    filter(p_adj<0.25)
  
  null_df1 <- null_df %>% 
    filter(score_type==st & threshold_prop== tp) %>% 
    select(-ends_with("cor")) %>% 
    unnest(res) %>%  unnest(res) %>% 
    select(drug_id,sample_df_idx, corvalue ) %>% 
    filter(drug_id %in% tmp1$drug_id) %>% 
    nest_by(drug_id)
  drug_level_all <- inner_join(tmp1, null_df1)
    
  dist_plot <-  map(1:nrow(drug_level_all), function(i){
    dens <- density(drug_level_all$data[[i]] %>% pull(corvalue))
    data <- tibble(x = dens$x, y = dens$y) %>% 
      mutate(variable = case_when(
        (x > (drug_level_all$corvalue[i]) ) ~ "On",
        TRUE ~ "off"))
    if(round(drug_level_all$p_adj[i],digits = 2)==0){
            title= paste0(tolower(drug_level_all$drug_name[i]),", ","FDR < 0.01")
    } 
    if(round(drug_level_all$p_adj[i],digits = 2)!=0){
        title= paste0(tolower(drug_level_all$drug_name[i])," ","FDR = ",round(drug_level_all$p_adj[i],digits = 2))
    }   
  
    ggplot(data, aes(x, y)) + geom_line() +
      geom_area(data = filter(data, variable == 'On'), fill = 'grey') +
      geom_vline(xintercept = drug_level_all$mean_null[i], lty= 2, color= "black")+
      geom_vline(xintercept = drug_level_all$corvalue[i], lty= 2, color= "red")+
      theme_classic()+
      xlab("Pearson correlation")+
      ylab("")+
      ggtitle(label = title)
    
  })
  
  fig <- ggpubr::ggarrange(
    overall_plot,dist_plot[[1]],dist_plot[[2]],
    dist_plot[[3]],dist_plot[[4]], dist_plot[[5]],
            ncol = 3, nrow=2, common.legend = T)
  return(fig)  
}
```


```{r,fig.height=5.5,fig.width=9}
fig <- plot_dist_from_all_sup(st = 1,tp = 0.25,null_type="norm1", null_df= par_grid_norm1)
fig
# ggsave(dpi = 500,fig,filename = "./fig_res/fig7a.png",units = "in", height = 4,width = 8)
# ggsave(fig,filename = "./fig_res/fig7a.pdf",units = "in", height = 5.5,width = 9)
```

Case study
```{r}
PISA_summary_augmented_drug_level_withsig <- PISA_summary_augmented_drug_level  %>% 
  inner_join(all_sup %>% filter(score_type==1 & threshold_prop==0.25) %>% select(data_norm1) %>% unnest(data_norm1)) %>% 
  arrange(p_adj)
```


report the top hit concordancy
```{r}
tmp2 <- PISA_summary_augmented_drug_level_withsig %>% 
  select(drug_id, drug_name, exp_id,drugid, data,corvalue,p_null, p_adj) %>%
  mutate(data= map(data, 
                   function(df){
                     df %>% 
                       select(gene_symbol, score1, sup_pred_score) %>% 
                       drop_na() %>% 
                       mutate(pisa_score_rank=rank(-score1,ties.method = "random")) %>% 
                       mutate(sup_score_rank=rank(-sup_pred_score,ties.method = "random")) %>% 
                       arrange(desc(sup_pred_score)) %>% 
                       slice(1:10) %>% 
                       filter(pisa_score_rank<21)}) 
           )  %>% 
  mutate(n_hit= map_int(data,nrow)) %>% 
  slice(1:5) %>% select(drug_name, data) %>% unnest(data) %>% 
  select(-score1, -sup_pred_score,-pisa_score_rank) %>% 
  mutate(color="Top Predicted target") %>% 
  arrange(drug_name, sup_score_rank) %>% 
  mutate(text= case_when(
    gene_symbol=="HMGCR" ~ T,
    drug_name=="Podophyllotoxin" ~ T,
    TRUE ~ F
    ))

tmp3 <- anti_join(
  expand_grid(sup_score_rank= 1:10, 
    drug_name= unique(tmp2$drug_name),
    gene_symbol=NA, 
    color="Top PISA target",
    text= F
    ),
  tmp2,
   by=c("drug_name","sup_score_rank")
  ) %>% bind_rows(tmp2) %>% 
  arrange(drug_name, sup_score_rank)%>% 
  mutate(drug_name=tolower(drug_name))
```


```{r,fig.height=2,fig.width=4}
fig <- ggplot(tmp3 , aes(x = sup_score_rank, y= drug_name, fill= color)) + 
  geom_tile(color = "black")+
  # scale_x_discrete()+
  scale_x_continuous(breaks= 1:10)+
  # geom_text(aes(x = sup_score_rank, label= sup_score_rank),y=-1, )+
  geom_text(data = tmp3 %>% filter(text),
            mapping = aes(x = sup_score_rank, y= drug_name, label= gene_symbol),
            size=2)+
  
  theme_classic()+
  scale_fill_manual(values = c("gray","white"),labels= c("Top PISA target", "Top Predicted target"))+
  xlab("Rank of predicted gene")+
  ylab("")+
  guides(fill = guide_legend(nrow = 1,ncol = 2,title = element_blank()))+
  theme(legend.position="top", 
        axis.ticks.x = element_blank(),axis.line.x=element_blank(),
        axis.ticks.y =element_blank() ,axis.line.y=element_blank())

fig
# ggsave(dpi = 500,fig,filename = "./fig_res/fig7b.png",units = "in", height = 2,width = 4)
# ggsave(fig,filename = "./fig_res/fig7a.pdf",units = "in", height = 5.5,width = 9)
```

```{r}
sessionInfo()
```

