---
title: "Drug sensitivity prediction forward modellin"
author: "Wenyu"
date: "1/15/2021"
output: html_document
---

The aim of this notebook is to explore the prediction accuracy
of different type of essentiality scores on drug sensitivity.

```{r, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(furrr)
library(tidyverse)
library(tidymodels)
```

checking whether there are failed jobs
```{r}
# tmp <- list.files("~/cluster_scratch/forward_modelling/prism_modelres/")
# tmp1 <- str_extract(string = tmp, pattern = "\\d{1,4}") 
```

# 1 CTRP


Because rmse or mae are influenced by the value, I standardized the AUC before calculation.
note binarization may lead to only one class (no sensitive cell lines.)
```{r}
load("~/cluster_scratch/forward_modelling/ctrp_input.RData")
ctrp_data <- data
rm(data)

plan(multisession,workers= 6)
res_ctrp <- furrr::future_map_dfr(
  .x = c(1:545), 
  .f = function(x){
    drug <- paste("~/cluster_scratch/forward_modelling/ctrp_modelresnew/drug_", x, ".RData", sep = "")
  load(drug)
  df= (ces1_perf %>% mutate(input= "ces")) %>% 
    bind_rows(ceres_perf %>% mutate(input = "ceres")) %>% 
    bind_rows(demeter2_perf %>% mutate(input = "demeter2")) %>%
    bind_rows(exp_perf %>% mutate(input = "exp")) %>% 
    mutate(drug_id= x)
}    ) %>%   
  rename(eva_data=final_res) %>% 
  mutate(eva_data= furrr::future_map(
    .x = eva_data,
    .f = function(x){
      x %>% 
        mutate(
          truth_auc= label/15,
          truth_auc_binary= as.factor((label/15)> quantile(label/15, 0.1)),
          pred= .pred/15
        )
    })) %>% 
  mutate(res= furrr::future_map(
    .x = eva_data,
    .f = function(x){
      metrics(data = x,truth= truth_auc, pred) %>% 
      bind_rows(
        roc_auc(data= x, 
                truth= truth_auc_binary,
                pred,
                event_level= "second")
      ) %>% 
      bind_rows(
        pr_auc(x, 
               truth= truth_auc_binary, 
               pred,
               event_level= "second")
      ) %>%
      add_row(.metric = "spearman coef",
              .estimator = "standard",
              .estimate = cor(x = x$truth_auc,
                              y = x$pred,
                              use= "complete.obs",
                              method= "spearman") )
        }))  %>%
  select(-eva_data) %>% 
  unnest(res)
plan(sequential)

res_ctrp1 <- res_ctrp %>% 
  select(input, drug_id, .metric, .estimate) %>% 
  group_by(input,drug_id,.metric) %>% 
  summarise(estimate= median(.estimate), variance=var(.estimate) ) %>% 
  ungroup()

res_ctrp2 <- res_ctrp1 %>%
  left_join(
    y = ctrp_data %>% 
      rename(sample_size= n_forward_modelling) %>%
      select(-sensitivity, -target) %>% 
      bind_cols(drug_id= 1:545)
  ) %>% 
  mutate(drug_pair= str_detect(cpd_smiles, "\\."))
```


# 2 GDSC data
```{r}
#load data
load("~/cluster_scratch/forward_modelling/gdsc_input.RData")
gdsc_data <- data
rm(data)

plan(multisession,workers= 6)
res_gdsc <- furrr::future_map_dfr(
  .x = c(1:198), 
  .f = function(x){
    drug <- paste("~/cluster_scratch/forward_modelling/gdsc_modelresnew/drug_", x, ".RData", sep = "")
  load(drug)
  df= (ces1_perf %>% mutate(input= "ces")) %>% 
    bind_rows(ceres_perf %>% mutate(input = "ceres")) %>% 
    bind_rows(demeter2_perf %>% mutate(input = "demeter2")) %>%
    bind_rows(exp_perf %>% mutate(input = "exp")) %>% 
    mutate(drug_id= x)
}    ) %>%   
  rename(eva_data=final_res) %>% 
  mutate(eva_data= furrr::future_map(
    .x = eva_data,
    .f = function(x){
      x %>% 
        mutate(
          truth_auc= label,
          truth_auc_binary= as.factor(label> quantile(label, 0.1)),
          pred= .pred
        )
    })) %>% 
  mutate(res= furrr::future_map(
    .x = eva_data,
    .f = function(x){
      metrics(data = x,truth= truth_auc, pred) %>% 
      bind_rows(
        roc_auc(data= x, 
                truth= truth_auc_binary,
                pred,
                event_level= "second")
      ) %>% 
      bind_rows(
        pr_auc(x, 
               truth= truth_auc_binary, 
               pred,
               event_level= "second")
      ) %>%
      add_row(.metric = "spearman coef",
              .estimator = "standard",
              .estimate = cor(x = x$truth_auc,
                              y = x$pred,
                              use= "complete.obs",
                              method= "spearman") )
        }))  %>%
  select(-eva_data) %>% 
  unnest(res)
plan(sequential)

res_gdsc1 <- res_gdsc %>% 
  select(input, drug_id, .metric, .estimate) %>% 
  group_by(input,drug_id,.metric) %>% 
  summarise(estimate= median(.estimate), variance=var(.estimate) ) %>% 
  ungroup()


res_gdsc2 <- res_gdsc1 %>%
  left_join(
    y = gdsc_data %>% 
      rename(sample_size= n_forward_modelling) %>%
      select(-sensitivity, -target) %>% 
      bind_cols(drug_id= 1:198)
  ) 
res_gdsc2new =res_gdsc2 
res_gdsc2new =res_gdsc2new %>% filter(.metric== "spearman coef")
```

# 3 prism

lets check the accuracy
```{r}
load( file = "~/cluster_scratch/forward_modelling/prism_input.RData")
prism_data <- data
rm(data)

plan(multisession,workers= 6)
res_prism <- furrr::future_map_dfr(
  .x = c(1:1448), 
  .f = function(x){
    drug <- paste("~/cluster_scratch/forward_modelling/prism_modelresnew/drug_", x, ".RData", sep = "")
  load(drug)
  df= (ces1_perf %>% mutate(input= "ces")) %>% 
    bind_rows(ceres_perf %>% mutate(input = "ceres")) %>% 
    bind_rows(demeter2_perf %>% mutate(input = "demeter2")) %>%
    bind_rows(exp_perf %>% mutate(input = "exp")) %>% 
    mutate(drug_id= x)
}    ) %>%   
  rename(eva_data=final_res) %>% 
  mutate(eva_data= furrr::future_map(
    .x = eva_data,
    .f = function(x){
      x %>% 
        mutate(
          truth_auc= label,
          truth_auc_binary= as.factor((label)> quantile(label, 0.1)),
          pred= .pred
        )
    })) %>% 
  mutate(res= furrr::future_map(
    .x = eva_data,
    .f = function(x){
      metrics(data = x,truth= truth_auc, pred) %>% 
      bind_rows(
        roc_auc(data= x, 
                truth= truth_auc_binary,
                pred,
                event_level= "second")
      ) %>% 
      bind_rows(
        pr_auc(x, 
               truth= truth_auc_binary, 
               pred,
               event_level= "second")
      ) %>%
      add_row(.metric = "spearman coef",
              .estimator = "standard",
              .estimate = cor(x = x$truth_auc,
                              y = x$pred,
                              use= "complete.obs",
                              method= "spearman") )
        }))  %>%
  select(-eva_data) %>% 
  unnest(res)
plan(sequential)

res_prism1 <- res_prism %>% 
  select(input, drug_id, .metric, .estimate) %>% 
  group_by(input,drug_id,.metric) %>% 
  summarise(estimate= median(.estimate), variance=var(.estimate) ) %>% 
  ungroup()

res_prism2 <- res_prism1 %>%
  left_join(
    y = prism_data %>% 
      rename(sample_size= n_forward_modelling) %>%
      select(-sensitivity, -target) %>% 
      bind_cols(drug_id= 1:1448)
  ) 
```


check the failed jobs and generate a list to rerun
```{r}
# tmp <- str_subset(string = list.files(path =  "/home/cloud-user/cluster_scratch/forward_modelling/prism_spearman/"),pattern = "drug_" )
# tmp  <- str_split(tmp,pattern = "_",n = 2,simplify = T)
# tmp <-  str_split(tmp[,2],pattern = ".RData",n = 2,simplify = T)
# error_idx <- setdiff(x= 1:1448, y = as.integer(tmp[,1]))
# write(error_idx, file = "~/cluster_wrk/drug_moa/sensitivity_fitting/forward_modelling/test_write.txt")
```


# 4 cross dataset comparison
```{r}
combined_performance <- bind_rows(
  res_ctrp1 %>% 
    select(input, .metric, estimate, variance) %>% 
    mutate(dataset= "CTRP")
  ,
  res_gdsc1 %>% 
    select(input, .metric, estimate, variance) %>% 
    mutate(dataset= "GDSC")
  ,
  res_prism1 %>% 
    select(input, .metric, estimate, variance) %>% 
    mutate(dataset= "PRISM")
  )

# generate a object for testing difference individually for each drug on cluster
combined_performance2 <- bind_rows(
  res_ctrp %>% 
    mutate(dataset= "CTRP")
  ,
  res_gdsc %>% 
    mutate(dataset= "GDSC")
  ,
  res_prism %>% 
    mutate(dataset= "PRISM")
  ) %>% 
  group_by(drug_id, dataset,.metric) %>% 
  nest() %>% 
  ungroup()
# save(combined_performance2,
#      file = "~/cluster_scratch/forward_modelling/performance_testres/input.RData")

# run the test on cluster and return the resulting objects to be used in Figure2C: "performance_difference_test_res1","performance_difference_test_res2"

combined_performance3 <- bind_rows(
  res_ctrp2 %>% 
    mutate(dataset= "CTRP") %>% 
    select( drug_id, broad_cpd_id, cpd_name, input,dataset,sample_size, .metric, estimate, variance) %>% 
    rename(drug_name=cpd_name) %>% 
    rename(ID=broad_cpd_id)
  ,
    res_gdsc2 %>% 
    mutate(dataset= "GDSC") %>% 
    select( drug_id, DRUG_ID, DRUG_NAME, input,dataset, sample_size,.metric, estimate, variance) %>% 
    rename(drug_name= DRUG_NAME) %>% 
    mutate(ID=as.character(DRUG_ID)) 
  ,
  res_prism2 %>% 
    mutate(dataset= "PRISM") %>% 
    select( drug_id, BROAD_ID, name, input,dataset,sample_size, .metric, estimate, variance) %>% 
    rename(drug_name=name) %>% 
    rename(ID=BROAD_ID)
  )
```


```{r}
sig_res <- 
  combined_performance3 %>% 
  nest_by(dataset,.metric) %>% 
  ungroup() %>% 
  mutate(aov_p_value=map_dbl(
    .x = data, 
    .f = function(df){
        res= aov(estimate~input,data = df)
        res= summary(res)[[1]][[5]][[1]] 
        return(res)
    } 
                 )) %>% 
  mutate(tukeyhsd_res=map(
    .x = data, 
    .f = function(df){
        res= aov(estimate~input,data = df)
        res= TukeyHSD(res, which = "input", paired=T) %>% tidy()
        return(res)
    }
                 )) %>% 
  select(-data) %>% 
  unnest(tukeyhsd_res)

```

```{r}
save.image("~/cluster_scratch/forward_modelling/forwardmodelling_all_new.RData")
```


# 5 visualization
```{r}
load("~/cluster_scratch/forward_modelling/forwardmodelling_all_new.RData")
combined_performance3 %>% 
  select(-variance) %>% 
  group_by(.metric, dataset, input) %>% 
  summarize(estimate_median= median(estimate))
```


plot for checking
```{r,fig.width=8,fig.height=12}
combined_performance3 %>%   
  ggplot(mapping = aes(x=input, y= estimate, color=input)) +
  geom_boxplot()+
  facet_grid(rows = vars(.metric),cols=vars(dataset) ,scale="free")
```


manuscript fig2b
```{r,fig.width=4,fig.height=5}
formatter <- function(...){
  function(x) format(x, ..., scientific = F, digit = 2)
}

ddummy = tibble(
  input= NA,
  ymax= c(0.3, 1.2), 
  dataset= c("CTRP", "GDSC"), 
  .metric= factor(
    x = c("rmse", "roc_auc"),
    levels = c("rmse", "roc_auc"), 
    labels = c("RMSE", "ROC-AUC") )
)

fig <- combined_performance3 %>%   
  filter(dataset !="prism") %>%
  mutate(input= toupper(input)) %>%
  mutate(dataset= toupper(dataset)) %>% 
  filter(.metric %in% c("rmse", "roc_auc")) %>% 
  mutate(.metric= factor(.metric,
                         levels = c("rmse", "roc_auc"),
                         labels = c("RMSE", "AUROC"))) %>% 
  ggplot(mapping = aes(x=input, y= estimate, fill=input)) +
  geom_violin()+
  geom_blank(data = ddummy,aes(x= input, y = ymax)) +
  facet_grid(rows = vars(.metric),cols=vars(dataset),
             scale="free", space= "free_x", switch="y")+
  ggpubr::stat_compare_means(method = "anova",
                             paired = T,
                             label.y.npc = 0.95,label.x.npc = 0.05)+
  theme_classic()+
  xlab("")+   ylab("Model fitness")+ 
  theme(legend.position="top", legend.title = element_blank(),
        axis.title.x = element_blank(),axis.text.x = element_blank())+
  guides(fill= guide_legend(nrow = 2,title.position = "top"))+
  scale_y_continuous(labels = formatter(nsmall = 2))+
  ggsci::scale_fill_npg()

fig
ggsave(fig, filename = "~/cluster_wrk/drug_moa/sensitivity_fitting/forward_modelling/fig_res/figure2B.pdf",width = 4,height = 5,bg = "transparent")

ggsave(fig, filename = "~/cluster_wrk/drug_moa/sensitivity_fitting/forward_modelling/fig_res/figure2B.png",width = 4,height = 5,dpi = 500,bg = "transparent")

```

supplementary fig
```{r,fig.width=4,fig.height=8}
ddummy = tibble(
  input= NA,
  ymax= c( 0.29,1.1,0.8,0.9), 
  dataset= c("CTRP", "CTRP", "GDSC", "GDSC"), 
  .metric= factor(
    x = c("mae","pr_auc", "rsq", "spearman coef"),
    levels = c("mae","pr_auc", "rsq", "spearman coef"), 
    labels = c("MAE","PRAUC", "R-square", "Spearman COR") )
)

fig <- combined_performance3 %>%   
  filter(dataset !="prism") %>%
  mutate(input= toupper(input)) %>%
  mutate(dataset= toupper(dataset)) %>% 
  filter(!(.metric %in% c("rmse",  "roc_auc"))) %>% 
  mutate(.metric= factor(.metric,
                         levels = c("mae","pr_auc", "rsq", "spearman coef"),
                         labels = c("MAE","PRAUC", "R-square", "Spearman coef"))) %>%
  ggplot(mapping = aes(x=input, y= estimate, fill=input)) +
  geom_violin()+
  geom_blank(data = ddummy,aes(x= input, y = ymax)) +
  facet_grid(rows = vars(.metric),cols=vars(dataset),
             scale="free", space= "free_x", switch="y")+
  ggpubr::stat_compare_means(method = "anova",
                             paired = T,
                             label.y.npc = 0.95,label.x.npc = 0.05)+
  theme_classic()+
  xlab("")+   ylab("Model fitness")+ 
  theme(legend.position="top", legend.title = element_blank(),
        axis.title.x = element_blank(),axis.text.x = element_blank())+
  guides(fill= guide_legend(nrow = 2,title.position = "top"))+
  scale_y_continuous(labels = formatter(nsmall = 2))+
  ggsci::scale_fill_npg()
fig
ggsave(fig, filename = "~/cluster_wrk/drug_moa/sensitivity_fitting/forward_modelling/fig_res/supplementary figure.pdf",width = 4,height = 8, bg="transparent")

ggsave(fig, filename = "~/cluster_wrk/drug_moa/sensitivity_fitting/forward_modelling/fig_res/supplementary figure.png",width = 4,height = 8,dpi = 500,bg="transparent")
```

figure2d

```{r,fig.height=3,fig.width=6}
plot_df1 <- combined_performance3 %>% 
  filter(.metric=="rmse") %>%
  filter(dataset !="prism") %>%
  # filter(dataset !="GDSC") %>%
  mutate(input= toupper(input)) %>%
  mutate(dataset= toupper(dataset)) %>% 
  mutate(sample_size = cut(sample_size, breaks = seq(0,500,by = 100))) %>%  
  mutate(sample_size = fct_relabel(sample_size, .fun = str_extract, pattern = "(?<=,)\\d{3}")) %>%  ungroup() %>% 
  filter(!((sample_size== "200")&(dataset=="GDSC")))
#too little sample size in this group

sig_res1 <- 
  plot_df1 %>% 
  nest_by(dataset, input) %>% 
  ungroup() %>% 
  mutate(aov_p_value=map_dbl(
    .x = data, 
    .f = function(df){
        res= aov(variance~sample_size,data = df)
        res= summary(res)[[1]][[5]][[1]] 
        return(res)
    } 
                 )) %>% 
  mutate(DunnettTest_res=map(
    .x = data, 
    .f = function(df){
        # res= aov(variance~sample_size,data = df)
        # res= TukeyHSD(res, which = "sample_size", paired=T) %>% tidy()
      res=DescTools::DunnettTest(df$variance, g= df$sample_size)
      res= tibble(comparison= row.names(res[[1]]), 
                  diff= res[[1]][,1],
                  p.value= res[[1]][,4])
      return(res)
    }
                 )) %>% 
  select(-data) %>% 
  unnest(cols = c(DunnettTest_res))
```


```{r,fig.height=4,fig.width=8}
stat.test <-sig_res1 %>% 
  separate(comparison, "-", into= c("group1","group2")) %>% 
  mutate(p.signif= "****") 
stat.test

fig <- plot_df1 %>% 
  ggplot(mapping = aes(x=sample_size, y= variance, fill=input)) +
  geom_violin()+
  ggpubr::stat_pvalue_manual(data = stat.test, x= "group1", y.position = 0.006,label= "p.signif")+
  facet_grid(cols = vars(input),rows= vars(dataset),switch = "y")+
  theme_classic()+
  xlab("Maximum Sample Size")+ ylab(expression(VAR["RMSE"]))+
  ggsci::scale_fill_npg()+
  theme(legend.position="none")

fig
ggsave(fig, filename = "~/cluster_wrk/drug_moa/sensitivity_fitting/forward_modelling/fig_res/figure2D.pdf",width = 8,height = 4,bg="transparent")

ggsave(fig, filename = "~/cluster_wrk/drug_moa/sensitivity_fitting/forward_modelling/fig_res/figure2D.png",width = 8,height = 4,dpi = 500,bg="transparent")
```




Figure 2 C
Showing how three versions of essentiality deconvolution results are not significantly different from each other.
derive the difference between ceres, ces, demeter from combined performance and
then use it together with CI from performance_difference_test_res1 object
```{r}
# most drugs are insignificant after multiple test correction of significance.
load("~/cluster_scratch/forward_modelling/performance_testres/output_ceresbased.RData")
# report numbers 
# 545+198=743

performance_difference_test_res1 %>%
  filter(.metric== "roc_auc") %>%
  filter(dataset!="prism") %>%
  mutate(significance = p_value< (0.05/(743*2))) %>%
  mutate(rest = case_when(
    upper_ci< 0 & significance ~ "CES better",
    lower_ci> 0 & significance  ~ "CERES better"
  )) %>%
  replace(is.na(.), values = "Insignificance") %>%
  group_by(dataset,rest) %>%
  summarise(N= n())
46/545 #insignficant percentage for CTRP
17/198 # GDSC
performance_difference_test_res2 %>%
  filter(.metric== "roc_auc") %>%
  filter(dataset!="prism") %>%
  mutate(significance = p_value< (0.05/(743*2))) %>%
  mutate(rest = case_when(
    upper_ci< 0 & significance ~ "DEMETER2 better",
    lower_ci> 0 & significance  ~ "CERES better"
  )) %>%
  replace(is.na(.), values = "Insignificance") %>%
  group_by(dataset,rest) %>%
  summarise(N= n())
25/545 #insignficant percentage for CTRP
9/198 # GDSC

roc_auc_diff_drug_level1 <- combined_performance3 %>% 
  select(-variance) %>% 
  pivot_wider(names_from = input, values_from= estimate) %>% 
  mutate(ceres_ces_diff= ceres-ces) %>%  
  right_join(y = bind_rows(
          performance_difference_test_res1 %>% mutate(diff_type= "ceres-ces")
    )) %>%
  filter(.metric== "roc_auc") %>%
  filter(dataset!="prism") %>% 
  arrange(ceres_ces_diff) %>% 
  mutate(ID = fct_reorder(ID, ceres_ces_diff) )

roc_auc_diff_drug_level2 <- combined_performance3 %>% 
  select(-variance) %>% 
  pivot_wider(names_from = input, values_from= estimate) %>% 
  mutate(ceres_demeter_diff= ceres- demeter2) %>% 
  right_join(y = bind_rows(
          performance_difference_test_res2 %>% mutate(diff_type= "ceres-demeter2")
    )) %>%
  filter(.metric== "roc_auc") %>%
  filter(dataset!="prism") %>% 
  arrange(ceres_demeter_diff) %>% 
  mutate(ID = fct_reorder(ID, ceres_demeter_diff) )

plot_df <- bind_rows(roc_auc_diff_drug_level1, roc_auc_diff_drug_level2)  %>% 
  mutate(dataset= toupper(dataset)) %>% 
  mutate(diff_type= factor(diff_type, 
                      levels = c("ceres-ces", "ceres-demeter2"),
                      labels=    c("CERES - CES","CERES - DEMETER2")
                      )
         )
```


```{r, fig.width=3, fig.height=4}
fig <- plot_df%>% 
  ggplot(aes(x=ID)) + 
  geom_errorbar(aes(ymin=lower_ci, ymax=upper_ci), width=.1,alpha= 0.3) +
  geom_hline(yintercept = 0,color= "red", lty=2)+
  facet_grid(rows = vars(diff_type),cols= vars(dataset),scales = "free",switch="y")+
  theme_classic()+
  theme(axis.text.x = element_blank() , axis.title.x = element_blank(), axis.ticks.x = element_blank())+
  ylab("\U0394AUROC")

fig
ggsave(fig, filename = "~/cluster_wrk/drug_moa/sensitivity_fitting/forward_modelling/fig_res/figure2C.pdf",width = 3,height = 4,bg="transparent")

ggsave(fig, filename = "~/cluster_wrk/drug_moa/sensitivity_fitting/forward_modelling/fig_res/figure2C.png",width = 3,height = 4,dpi = 500,bg="transparent")
```


```{r}
save.image("~/cluster_scratch/forward_modelling/forwardmodelling_paper_result.RData")
write_csv(sig_res, "sig_res.csv")
write_csv(sig_res1, "sig_res1.csv")
write_csv(roc_auc_diff_drug_level1, "roc_auc_diff_drug_level1.csv")
write_csv(roc_auc_diff_drug_level2, "roc_auc_diff_drug_level2.csv")
```




